### 2017-07-21 Outline.Rmd
added outline, readme

---
title: "Outline"
author: "Shannon Pileggi"
date: "July 21, 2017"
output: html_document
---

###Target Journal: 
[*Technology Innovations in Statistics Education*](http://escholarship.org/uc/uclastat_cts_tise)

###Authors (in no particular order)
+ Shannon Pileggi (mailto:spileggi@calpoly.edu), Assistant Professor, Statistics Department, Cal Poly SLO
+ Tessa McDonnel (mailto:tessamcdonnel@ymail.com), Undergraduate Research Assistant, Statistics Department, Cal Poly SLO
+ Weston Stearns??? (mailto:weston@datacamp.com), Lead Community Course Development, DataCamp
+ Mine Centikaya-Rundel??? (mailto:mine@stat.duke.edu) Assistant Professor?, Statistics Department, Duke

###Scope:
(3) Technology Innovations - discussions of new technology created by the author(s)

 > New technologies should solve educational problems, provide infrastructure to assist statistics educators, or provide infrastructure to assist developers of statistics education technology. New Technology manuscripts should provide (at a minimum) a pedagogical context for the technology that includes a discussion of how the technology is meant to be used, who the intended users are, and what skills or concepts it is meant to help students learn. Manuscripts should provide a high-level description of the technology that includes discussing features of the design. Manuscripts must include a comparison and contrast with competing technologies, as appropriate. Authors should explain why the technology is innovative. Examples of New Technologies might include, but certainly not be limited to, web-based statistical software, applets designed to teach statistical concepts, or technology that harvests data for classroom use.

###Educational problem solved
+ Interactive platform to learn coding, with built in assistance and checks

###Infrastructure provided to assist statistics educators
+ Take advantage of existing premium courses or build your own community course

###Pedagogical context
+ How technology is meant to be used - can be used as traditional homework assignment, in the classroom during lab periods, as pre-class assignments for flipped classrooms, even as a  test or assessment tools??
+ Intendend users - novice through advanced programming students will benefit, any college educator can access or contribute
+ Skills or concepts learned - focus is on coding in R to obtain statistical results, with some interpretation

###High level description of technology
+ features of the design

###Comparison and contrast with competing technologies

###Explain why technology is innovative
+ Coding lesson / instructions are juxtaposed with practice window

###How to Create a DataCamp Community Course
+ What is needed to get started:  DataCamp account (verified instructor), GitHub
+ How to start building (including with collaborators)
+ Examples of DataCamp code for building different types of modules

### 2017-07-21 Outline.Rmd
modified formatting

@@
 
-###Educational problem solved
+### Educational problem solved
 + Interactive platform to learn coding, with built in assistance and checks
 
-###Infrastructure provided to assist statistics educators
+### Infrastructure provided to assist statistics educators
 + Take advantage of existing premium courses or build your own community course
 
-###Pedagogical context
+### Pedagogical context
 + How technology is meant to be used - can be used as traditional homework assignment, in the classroom during lab periods, as pre-class assignments for flipped classrooms, even as a  test or assessment tools??
@@
 
-###High level description of technology
+### High level description of technology
 + features of the design
 
-###Comparison and contrast with competing technologies
+### Comparison and contrast with competing technologies
 
-###Explain why technology is innovative
+### Explain why technology is innovative
 + Coding lesson / instructions are juxtaposed with practice window
 
-###How to Create a DataCamp Community Course
+### How to Create a DataCamp Community Course
 + What is needed to get started:  DataCamp account (verified instructor), GitHub

### 2017-07-21 Outline.Rmd
updated outline

@@
 ### Educational problem solved
-+ Interactive platform to learn coding, with built in assistance and checks
++ Interactive platform to learn coding, with built in assistance and checks for understanding
 
 ### Infrastructure provided to assist statistics educators
-+ Take advantage of existing premium courses or build your own community course
++ Take advantage of existing courses or build your own community course
++ Tutorials on how to build courses
++ Links to some github repositories
 
@@
 
-### High level description of technology
-+ features of the design
-
-### Comparison and contrast with competing technologies
-
-### Explain why technology is innovative
-+ Coding lesson / instructions are juxtaposed with practice window
-
-### How to Create a DataCamp Community Course
+### High level description of technology / How to Create a DataCamp Community Course
 + What is needed to get started:  DataCamp account (verified instructor), GitHub
@@
 + Examples of DataCamp code for building different types of modules
+
+### Comparison and contrast with competing technologies  
++ Swirl lessons
++ Anything else?
+
+### Explain why technology is innovative
++ Coding lesson and instructions are juxtaposed with practice window, built in points and assessments to check for understanding, can integrate class with learning management systems

### 2017-07-21 Outline.Rmd
Update Outline.Rmd

@@
 
-###Target Journal: 
+### Target Journal: 
 [*Technology Innovations in Statistics Education*](http://escholarship.org/uc/uclastat_cts_tise)
 
-###Authors (in no particular order)
+### Authors (in no particular order)
 + Shannon Pileggi (mailto:spileggi@calpoly.edu), Assistant Professor, Statistics Department, Cal Poly SLO
@@
 
-###Scope:
+### Scope:
 (3) Technology Innovations - discussions of new technology created by the author(s)

### 2017-07-21 Outline.Rmd
Update Outline.Rmd

@@
 + Shannon Pileggi (mailto:spileggi@calpoly.edu), Assistant Professor, Statistics Department, Cal Poly SLO
-+ Tessa McDonnel (mailto:tessamcdonnel@ymail.com), Undergraduate Research Assistant, Statistics Department, Cal Poly SLO
++ Tessa Mcdonnel (mailto:tessamcdonnel@ymail.com), Undergraduate Research Assistant, Statistics Department, Cal Poly SLO
 + Weston Stearns??? (mailto:weston@datacamp.com), Lead Community Course Development, DataCamp

### 2017-07-23 Outline.Rmd
added competing tech and innovation

@@
 + Swirl lessons
++ 'Try R' by Code School 
 + Anything else?
@@
 + Coding lesson and instructions are juxtaposed with practice window, built in points and assessments to check for understanding, can integrate class with learning management systems
++ All DataCamp courses are linked through GitHub version control, making it easy for statistics educators to collaborate and reproduce code.

### 2017-07-24 Outline.Rmd
Update Outline.Rmd

@@
 + Interactive platform to learn coding, with built in assistance and checks for understanding
++ User-friendly interface, unlike Swirl's interface which can be daunting for students who have never seen R
 
@@
 + Swirl lessons
-+ 'Try R' by Code School 
++ 'Try R' by Code School--> interactive platform but not reproducible
 + Anything else?

### 2017-07-24 Scope.Rmd
Rename Outline.Rmd to Scope.Rmd

--- 2017-07-24 Outline.Rmd
@@
 + Tutorials on how to build courses
-+ Links to some github repositories
++ Use the template course files from 'Create a DataCamp Course' dialog
++ Links to some github repositories: most importantly 'datacamp/testwhat' to help with submission correctness tests
 

### 2017-07-25 Outline.Rmd
added outline

--- 2017-07-21 Outline.Rmd
@@
 title: "Outline"
-author: "Shannon Pileggi"
-date: "July 21, 2017"
+author: "Tessa McDonnel"
+date: "7/24/2017"
 output: html_document
@@
 
-### Target Journal: 
-[*Technology Innovations in Statistics Education*](http://escholarship.org/uc/uclastat_cts_tise)
+### Abstract
 
-### Authors (in no particular order)
-+ Shannon Pileggi (mailto:spileggi@calpoly.edu), Assistant Professor, Statistics Department, Cal Poly SLO
-+ Tessa Mcdonnel (mailto:tessamcdonnel@ymail.com), Undergraduate Research Assistant, Statistics Department, Cal Poly SLO
-+ Weston Stearns??? (mailto:weston@datacamp.com), Lead Community Course Development, DataCamp
-+ Mine Centikaya-Rundel??? (mailto:mine@stat.duke.edu) Assistant Professor?, Statistics Department, Duke
-
-### Scope:
-(3) Technology Innovations - discussions of new technology created by the author(s)
-
- > New technologies should solve educational problems, provide infrastructure to assist statistics educators, or provide infrastructure to assist developers of statistics education technology.
-New Technology manuscripts should provide (at a minimum) a pedagogical context for the technology that includes a discussion of how the technology is meant to be used, who the intended users are, and what skills or concepts it is meant to help students learn.
-Manuscripts should provide a high-level description of the technology that includes discussing features of the design.
-Manuscripts must include a comparison and contrast with competing technologies, as appropriate.
-Authors should explain why the technology is innovative.
-Examples of New Technologies might include, but certainly not be limited to, web-based statistical software, applets designed to teach statistical concepts, or technology that harvests data for classroom use.
-
-### Educational problem solved
-+ Interactive platform to learn coding, with built in assistance and checks for understanding
-
-### Infrastructure provided to assist statistics educators
-+ Take advantage of existing courses or build your own community course
-+ Tutorials on how to build courses
-+ Links to some github repositories
-
-### Pedagogical context
+### Introduction
+* What is DataCamp?
+* increased use of R and R Markdown in classrooms- need more effective way to get students familiar with R
+* competing technologies- alternative ways for students to learn R in/out of the classroom with interactive platform
+    + Swirl: versatile for instructors but can not monitor student work 
+    + TryR: not versatile and can not monitor student work
+* Gamification- increased student focus when points are on the line, must actively engage to do well
+* Pedagogical Context
     + How technology is meant to be used - can be used as traditional homework assignment, in the classroom during lab periods, as pre-class assignments for flipped classrooms, even as a  test or assessment tools??
@@
 
-### High level description of technology / How to Create a DataCamp Community Course
-+ What is needed to get started:  DataCamp account (verified instructor), GitHub
-+ How to start building (including with collaborators)
-+ Examples of DataCamp code for building different types of modules
+### How to use Data Camp
 
-### Comparison and contrast with competing technologies  
-+ Swirl lessons
-+ Anything else?
+##### Using Courses
+* need a DataCamp account
+* Easy for students- don't have to download anything because course is web based 
+* Take advantage of free community courses- beginner to advanced programming students
+* Premium content free for academia- create a Classroom Group to track student progress
+* Monitor your own progress with My Profile
 
-### Explain why technology is innovative
-+ Coding lesson and instructions are juxtaposed with practice window, built in points and assessments to check for understanding, can integrate class with learning management systems
+##### Creating Course
+* What is needed to get started:  DataCamp account (verified instructor), link to GitHub
+* Use the template course files from 'Create a DataCamp Course' dialog
+* How to start building (including with collaborators)
+    + Course Structure
+    + Using Teach Editor (as opposed to GitHub)- can easily edit, preview and save changes
+    + Examples of DataCamp code for building different types of modules: normal, plain multiple choice, multiple choice for exercises involving graphs/images
+    + Capabilities of SCTs
+    + Links to some github repositories: 'datacamp/courses-intro-r' as another example of DataCamp code and 'datacamp/testwhat' to help with submission correctness tests
+    + Tailoring pre-existing code to fit specific needs
+    + Assign course to Classroom Group- can assign specific chapters/entire course/number of points
+* Tips for smoother course development process
+    + Using LaTeX math symbols to display greek letters, operators, ect.
+    + Need to add 'requirements.r' file with devtools to add packages
+
+### Integrating with LMS
+* Easy to track student progress
+
+### Discussion 
+* experience of statistics instructors who have created a DataCamp course and used it in the classroom
+* overall pros, some cons- doesn't help students learn R Markdown
+* student difficulties/feedback?
+* how to get premium content free for teachers

### 2017-07-25 Meeting Notes.Rmd
added meeting notes

---
title: "Meeting Notes 7/25/17"
author: "Tessa McDonnel"
date: "7/25/2017"
output: html_document
---

#### Weston Role for Collaboration

* can provide data on users (1.3) million who have taken classes
* know common mistakes from users
* scts tailored to student mistakes
* 1,000 universities enrolled
* Professors use it as pre-lab exercise or assign entire courses

#### Perspectives on how it works in classroom

* Weston will try to get someone who has experience... might have to wait till October

#### Sharing platform preference

* LaTeX and GitHub
* Use email to communicate

#### Weston Workflow
* what data camp is 
* look over what's written about the how-to

## integrating LMS

* used a lot by professors and works well

### 2017-07-26 manuscript.tex
Added TISE style file and shell for .tex manuscript.

\documentclass[]{tise_style}

\title{Enter our title here}

\author{Tessa Mcdonnel \\Statistics Department, California Polytechnic State University, San Luis Obispo}
%\author{Shannon Pileggi \\Statistics Department, California Polytechnic State University, San Luis Obispo}

\begin{document}

\section{Introduction}

Check this out

\end{document}

### 2017-07-26 TISE reviewer guidelines.Rmd
added TISE reviewer guidelines

---
title: "GUIDELINES FOR REVIEWING TECHNOLOGY INNOVATIONS"
author: "Shannon Pileggi"
date: "July 26, 2017"
output: html_document
---

### Guidelines

This paper has been submitted as a Technology Innovations paper.  A description of technology innovation papers from the Aims & Scope seciton of the journal is provided below for reference.  When reviewing this manuscript, please pay attention to the questions listed below.   Of course, we are interested in any other comments or criticism you might have that would improve this paper, and also any suggestions for advice we should give to future reviewers of technology innovations.

1. Innovation is key.  Does the paper clearly describe the innovation and why it is innovative?   The new technology could very well be a modification of existing technology or technologies.  Does the author make it clear which parts are innovative and which are not?    Is the innovation useful? Would you use it or could you imagine a colleague using it?

2. Does the author clearly state the problem (educational, technical, administrative, etc.) that is to be solved by the technology? Do you feel that this is a compelling problem that is in need of a solution?

3. Authors are not required to empirically justify that their innovation is effective. That said, does the paper propose a  convincing argument for why the proposed innovation is capable of solving or alleviating the stated problem? Can you suggest ways of strengthening this argument.

4. Does the paper make clear the target audience for the innovation? What level of students, what level of preparation? What is assumed about the students' backgrounds? About the teachers'/instructors' background?

5. Has the paper given readers enough information to decide whether this is an implementation that readers would like to adopt?

6. For papers that describe new technologies, does the technology seem to you to be well designed? Can you suggest improvements, or identify features that would be hindrances either for students or instructors? (This might not be applicable to all submissions, of course.) Are you lacking information to make this decision and would such information, if provided, improve the paper?

7. Finally: should it be published?  Will it be publishable after your recommendations are made? Is it already publishable (pending minor changes)? Or are there too many open questions, a lack of novelty, or a lack of interest that prevent it from being publishable?

### Aims & Scope

Technology Innovations are of two types: discussions of new technology created by the author(s) or case studies of innovative uses of existing technology. New technologies should solve educational problems, provide infrastructure to assist statistics educators, or provide infrastructure to assist developers of statistics education technology. New Technology manuscripts should provide (at a minimum) a pedagogical context for the technology that includes a discussion of how the technology is meant to be used, who the intended users are, and what skills or concepts it is meant to help students learn. Manuscripts should provide a high-level description of the technology that includes discussing features of the design. Manuscripts must include a comparison and contrast with competing technologies, as appropriate. Authors should explain why the technology is innovative. Examples of New Technologies might include, but certainly not be limited to, web-based statistical software, applets designed to teach statistical concepts, or technology that harvests data for classroom use.

Technology Case Studies are descriptions of particular innovative uses of existing technology to improve statistics education or are descriptions of methods for teaching the use of technology to solve problems of general statistical interest. Technology case studies should be feasible in a variety of settings, and authors should discuss implementation and access issues (e.g. cost, maintenance). Authors must provide a pedagogical context that includes a description of the problem solved by the use of technology and, more particularly, a description of the setting in which the authors implemented the technology. Examples might include descriptions of using data collection problems to collect "live" data, an example of using XML for data exchange, or demonstrations of teaching technologies that allow students to access unusual or complex data formats.

### 2017-07-27 manuscript.tex

@@
-\documentclass[]{tise_style}
+\documentclass{tise_style}
+\usepackage{natbib}
 
@@
 
-\author{Tessa Mcdonnel \\Statistics Department, California Polytechnic State University, San Luis Obispo}
+\author{Tessa Mcdonnel, Shannon Pileggi,  \\Statistics Department, California Polytechnic State University, San Luis Obispo}
 %\author{Shannon Pileggi \\Statistics Department, California Polytechnic State University, San Luis Obispo}
+
+\Abstract{ The text of your abstract.}
+
+\Keywords{one, two, three}
 
@@
 
-Check this out
+Check this out, Schubert said this \cite{Schubert13}.
+
+Check this out, Campbell said this \cite{Campbell02} regularly, but cite this in parentheses \citep{Campbell02}.
+
+Check this out, Chi said this \cite{Chi81}.
+
+\bibliographystyle{ECA_jasa}
+\bibliography{bibfile}
 

### 2017-08-08 manuscript.tex
started draft of intro

@@
 
+It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to unfold, the use of statistical software has become increasingly emphasized in statistics education.
+By integrating the capabilities of technology in introductory statistics courses, students can explore statistical ideas by analyzing and interpreting real data sets (Chance2007), giving them an authentic view of how statistics is practiced outside of the classroom (Broaddus2013).
+The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education} (GAISE) College Report has also prompted the use of more technology in introductory courses.
+
+The goal for any introductory statistics course is to help students develope the ability to think statistically (AmericanStatisticalAssociation2016). 
+Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as variability, randomness and simulation.
+
+Although numerous statistical technologies exist, \textit{R} and \textit{R Studio} provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses (Chance2007).
+R allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark an interest in the domain of statistics.
+
+With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R.
+
+For a statistical learning tool to be effective, the software system should be modular, extensible, reproducable, and web-based (Hare2017).
+
+Modulariy is critical component in designing a statistical learning tool; it allows independent pieces to be easily added, modified or removed from the entire functionality (Hare2017).
+
 Check this out, Schubert said this \cite{Schubert13}.

### 2017-08-08 manuscript.tex
started intro draft
Update manuscript.tex

@@
 
-It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to unfold, the use of statistical software has become increasingly emphasized in statistics education.
-By integrating the capabilities of technology in introductory statistics courses, students can explore statistical ideas by analyzing and interpreting real data sets (Chance2007), giving them an authentic view of how statistics is practiced outside of the classroom (Broaddus2013).
-The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education} (GAISE) College Report has also prompted the use of more technology in introductory courses.
+It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to 
+unfold, the use of statistical software has become increasingly emphasized in statistics education. By integrating the 
+capabilities of technology in introductory statistics courses, students can explore statistical ideas by analyzing and 
+interpreting real data sets (Chance2007), giving them an authentic view of how statistics is practiced outside of the 
+classroom (Broaddus2013). The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education} (GAISE) 
+College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators to use technology "as a way to explore conceptual ideas and enhance student learning" (AmericanStatisticalAssociation2016).
 

### 2017-08-08 manuscript.tex
Update manuscript.tex

@@
 With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R.
+For students who have never been exposed to programing, the \textit{R} interface can be a intimidating. It is often the case
+that the main source of student difficulties are with software and not the statistical concepts themselves (Hare2017). To 
+overcome this learning curve, instructors utilize R teaching tools such as Swirl and TryR. Swirl is sim
 

### 2017-08-08 manuscript.tex
Update manuscript.tex

@@
 
-With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R.
-For students who have never been exposed to programing, the \textit{R} interface can be a intimidating. It is often the case
-that the main source of student difficulties are with software and not the statistical concepts themselves (Hare2017). To 
-overcome this learning curve, instructors utilize R teaching tools such as Swirl and TryR. Swirl is sim
+With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R 
+programing.
+For students who have never been exposed to computer coding, the \textit{R} interface can be a intimidating. It is often the 
+case that the main source of student difficulties are with software and not the statistical concepts themselves (Hare2017). To 
+overcome this learning curve, instructors utilize R teaching tools such as Swirl and TryR. Similar to a DataCamp course, Swirl
+offers an interactive learning environment and allows educators to tailor the existing material to meet their specific needs.
+
+While these technologies have similar capabilities,
 

### 2017-08-09 Outline.Rmd
added meeting notes
updated outline with Mine's input

@@
     + TryR: not versatile and can not monitor student work
+    + LearnR
 * Gamification- increased student focus when points are on the line, must actively engage to do well
@@
     + Skills or concepts learned - focus is on coding in R to obtain statistical results, with some interpretation
+*accessibility - available on tablets/mobile devices
 
@@
     + Need to add 'requirements.r' file with devtools to add packages
+    + When using datacamp and github, press 'refresh' when available on the screen
 
@@
 * Easy to track student progress
+
+### iterative development
+* not sure where this fits in the outline - but use metadata from course to iteratively develop labs/activities where students are struggling
 

### 2017-08-13 manuscript.tex
added competing technologies

--- 2017-08-08 manuscript.tex
@@
 capabilities of technology in introductory statistics courses, students can explore statistical ideas by analyzing and 
-interpreting real data sets (Chance2007), giving them an authentic view of how statistics is practiced outside of the 
-classroom (Broaddus2013). The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education} (GAISE) 
-College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators to use technology "as a way to explore conceptual ideas and enhance student learning" (AmericanStatisticalAssociation2016).
+interpreting real data sets \citep{Chance2007}, giving them an authentic view of how statistics is practiced outside of the 
+classroom \citep{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education} 
+(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators 
+to use technology "as a way to explore conceptual ideas and enhance student learning" (AmericanStatisticalAssociation2016).
 
-The goal for any introductory statistics course is to help students develope the ability to think statistically (AmericanStatisticalAssociation2016). 
-Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as variability, randomness and simulation.
+The goal for any introductory statistics course is to help students develope the ability to think statistically 
+\citep{AmericanStatisticalAssociation2016}. 
+Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
+variability, randomness and simulation.
 
-Although numerous statistical technologies exist, \textit{R} and \textit{R Studio} provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses (Chance2007).
-R allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark an interest in the domain of statistics.
+Although numerous statistical technologies exist, \textit{R} and \textit{R Studio} provide extensive statistical capabilites 
+(free of charge) and are commonly used in statistics courses \citep{Chance2007}. R allows students to explore real-world data 
+sets which can not only enhance their understanding of concepts, but can also spark an interest in the domain of statistics 
+\citep{Wang2017}.
 
-With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R.
+With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R. While R
+software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition,
+popular interactive teaching technologies have been created including Swirl (need to cite this), LearnR and TryR. These tools 
+allow students to work through coding problems while recieving immediate feedback. Swirl is an open source R software package 
+that users access in their R console. This interactive learning tool contains several pre-existing lessons but what makes 
+Swirl so popular is its versitality; educators can create their own lesson (or tailor a pre-existing one) to fit their 
+curriculum and assign it to students. TryR (Code School 2014) and LearnR are web-based programs and do not have this 
+reproducible capability. Public content authoring is not available so educators are limited on what they can teach their 
+students. The R console can be intimidating to introductory statistics students so an advantage of web-based teaching tools is 
+the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with 
+software than the statistical concepts themselves \citep{Hare2017}.
 
-For a statistical learning tool to be effective, the software system should be modular, extensible, reproducable, and web-based (Hare2017).
+A not so popular interactive teaching tool is DataCamp- a web application where students can take existing courses or lessons 
+that their instructure created.
+
+For a statistical learning tool to be effective, the software system should be modular, extensible, reproducable, and web-
+based (Hare2017).
 

### 2017-08-14 manuscript.tex
Update manuscript.tex

@@
 software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition,
-popular interactive teaching technologies have been created including Swirl (need to cite this), LearnR and TryR. These tools 
-allow students to work through coding problems while recieving immediate feedback. Swirl is an open source R software package 
+popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR and TryR. These tools 
+allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an open source R software package 
 that users access in their R console. This interactive learning tool contains several pre-existing lessons but what makes 
 Swirl so popular is its versitality; educators can create their own lesson (or tailor a pre-existing one) to fit their 
-curriculum and assign it to students. TryR (Code School 2014) and LearnR are web-based programs and do not have this 
-reproducible capability. Public content authoring is not available so educators are limited on what they can teach their 
-students. The R console can be intimidating to introductory statistics students so an advantage of web-based teaching tools is 
+curriculum and assign it to students \citep{Carchedi2014}.
+
+*I'm confused about LearnR and thinks someone else should write about it.*
+
+TryR (Code School 2014) is a web-based programs and do not have this reproducible capability.
+Since public content authoring is not available, educators are limited on what they can teach their students.
+The R console can be intimidating to introductory statistics students so an advantage of web-based teaching tools is
 the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with 
-software than the statistical concepts themselves \citep{Hare2017}.
+software than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
+all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.
 
-A not so popular interactive teaching tool is DataCamp- a web application where students can take existing courses or lessons 
-that their instructure created.
+DataCamp is also a web application that offers exhisting interactive R programing courses but unlike TryR, educators can 
+create their own courses that coincide with the material.
 

### 2017-08-14 manuscript.tex
added some how-to

@@
 Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
-variability, randomness and simulation.
-
-Although numerous statistical technologies exist, \textit{R} and \textit{R Studio} provide extensive statistical capabilites 
-(free of charge) and are commonly used in statistics courses \citep{Chance2007}. R allows students to explore real-world data 
-sets which can not only enhance their understanding of concepts, but can also spark an interest in the domain of statistics 
-\citep{Wang2017}.
+variability, randomness and simulation. Although numerous statistical technologies exist, \textit{R} and \textit{R Studio} 
+provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \citep{Chance2007}. R 
+allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
+an interest in the domain of statistics \citep{Wang2017}.
 
@@
 
-TryR (Code School 2014) is a web-based programs and do not have this reproducible capability.
+TryR (Code School 2014) is a web-based programs and does not have this reproducible capability.
 Since public content authoring is not available, educators are limited on what they can teach their students.
@@
 
-DataCamp is also a web application that offers exhisting interactive R programing courses but unlike TryR, educators can 
-create their own courses that coincide with the material.
+DataCamp is also a web application that offers interactive R programing courses but unlike TryR, educators can 
+create their own courses that coincide with the lessons or assign a pre-existing DataCamp course. The DataCamp website offers 
+free community courses as well as more specialized classes that you need to purchase. ... (i'll come back to this)
 
@@
 
-Modulariy is critical component in designing a statistical learning tool; it allows independent pieces to be easily added, modified or removed from the entire functionality (Hare2017).
+Modulariy is critical component in designing a statistical learning tool; it allows independent pieces to be easily added, 
+modified or removed from the entire functionality (Hare2017).
+
+\section{How to Use DataCamp}
+Pre-existing courses:
+DataCamp has a range of available free community courses that educators can utilize for supplimental R practice.
+
+Creating a DataCamp Course:
+To create a course on DataCamp you will first need to create a DataCamp account by visiting website\www.datacamp.com/teach and
+have a GitHub account. The simplest way to begin building the course is to use the templete course files from the 'Create
+DataCamp Course' dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are 
+make through DataCamp will update the GitHub repository and visa versa. The GitHub repository will contain three files: 
+README.md, course.yml, and chapter1.Rmd.
+Readme.md contains helpful information of how to get started, citing resourses to learn more about the process. 
+course.yml is a file that contains general information about the course you're creating: title, university, description, 
+difficulty level, ect.  
+chapter1.Rmd is a template chapter file with examples of 'normal' interative coding exercises and multiple choice questions.
+To add more chapters to an R course, create new files in the repository and name them chapter1.Rmd, chapter2.Rmd, chapter3.Rmd
+ect.
+
+DataCamp courses can contain 3 different types of exercises: Normal, Multiple choice, and video.
 

### 2017-08-14 manuscript.tex
Update manuscript.tex

@@
 popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR and TryR. These tools 
-allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an open source R software package 
-that users access in their R console. This interactive learning tool contains several pre-existing lessons but what makes 
-Swirl so popular is its versitality; educators can create their own lesson (or tailor a pre-existing one) to fit their 
-curriculum and assign it to students \citep{Carchedi2014}.
+allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an 
+open source R software package that allows students to learn R programing in their R console.
+This interactive learning tool contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own
+lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \citep{Carchedi2014}.
 
@@
 create their own courses that coincide with the lessons or assign a pre-existing DataCamp course. The DataCamp website offers 
-free community courses as well as more specialized classes that you need to purchase. ... (i'll come back to this)
+free community courses and specialized 'Premium' classes that you need to purchase. However, when used for academic purposes
+the premium DataCamp content if free.. (i'll come back to this).
 
-For a statistical learning tool to be effective, the software system should be modular, extensible, reproducable, and web-
-based (Hare2017).
-
-Modulariy is critical component in designing a statistical learning tool; it allows independent pieces to be easily added, 
-modified or removed from the entire functionality (Hare2017).
+Each chapter in a DataCamp course is made up of modular exercises.
+Modulariy is critical component in designing a statistical learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality \citep{Hare2017}.
+Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
+these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
+are not cummulative; every exercise begins with a clear workspace so any object defined in a previous exercise needs to be 
+defined again.
 
 \section{How to Use DataCamp}
-Pre-existing courses:
+
+\subsection{Pre-existing R courses}
 DataCamp has a range of available free community courses that educators can utilize for supplimental R practice.
 
-Creating a DataCamp Course:
+\subsection{Creating a DataCamp Course}
 To create a course on DataCamp you will first need to create a DataCamp account by visiting website\www.datacamp.com/teach and

### 2017-08-14 manuscript.tex
Update manuscript.tex

@@
 With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R. While R
-software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition,
-popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR and TryR. These tools 
+software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition 
+to R programming, popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR
+and TryR. These tools 
 allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an 
-open source R software package that allows students to learn R programing in their R console.
-This interactive learning tool contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own
+open source R software package that allows students to learn R programing in their R console. This interactive learning tool
+contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own 
 lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \citep{Carchedi2014}. 
+*Swirl can be linked to a Coursera gradebook- learners can have swirl automatically notify coursera of a completed lesson
+but this is not avaiblable for the classroom setting (coursera website) so should I include this?*
 
@@
 
-TryR (Code School 2014) is a web-based programs and does not have this reproducible capability.
-Since public content authoring is not available, educators are limited on what they can teach their students.
-The R console can be intimidating to introductory statistics students so an advantage of web-based teaching tools is
+TryR (Code School 2014) is a web-based programs and does not have this reproducible capability. Since public content authoring 
+is not available, educators are limited on what they can teach their students. The R console can be intimidating to 
+introductory statistics students so an advantage of web-based teaching tools is 
 the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with 
@@
 
-DataCamp is also a web application that offers interactive R programing courses but unlike TryR, educators can 
-create their own courses that coincide with the lessons or assign a pre-existing DataCamp course. The DataCamp website offers 
-free community courses and specialized 'Premium' classes that you need to purchase. However, when used for academic purposes
-the premium DataCamp content if free.. (i'll come back to this).
+DataCamp has the same reproducable capabilities as Swirl but is a web-based application; educators can 
+create their own courses that coincide with their lessons and students can access the course without having to install R. 
+The DataCamp website offers pre-existing free community courses and specialized 'Premium' classes that you need to purchase. 
+However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this). 
+When you create a free classroom group on the DataCamp website, you can add student's to the group and assign pre-existing 
+course or a course that you've created for the particular class.
 
-Each chapter in a DataCamp course is made up of modular exercises.
-Modulariy is critical component in designing a statistical learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality \citep{Hare2017}.
-Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
+A feature that set's DataCamp courses apart from competing technologies is the ability to track student progress. Educators
+can set deadlines for assignments and easily see not only when students complete an assignment but also which sections the
+students had trouble with in a detailed report (datacamp/teach website). Student scores can be automatically updated to a 
+current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration.
+
+Each chapter in a DataCamp course is made up of modular exercises. Modulariy is critical component in designing a statistical
+learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality 
+\citep{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
 these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions

### 2017-08-14 manuscript.tex
added gamification section draft

@@
 lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \citep{Carchedi2014}.
+
 *Swirl can be linked to a Coursera gradebook- learners can have swirl automatically notify coursera of a completed lesson
@@
 are not cummulative; every exercise begins with a clear workspace so any object defined in a previous exercise needs to be 
-defined again.
+defined again. Each of these exercises can be given a number of redeemable points which the students can see when they begin
+the exercise, introducing a gamification feature to the learning experience. If the student completes the exercise without 
+any help they will recieve the full points. If they ask for a hint, 30 percent of the available points will be deducted and 
+all of the points will be deducted if they ask for the entire answer. When in a classroom group, students can view their 
+progress (points and chapters completed) as well as then progress of their peers. This can help students perform better 
+because they want to be on par with the rest of the class; furthermore, when students can see the number of available points 
+for an exercise it will motivate them to meet their personal achievement goals. \citep{Chang2016}.
 

### 2017-08-15 manuscript.tex
draft of course exercise structure

@@
 \section{Introduction}
+\usepackage{hyperref}
 
@@
 \subsection{Creating a DataCamp Course}
-To create a course on DataCamp you will first need to create a DataCamp account by visiting website\www.datacamp.com/teach and
+To create a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} and
 have a GitHub account. The simplest way to begin building the course is to use the templete course files from the 'Create
@@
 
+Educators are able to edit their courses in a number of ways but the 'Teach Editor' located in the teach dashboard is the
+most straight forward editor. The 'Teach Editor' is specifically designed to make the creation process of a DataCamp course
+as painless as possible, allowing writers to edit, preview, save changes and synchronize to a GitHub repository. Editing can
+also be done through GitHub's online editor and through git locally but these methods do not allow for automatic content
+previewing.
+
 DataCamp courses can contain 3 different types of exercises: Normal, Multiple choice, and video.
+
+A 'NormalExercise' is an interactive coding exercise containing a lesson section, instructions, pre-exercise code, sample 
+code, hint, solution and a submission correctness testing coded (SCT). However, the interface for students (or the 'Preview
+mode) only includes the lesson, Instructions, R script panel and a R console panel.
+
+In the 'assignment' portion of the exercise, instructors can add additional information about the assignment that will help
+students understand and complete the instructions. The Instructions section will contain the actual task the student is 
+asked to execute. The 'pre-exercise code' sets up the workspace for the student; this section will contain code to import
+data sets, install packages and any other operation that you want to be in the workspace but hidden from students. The 'sample
+code' section contains code or notes that students view in the R script panel. Students' also use the R script panel to write
+the code that solves the tasks in the instructions. If students are not able to complete the task without help, they can click
+on the 'Hint' button or eventually the 'solution'.
+
+Solution Correctness Test code..
 

### 2017-08-19 manuscript.tex
Updated bib file with new entries - in future export bib file from mendeley when adding new sources.  Updated tex file with new bibliogrphy style - hopefully this will allow you to compile in RStudio better.
Update manuscript.tex

@@
 \usepackage{natbib}
+%Having trouble getting tise_style to compile correctly in RStudio, will re-run it with this before submission
+
+%-----------------------------------------------------------------------------------------------------
+%Substitute this all with tise_style
+%\documentclass[12pt]{article}
+%\usepackage{natbib}  % used for citations
+%\usepackage[parfill]{parskip} %used for formatting style of text
+%\usepackage{url}
+
+% Sets margins to 1 in
+%\addtolength{\oddsidemargin}{-.5in}%
+%\addtolength{\evensidemargin}{-.5in}%
+%\addtolength{\textwidth}{1in}%
+%\addtolength{\textheight}{1.3in}%
+%\addtolength{\topmargin}{-.8in}%
+%-----------------------------------------------------------------------------------------------------
 
@@
 
-\Abstract{ The text of your abstract.}
-
-\Keywords{one, two, three}
-
 \begin{document}
 
+\maketitle
+
 \section{Introduction}
-\usepackage{hyperref}
 
@@
 
-*I'm confused about LearnR and thinks someone else should write about it.*
+*I'm confused about LearnR and think someone else should write about it.*
 
@@
 
-Check this out, Schubert said this \cite{Schubert13}.
+%Check this out, Schubert said this \cite{Schubert13}.
 
-Check this out, Campbell said this \cite{Campbell02} regularly, but cite this in parentheses \citep{Campbell02}.
+%Check this out, Campbell said this \cite{Campbell02} regularly, but cite this in parentheses \citep{Campbell02}.
 
-Check this out, Chi said this \cite{Chi81}.
+%Check this out, Chi said this \cite{Chi81}.
 
-\bibliographystyle{ECA_jasa}
-\bibliography{bibfile}
+%Use this for final submission
+%\bibliographystyle{ECA_jasa}
+\bibliographystyle{Chicago}
+\bibliography{library}
 

### 2017-08-22 manuscript.tex
Update manuscript.tex
testing merge
added SCTs and exercise overview

@@
 Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
-variability, randomness and simulation. Although numerous statistical technologies exist, \textit{R} and \textit{R Studio}
+variability, randomness and hypothesis testing. Although numerous statistical technologies exist, \textit{R} and \textit{R Studio}
 provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \citep{Chance2007}. R
@@
 
-*Swirl can be linked to a Coursera gradebook- learners can have swirl automatically notify coursera of a completed lesson
-but this is not avaiblable for the classroom setting (coursera website) so should I include this?*
+While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, this is not avaiblable for the classroom
+learning management systems (LMS).
 
@@
 
-A feature that set's DataCamp courses apart from competing technologies is the ability to track student progress. Educators
+A feature that sets DataCamp apart from competing technologies is the ability to track student progress. Educators
 can set deadlines for assignments and easily see not only when students complete an assignment but also which sections the
 students had trouble with in a detailed report (datacamp/teach website). Student scores can be automatically updated to a
-current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration.
+current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration of student work.
 
@@
 
+The submission correctness testing code (or SCT) is the backbone for DataCamp's interactive nature. If a student submits an incorrect answer, they will 
+receive immediate feedback on what they are doing wrong and the system will guide them to the right answer. Instructors can use the default feedback
+that DataCamp automatically generates or write their own custom messages. The default feedback is meaningful and specific; most of the time custom messages
+are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. DataCamp provides a helpful
+R package called 'testwhat' which acts as a guide to writing the SCTs. 'testwhat' contains functions that can test different types of problems including
+loops, object definitions, printed output, functions, ect (datacamp website), this submission correctness testing code compares the ideal answer (from the 
+solution) to the students answer. Different arguements can be added to the test functions to alter the testing process and automatic feedback.
+
+**add an example of a test_function sct
+
 In the 'assignment' portion of the exercise, instructors can add additional information about the assignment that will help
@@
 data sets, install packages and any other operation that you want to be in the workspace but hidden from students. The 'sample
-code' section contains code or notes that students view in the R script panel. Students' also use the R script panel to write
+code' section contains code or notes that students view in the R script panel. Students also use the R script panel to write
 the code that solves the tasks in the instructions. If students are not able to complete the task without help, they can click
-on the 'Hint' button or eventually the 'solution'.
+on the 'Hint' button or eventually the 'solution'. When the student clicks the 'Submit Code' button, their answer passes through the SCT code where the
+code is checked for errors.
 
-Solution Correctness Test code..
+**add example of a normal coding exercise
+
+The 'MultipleChoiceExercise', as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson' 
+portion of the exercise and offer solutions in the 'Insruction' section. Like the 'normal' coding exercises, the lesson, instructions, pre-exercise code and
+SCTs have to be specified but sample and solution code do not. There are two types of multiple choice questions, simple and regular. The simple multiple 
+choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises allow instructors to pre
+-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises are straightforward to write can 
+act as quick checks for understanding throughout the chapter.
+
+**add example of regular multiple choice exercise
+
+Video exercises act as in instructional video addition to a DataCamp course; instructors can add short videos of them explaining concepts and with relevent slides that appear in the background.
+The DataCamp website \url{https://www.datacamp.com/teach/documentation#tab_code_exercises} provides more detail on the content of the various exercises.
 

### 2017-08-22 manuscript.tex
edited intro

@@
 It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
-unfold, the use of statistical software has become increasingly emphasized in statistics education. By integrating the
-capabilities of technology in introductory statistics courses, students can explore statistical ideas by analyzing and
+unfold, the use of statistical software has become increasingly emphasized in education. By integrating the
+capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
 interpreting real data sets \citep{Chance2007}, giving them an authentic view of how statistics is practiced outside of the
@@
 
-With this increased use of R in classrooms, there is a need for a more effective way to get students familiar with R. While R
+With this increased use of R in classrooms, there is a need for an effective way to get students familiar with R. While R
 software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition
@@
 lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \citep{Carchedi2014}.
-
 While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, this is not avaiblable for the classroom
@@
 is not available, educators are limited on what they can teach their students. The R console can be intimidating to
-introductory statistics students so an advantage of web-based teaching tools is
+introductory statistics students so an advantage of a web-based teaching tool is
 the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with
@@
 create their own courses that coincide with their lessons and students can access the course without having to install R.
+Courses are available through the DataCamp website so students can access the lesson through their web-browser on their laptop,
+tablet, or moble device. 
 The DataCamp website offers pre-existing free community courses and specialized 'Premium' classes that you need to purchase. 
 However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
-When you create a free classroom group on the DataCamp website, you can add student's to the group and assign pre-existing
-course or a course that you've created for the particular class.
+Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
+'community' courses and assign a course that they've created for the particular class.
+
+The collection of community courses avaiable at DataCamp inlcude a wide range of topics from 'Introduction to R' to
+'Quantitative Risk Management in R' so novice through advanced programming students will benefit.
 
@@
 these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
-are not cummulative; every exercise begins with a clear workspace so any object defined in a previous exercise needs to be
+are not cummulative; every exercise begins with a clear workspace so an object defined in a previous exercise needs to be
 defined again. Each of these exercises can be given a number of redeemable points which the students can see when they begin
@@
 
+DataCamp can be used in the classroom in a number of ways: as traditional homework assignments, as an
+activity during lab periods, as pre-class assignments for a flipped classroom, and even as a test or assessment tool.
+
 \section{How to Use DataCamp}
@@
 To create a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} and
-have a GitHub account. The simplest way to begin building the course is to use the templete course files from the 'Create
+also a GitHub account. The simplest way to begin building the course is to use the templete course files from the 'Create
 DataCamp Course' dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
@@
 also be done through GitHub's online editor and through git locally but these methods do not allow for automatic content
-previewing.
+viewing.
 
-DataCamp courses can contain 3 different types of exercises: Normal, Multiple choice, and video.
+DataCamp courses may contain 3 different types of exercises: Normal, Multiple choice, and video.
 

### 2017-08-29 manuscript.tex

@@
 create their own courses that coincide with their lessons and students can access the course without having to install R.
-Courses are available through the DataCamp website so students can access the lesson through their web-browser on their laptop,
-tablet, or moble device. 
+Courses are available through the DataCamp website and students can access the lesson through their web-browser on their laptop,
+tablet or moble device, making the courses accessable to anyone with an internet connection. 
 The DataCamp website offers pre-existing free community courses and specialized 'Premium' classes that you need to purchase. 
@@
 'Quantitative Risk Management in R' so novice through advanced programming students will benefit.
+DataCamp can be used in the classroom in a number of ways: as traditional homework assignments, as an
+activity during lab periods, as pre-class assignments for a flipped classroom, and even as a test or assessment tool.
 
@@
 for an exercise it will motivate them to meet their personal achievement goals. \citep{Chang2016}.
-
-DataCamp can be used in the classroom in a number of ways: as traditional homework assignments, as an
-activity during lab periods, as pre-class assignments for a flipped classroom, and even as a test or assessment tool.
 
@@
 
+When starting to create a DataCamp course, it is helpful to view code from pre-existing community courses which can be found on GitHub.
+You can use these files as a guide to build your own course or duplicate the repository and tailor the content to fit specific needs.
+The DataCamp github repository contains links to the code for available courses; one of the most helpful when starting to build a course 
+is 'datacamp/courses-intro-r' which contains the source files for the 'Intoduction to R' course.
+
+- 'datacamp/testwhat' to help with submission correctness tests
+
 DataCamp courses may contain 3 different types of exercises: Normal, Multiple choice, and video.
@@
 are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. DataCamp provides a helpful
-R package called 'testwhat' which acts as a guide to writing the SCTs. 'testwhat' contains functions that can test different types of problems including
-loops, object definitions, printed output, functions, ect (datacamp website), this submission correctness testing code compares the ideal answer (from the 
-solution) to the students answer. Different arguements can be added to the test functions to alter the testing process and automatic feedback.
+R package called 'testwhat' which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub repository: 'datacamp/testwhat'). 
+'testwhat' contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect 
+(datacamp website), this submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
+arguements can be added to the test functions to alter the testing process and automatic feedback.
 
@@
 portion of the exercise and offer solutions in the 'Insruction' section. Like the 'normal' coding exercises, the lesson, instructions, pre-exercise code and
-SCTs have to be specified but sample and solution code do not. There are two types of multiple choice questions, simple and regular. The simple multiple 
+SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions, simple and regular. The simple multiple 
 choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises allow instructors to pre

### 2017-08-29 manuscript.tex
edit

@@
 create their own courses that coincide with their lessons and students can access the course without having to install R.
-Courses are available through the DataCamp website and students can access the lesson through their web-browser on their laptop,
+Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
 tablet or moble device, making the courses accessable to anyone with an internet connection. 
@@
 
-- 'datacamp/testwhat' to help with submission correctness tests
-
 DataCamp courses may contain 3 different types of exercises: Normal, Multiple choice, and video.
@@
 receive immediate feedback on what they are doing wrong and the system will guide them to the right answer. Instructors can use the default feedback
-that DataCamp automatically generates or write their own custom messages. The default feedback is meaningful and specific; most of the time custom messages
-are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. DataCamp provides a helpful
-R package called 'testwhat' which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub repository: 'datacamp/testwhat'). 
+that DataCamp automatically generates or write their own custom messages. The default feedback is meaningful and specific; most of the time custom 
+messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
+DataCamp provides a helpful R package called 'testwhat' which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
+repository: 'datacamp/testwhat'). 
 'testwhat' contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect 
@@
 
-**add an example of a test_function sct
+%add an example of a test_function sct
 
@@
 the code that solves the tasks in the instructions. If students are not able to complete the task without help, they can click
-on the 'Hint' button or eventually the 'solution'. When the student clicks the 'Submit Code' button, their answer passes through the SCT code where the
-code is checked for errors.
+on the 'Hint' button or eventually the 'solution'. When the student clicks the 'Submit Code' button, their answer passes through the SCT code where 
+the code is checked for errors.
 
-**add example of a normal coding exercise
+%add example of a normal coding exercise
 
 The 'MultipleChoiceExercise', as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson'
-portion of the exercise and offer solutions in the 'Insruction' section. Like the 'normal' coding exercises, the lesson, instructions, pre-exercise code and
-SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions, simple and regular. The simple multiple 
-choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises allow instructors to pre
--program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises are straightforward to write can 
-act as quick checks for understanding throughout the chapter.
+portion of the exercise and offer solutions in the 'Insruction' section. Like the 'normal' coding exercises, the lesson, instructions, pre-exercise 
+code and SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions, simple and regular. 
+The simple multiple choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises 
+allow instructors to pre-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises 
+are straightforward to write can act as quick checks for understanding throughout the chapter.
 
-**add example of regular multiple choice exercise
+%add example of regular multiple choice exercise
 
-Video exercises act as in instructional video addition to a DataCamp course; instructors can add short videos of them explaining concepts and with relevent slides that appear in the background.
-The DataCamp website \url{https://www.datacamp.com/teach/documentation#tab_code_exercises} provides more detail on the content of the various exercises.
+Video exercises act as in instructional video addition to a DataCamp course; instructors can add short videos of them explaining concepts and with 
+relevent slides that appear in the background. The DataCamp website \url{https://www.datacamp.com/teach/documentation#tab_code_exercises} provides 
+more detail on the content of the various exercises.
 

### 2017-08-31 manuscript.tex

@@
 capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
-interpreting real data sets \citep{Chance2007}, giving them an authentic view of how statistics is practiced outside of the
-classroom \citep{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
+interpreting real data sets \cite{Chance2007}, giving them an authentic view of how statistics is practiced outside of the
+classroom \cite{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
 (GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
@@
 The goal for any introductory statistics course is to help students develope the ability to think statistically
-\citep{AmericanStatisticalAssociation2016}.
+\cite{AmericanStatisticalAssociation2016}.
 Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
 variability, randomness and hypothesis testing. Although numerous statistical technologies exist, \textit{R} and \textit{R Studio}
-provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \citep{Chance2007}. R
+provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \cite{Chance2007}. R
 allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
-an interest in the domain of statistics \citep{Wang2017}.
+an interest in the domain of statistics \cite{Wang2017}.
 
@@
 contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own
-lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \citep{Carchedi2014}.
+lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \cite{Carchedi2014}.
 While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, this is not avaiblable for the classroom
@@
 the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with
-software than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
+software than the statistical concepts themselves \cite{Hare2017}. When students only need their web browser to participate,
 all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.
@@
 learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality
-\citep{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
+\cite{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
 these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions

### 2017-09-01 manuscript.tex
edited library
added example

@@
-\documentclass{tise_style}
-\usepackage{natbib}
+%\documentclass{tise_style}
+%\usepackage{natbib}
 %Having trouble getting tise_style to compile correctly in RStudio, will re-run it with this before submission
@@
 %Substitute this all with tise_style
-%\documentclass[12pt]{article}
-%\usepackage{natbib}  % used for citations
-%\usepackage[parfill]{parskip} %used for formatting style of text
-%\usepackage{url}
-
+\documentclass[12pt]{article}
+\usepackage{natbib}  % used for citations
+\usepackage[parfill]{parskip} %used for formatting style of text
+\usepackage{url}
+\usepackage{graphicx}
 % Sets margins to 1 in
@@
 
+Questions: 
+1) should i add more about how it can be used in a flipped classroom?
+
 It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
-unfold, the use of statistical software has become increasingly emphasized in education. By integrating the
+unfold, the use of statistical software has become increasingly emphasized in education (**do i need to cite this**). By integrating the
 capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
-interpreting real data sets \cite{Chance2007}, giving them an authentic view of how statistics is practiced outside of the
+interpreting real data sets \cite{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
 classroom \cite{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
 (GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
-to use technology "as a way to explore conceptual ideas and enhance student learning" (AmericanStatisticalAssociation2016).
+to use technology "as a way to explore conceptual ideas and enhance student learning" \cite{AmericanStatisticalAssociation2016}.
 
@@
 
-With this increased use of R in classrooms, there is a need for an effective way to get students familiar with R. While R
+With this increased use of R in classrooms, there is a need for an effective way to get students familiar with R \cite{Baumer2014}. While R
 software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition
@@
 DataCamp Course' dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
-make through DataCamp will update the GitHub repository and visa versa. The GitHub repository will contain three files:
-README.md, course.yml, and chapter1.Rmd.
+make through DataCamp will update the GitHub repository and visa versa. Every DataCamp course is linked through GitHub version control,
+allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
+on GitHub and under 'Settings' you can select the 'Collabroators' tab and enter the usernames of people you want to collaborate with.
+
+The GitHub repository will contain three files: README.md, course.yml, and chapter1.Rmd.
 Readme.md contains helpful information of how to get started, citing resourses to learn more about the process.
@@
 
-The submission correctness testing code (or SCT) is the backbone for DataCamp's interactive nature. If a student submits an incorrect answer, they will 
+The submission correctness testing code (or SCT) is the backbone for DataCamps' interactive nature. If a student submits an incorrect answer, they will 
 receive immediate feedback on what they are doing wrong and the system will guide them to the right answer. Instructors can use the default feedback
@@
 %add example of a normal coding exercise
+
+\begin{figure}
+  \includegrpahics[width = \linewidth] {preview.jpg}
+\end{figure}
 

### 2017-09-06 manuscript.tex
added image
Added to 'how-to' section (tips/explanation of exercise headers)

@@
 Questions:
+
 1) should i add more about how it can be used in a flipped classroom?
+
+2) how to get side by side pictures (for the teach editor code vs. preview)?
+
+3) also, what is the best way to add pictures? They are not inserted in the pdf where i have the code
+
+4) what are the bottom comments about the citations?
 
@@
 
-With this increased use of R in classrooms, there is a need for an effective way to get students familiar with R \cite{Baumer2014}. While R
-software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate this transition
-to R programming, popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR
-and TryR. These tools
-allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an
+With this increased use of R in classrooms, there is a need for an effective way to get students familiar with statistical software
+\cite{Baumer2014}. While Rsoftware provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate
+this transition to R programming, popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR
+and TryR. 
+These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an
 open source R software package that allows students to learn R programing in their R console. This interactive learning tool
@@
 lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \cite{Carchedi2014}.
-While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, this is not avaiblable for the classroom
-learning management systems (LMS).
+While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, integration of learning management 
+systems (LMS) is not available for the classroom.
 
@@
 tablet or moble device, making the courses accessable to anyone with an internet connection. 
-The DataCamp website offers pre-existing free community courses and specialized 'Premium' classes that you need to purchase. 
+The DataCamp website offers pre-existing free community courses as well as specialized 'Premium' classes that you need to purchase. 
 However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
 Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
-'community' courses and assign a course that they've created for the particular class.
+'community' courses or assign a course that they've created for the particular class.
 
@@
 \subsection{Creating a DataCamp Course}
-To create a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} and
-also a GitHub account. The simplest way to begin building the course is to use the templete course files from the 'Create
+To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} and
+a GitHub account \url{https://github.com}. The simplest way to begin building the course is to use the templete course files from the 'Create
 DataCamp Course' dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
@@
 
+When starting to create a DataCamp course, it is helpful to view code from pre-existing community courses which can be found on GitHub.
+You can use these files as a guide to build your own course or duplicate the repository and tailor the content to fit specific needs.
+The DataCamp github repository contains links to the code for available courses; one of the most helpful when starting to build a course 
+is 'datacamp/courses-intro-r' which contains the source files for the 'Intoduction to R' course.
+
 Educators are able to edit their courses in a number of ways but the 'Teach Editor' located in the teach dashboard is the
@@
 viewing.
-
-When starting to create a DataCamp course, it is helpful to view code from pre-existing community courses which can be found on GitHub.
-You can use these files as a guide to build your own course or duplicate the repository and tailor the content to fit specific needs.
-The DataCamp github repository contains links to the code for available courses; one of the most helpful when starting to build a course 
-is 'datacamp/courses-intro-r' which contains the source files for the 'Intoduction to R' course.
 
@@
 
-The submission correctness testing code (or SCT) is the backbone for DataCamps' interactive nature. If a student submits an incorrect answer, they will 
-receive immediate feedback on what they are doing wrong and the system will guide them to the right answer. Instructors can use the default feedback
-that DataCamp automatically generates or write their own custom messages. The default feedback is meaningful and specific; most of the time custom 
-messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
-DataCamp provides a helpful R package called 'testwhat' which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
-repository: 'datacamp/testwhat'). 
-'testwhat' contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect 
-(datacamp website), this submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
-arguements can be added to the test functions to alter the testing process and automatic feedback.
+\begin{figure}[h]
+  \includegraphics[scale = 0.2] {edit.jpg}
+\end{figure}
 
-%add an example of a test_function sct
+\begin{figure}[h]
+  \includegraphics[scale = 0.19] {preview.jpg}
+\end{figure}
+
+Whenever a new exercise is added, DataCamp automatically produces the top line in the editor. The header specifies the type
+of exercise (type), language (lang), available points (xp), skills learned (skills) and a 'key'. The key acts as a unique
+identifier for that exercise, allowing you to modify the content without losing any student data. Currenly, DataCamp offers
+eight different skills which are defined by numbers 1-8. The skills and their corresponding numbers can be found in the DataCamp
+documentation \url{https://www.datacamp.com/teach/documentation#tab_gamification}. 
+In the above exercise code, the 'type' is Normal, the language is R, the available points is 100 and the skills learned is 1 (which 
+corresponds to *R Programming*. DataCamp assigns 100 points to normal coding exercises but this value can be modified depending on
+difficulty level. After students have completed the exercise, they can check their personal profile to see how many points they earned.
 
@@
 the code that solves the tasks in the instructions. If students are not able to complete the task without help, they can click
-on the 'Hint' button or eventually the 'solution'. When the student clicks the 'Submit Code' button, their answer passes through the SCT code where 
-the code is checked for errors.
+on the 'Hint' button or eventually the 'solution'. When the student clicks the 'Submit Code' button, their answer passes through
+the SCT code where the code is checked for errors.
 
-%add example of a normal coding exercise
+The submission correctness testing code (or SCT) is the backbone for DataCamps' interactive nature. If a student submits an incorrect answer, they will 
+receive immediate feedback on what they are doing wrong and the system will guide them to the right answer. Instructors can use the default feedback
+that DataCamp automatically generates or write their own custom messages. The default feedback is meaningful and specific; most of the time custom 
+messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
+DataCamp provides a helpful R package called 'testwhat' which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
+repository: \url{https://github.com/datacamp/testwhat/wiki}. 
+'testwhat' contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect.
+The submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
+arguements can be added to the test functions to alter the testing process and automatic feedback. (**do I cite datacamp website here?**)
 
-\begin{figure}
-  \includegrpahics[width = \linewidth] {preview.jpg}
-\end{figure}
+%add an example of a test_function sct.... maybe plot
 
 The 'MultipleChoiceExercise', as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson'
-portion of the exercise and offer solutions in the 'Insruction' section. Like the 'normal' coding exercises, the lesson, instructions, pre-exercise 
-code and SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions, simple and regular. 
+portion of the exercise and offer solutions in the 'Insructions' section. Similar to the 'normal' coding exercises, the lesson, instructions, pre-exercise 
+code and SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions: simple and regular. 
 The simple multiple choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises 
@@
 
-%add example of regular multiple choice exercise
+%add example of regular multiple choice exercise --> use Quick check 2 from lab 8
 
@@
 more detail on the content of the various exercises.
+
+All DataCamp courses will have a course badge and most will use data sets and R packages. Information on how to add data sets and images
+can be found in DataCamps 'Teach' documentation \url{https://www.datacamp.com/teach/documentation} under the 'Upload Assets' tab. However,
+there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
+in the GitHub course repository named 'requirements.r'. The file should contain: $devtools::install_version$, package name and version for every
+package you use in the DataCamp course. For example, following code will add the 'ggplot2' and 'mosaic' packages to the repository.
+
+$$devtools::install_version("ggplot2", "2.2.0")$$
+$$devtools::install_version("mosaic", "0.14.4")$$
+
+In order for DataCamp to recognize this new file, you will need to add $$from: r-base-prod:27$$ to the course.yml file.
+
+**How do I override the subscripts for devtools?**
 
@@
 \bibliographystyle{Chicago}
-\bibliography{library}
+\bibliography{TISE-DataCamp(Private Group)}
+% before it was 'library' so I thought if I changed it to the new bib file it would work but it doesn't :(
 

### 2017-09-10 manuscript.tex
added question

@@
 
+5) should i add that the courses are written in Hadley Wickham style?
+
 It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
@@
 \cite{Baumer2014}. While Rsoftware provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate
-this transition to R programming, popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR
-and TryR. 
+this transition to R programming, popular interactive teaching technologies have been created including Swirl (**need to cite this?
+if so what should i cite**), LearnR and TryR. 
 These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an
@@
 
+Try R website --> \url{http://tryr.codeschool.com} i dont know how to cite this with mendeley
 TryR (Code School 2014) is a web-based programs and does not have this reproducible capability. Since public content authoring
@@
 
-DataCamp has the same reproducable capabilities as Swirl but is a web-based application; educators can
+The purpose of this paper is to introduce a relatively new interactive teaching tool, DataCamp, which incorporates only the best
+qualities from the tools mentioned above.
+
+DataCamp has the same reproducable capabilities as swirl but is a web-based application; educators can
 create their own courses that coincide with their lessons and students can access the course without having to install R.

### 2017-09-11 manuscript.tex
edited intro

@@
 
-The purpose of this paper is to introduce a relatively new interactive teaching tool, DataCamp, which incorporates only the best
-qualities from the tools mentioned above.
+The purpose of this article is to introduce a relatively new technology, DataCamp, which incorporates the best
+qualities from the teaching tools mentioned above.
 
@@
 
+\begin{verbatim}
+--- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1 key:9707072219
+## Quick check 2
+
+What can R be used for?
+
+*** =instructions
+- Graphing data
+- Analyzing data
+- Calculations
+- All of the above
+
+*** =hint
+R software can be used for all of these things.
+
+*** =pre_exercise_code
+```{r}
+
+```
+
+*** =sct
+```{r}
+
+msg_bad <- "That is not correct"
+msg_success <- "Exactly! R can do all of these things."
+test_mc(correct = 4, feedback_msgs = c(msg_bad, msg_bad, msg_bad, msg_success))
+```
+
+\end{verbatim}
+
 \begin{figure}[h]
@@
 there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
-in the GitHub course repository named 'requirements.r'. The file should contain: $devtools::install_version$, package name and version for every
-package you use in the DataCamp course. For example, following code will add the 'ggplot2' and 'mosaic' packages to the repository.
+in the GitHub course repository named \texttt{requirements.r}. The file should contain: \texttt{devtools::install\_version}, package name and version for every
+package you use in the DataCamp course. For example, following code will add the \texttt{ggplot2} and \texttt{mosaic} packages to the repository.
 
-$$devtools::install_version("ggplot2", "2.2.0")$$
-$$devtools::install_version("mosaic", "0.14.4")$$
-
-In order for DataCamp to recognize this new file, you will need to add $$from: r-base-prod:27$$ to the course.yml file.
+\begin{verbatim}
+devtools::install_version("ggplot2", "2.2.0")
+devtools::install_version("mosaic", "0.14.4")
+\end{verbatim}
+In order for `DataCamp' to recognize this new file, you will need to add $$from: r-base-prod:27$$ to the course.yml file.
 

### 2017-09-13 manuscript.tex
edit intro

@@
 interpreting real data sets \cite{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
-classroom \cite{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
+classroom \citet{wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
 (GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
@@
 \bibliographystyle{Chicago}
-\bibliography{TISE-DataCamp(Private Group)}
+\bibliography{library}
 % before it was 'library' so I thought if I changed it to the new bib file it would work but it doesn't :(

### 2017-09-13 manuscript.tex
changed code words/phrases to text-mode

@@
 
-1) should i add more about how it can be used in a flipped classroom?
+1) should i add more about how it can be used in a flipped classroom
 
-2) how to get side by side pictures (for the teach editor code vs. preview)?
-
-3) also, what is the best way to add pictures? They are not inserted in the pdf where i have the code
-
-4) what are the bottom comments about the citations?
-
-5) should i add that the courses are written in Hadley Wickham style?
+2) should i add that the courses are written in Hadley Wickham style?
+  - yes one sentence
 
@@
 interpreting real data sets \cite{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
-classroom \citet{wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
+classroom \citet{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
 (GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
@@
 Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
-variability, randomness and hypothesis testing. Although numerous statistical technologies exist, \textit{R} and \textit{R Studio}
+variability, randomness and hypothesis testing. Although numerous statistical technologies exist, R and R Studio
 provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \cite{Chance2007}. R
@@
 \cite{Baumer2014}. While Rsoftware provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate
-this transition to R programming, popular interactive teaching technologies have been created including Swirl (**need to cite this?
+this transition to R programming, popular interactive teaching technologies have been created including swirl (**need to cite this?
 if so what should i cite**), LearnR and TryR. 
-These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an
+These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. swirl is an
 open source R software package that allows students to learn R programing in their R console. This interactive learning tool
-contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own
-lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \cite{Carchedi2014}.
+contains several pre-existing lessons but what makes swirl so popular is its versitality; educators can also create their own
+lesson to fit the curriculum and assign it to students \cite{Carchedi2014}.
 While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, integration of learning management 
@@
 
-Try R website --> \url{http://tryr.codeschool.com} i dont know how to cite this with mendeley
-TryR (Code School 2014) is a web-based programs and does not have this reproducible capability. Since public content authoring
+*Try R website  \url{http://tryr.codeschool.com} i dont know how to cite this with mendeley*
+
+TryR (Code School 2014) is a web-based program and does not have swirls reproducible capability. Since public content authoring
 is not available, educators are limited on what they can teach their students. The R console can be intimidating to
@@
 Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
-'community' courses or assign a course that they've created for the particular class.
+\textit{community} courses or assign a course that they've created for the particular class.
 
-The collection of community courses avaiable at DataCamp inlcude a wide range of topics from 'Introduction to R' to
-'Quantitative Risk Management in R' so novice through advanced programming students will benefit.
+The collection of community courses avaiable at DataCamp inlcude a wide range of topics from \textit{Introduction to R} to
+\textit{Quantitative Risk Management in R} so novice through advanced programming students will benefit.
 DataCamp can be used in the classroom in a number of ways: as traditional homework assignments, as an
@@
 can set deadlines for assignments and easily see not only when students complete an assignment but also which sections the
-students had trouble with in a detailed report (datacamp/teach website). Student scores can be automatically updated to a
+students had trouble with in a detailed report (cite datacamp/teach website?). Student scores can be automatically updated to a
 current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration of student work.
@@
 \subsection{Pre-existing R courses}
-DataCamp has a range of available free community courses that educators can utilize for supplimental R practice.
+DataCamp has a range of available courses that educators can use as supplimental R practice. In order to utilize 
+DataCamp's \textit{classroom} benefits, you will first need to create an academic group on the website \url{https://www.datacamp.com/groups/education}.
+After your university information has been verified and the classroom account has been approved, you can add students by their university
+email address on the \textit{Members} tab and link the account to your LMS.
 
@@
 
-The GitHub repository will contain three files: README.md, course.yml, and chapter1.Rmd.
-Readme.md contains helpful information of how to get started, citing resourses to learn more about the process.
-course.yml is a file that contains general information about the course you're creating: title, university, description,
+The GitHub repository will contain three files: \texttt{README.md}, \texttt{course.yml}, and \texttt{chapter1.Rmd}.
+\texttt{Readme.md} contains helpful information of how to get started, citing resourses to learn more about the process.
+\texttt{course.yml} is a file that contains general information about the course you're creating: title, university, description,
 difficulty level, ect.
-chapter1.Rmd is a template chapter file with examples of 'normal' interative coding exercises and multiple choice questions.
-To add more chapters to an R course, create new files in the repository and name them chapter1.Rmd, chapter2.Rmd, chapter3.Rmd
-ect.
+\texttt{chapter1.Rmd} is a template chapter file with examples of 'normal' interative coding exercises and multiple choice questions.
+To add more chapters to an R course, create new files in the repository and name them \texttt{chapter1.Rmd}, \texttt{chapter2.Rmd},
+\texttt{chapter3.Rmd}, ect.
 
@@
 mode) only includes the lesson, Instructions, R script panel and a R console panel.
-
-\begin{figure}[h]
-  \includegraphics[scale = 0.2] {edit.jpg}
-\end{figure}
 

### 2017-09-19 research_slides.tex
started presentation outline

\documentclass{beamer}

\usepackage[utf8]{inputenc}

%Information to be included in the title page:
\title{Creating DataCamp courses}
\subtitle{An interactive teaching tool}
\author{Tessa McDonnel}
\institute{Cal Poly San Luis Obispo}
\date{}

\begin{document}

\frame{\titlepage}

\begin{frame}
\frametitle{questions for Pileggi}

1) Should I be talking about using Git/LaTeX/Mendeley? mainly git

2) Am i focusing on what I actually did (installed software, went throug labs, wrote accompaning datacamp course)? or like what im writing for the article?

\end{frame}

\begin{frame}
\frametitle{Purpose of reasearch project}

This summer I worked with Dr. Pileggi and improved upon the STAT 217 labs in R by creating
a supplimental online DataCamp course that accompanies the labs.

\begin{itemize}
 \item<1-> Technology plays a huge role in statistics, and even introductory statistics courses are utilizing statistical software.
 \item<2-> Non-statistics major students have a lot of trouble with R because they've never seen anything like it.
 \item<3-> The previous STAT 217 pre-labs consisted of a lab manual and video. \textbf{Should i add more about previous pre-labs?}
 \item<4-> My job this summer was to convert the previous lab materials to an interactive online R programming course
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{What is DataCamp?}
\begin{itemize}
 \item<1-> interactive leaning tool; receive instant personalized feedback
 \item<2-> DataCamp is a web-based application, only need a web browser to access courses (no R installation required)- can be very helpful for intro stats 
 \item<3-> Similar to swirl, educators can create their own DataCamp courses or utilize the free existing courses 
 \item<4-> Free for academic groups 
 \item<5-> DataCamp can be linked to learning management systems, easy to track student progress
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Step One}

Work through all of the existing lab assignments, this includes reading lab manuals, watching videos, taking quiz's and completing the actual lab assignment.
\begin{itemize}
 \item<1-> 
 \item<2-> 
 \item<3-> 
 \item<4-> 
\end{itemize}

\end{frame}

\begin{frame}

Slide showing the code for a coding example with a data set and it's corresponding preview

\end{frame}
\end{document}

### 2017-09-23 research_slides.tex
added questions/slides

@@
 \usepackage[utf8]{inputenc}
-
+\usepackage{hyperref} 
+\usepackage{url}
 %Information to be included in the title page:
@@
 
-1) Should I be talking about using Git/LaTeX/Mendeley? mainly git
+1) For the slide `Creating DataCamp Course', how can I show the Step 1 bullets first, then the step 2?
+Right now it is showing the first point in both, then second, ect.
 
-2) Am i focusing on what I actually did (installed software, went throug labs, wrote accompaning datacamp course)? or like what im writing for the article?
+2) I'm looking through the DataCamp course and finding a good exercise to show in the presentation but I'm seeing a lot of 
+errors... The subscripts for hypotheses are not working anymore (at least when I view the course).
 
+3) Should I say `R coding' or `R programming' or just `R'
 \end{frame}
@@
 \begin{itemize}
- \item<1-> Technology plays a huge role in statistics, and even introductory statistics courses are utilizing statistical software.
- \item<2-> Non-statistics major students have a lot of trouble with R because they've never seen anything like it.
- \item<3-> The previous STAT 217 pre-labs consisted of a lab manual and video. \textbf{Should i add more about previous pre-labs?}
- \item<4-> My job this summer was to convert the previous lab materials to an interactive online R programming course
+ \item<1-> Technology plays a huge role in statistics education.
+ \item<2-> Non-statistics major students have a lot of trouble with statistical software.
+ \item<3-> The previous STAT 217 pre-labs consisted of a lab manual and video tutorial.
+ \item<4-> My job this summer was to convert the previous lab materials to an interactive online R programming course.
 \end{itemize}
@@
  \item<1-> interactive leaning tool; receive instant personalized feedback
- \item<2-> DataCamp is a web-based application, only need a web browser to access courses (no R installation required)- can be very helpful for intro stats 
- \item<3-> Similar to swirl, educators can create their own DataCamp courses or utilize the free existing courses 
+ \item<2-> Similar to swirl, educators can create their own DataCamp courses or utilize the free existing courses 
+ \item<3-> DataCamp is a web-based application, only need a web browser to access courses (no R installation required)- can be very helpful for intro stats 
  \item<4-> Free for academic groups 
@@
 \begin{frame}
-\frametitle{Step One}
+\frametitle{Creating DataCamp Course}
+\textbf{Step 1: Review}
+For each of the 8 labs, I took notes of:
+\begin{itemize}
+ \item<1-> Statistical concepts used
+ \item<2-> R commands used 
+ \item<3-> What kind of data set and variable types were used
+\end{itemize}
+\textbf{Step 2: Create}
+To convert the existing labs into an online course:
+\begin{itemize}
+  \item<1-> completed a few existing courses on DataCamp 
+  \item<2-> read through all of the DataCamp documentation
+  \item<3-> started building the course
+\end{itemize}
+\end{frame}
 
-Work through all of the existing lab assignments, this includes reading lab manuals, watching videos, taking quiz's and completing the actual lab assignment.
-\begin{itemize}
- \item<1-> 
- \item<2-> 
- \item<3-> 
- \item<4-> 
-\end{itemize}
+\begin{frame}
+Exercise code and preview mode from a Lab: demonstrate the interactive ability of DataCamp.
+(thinking maybe the arithemic slides?
+I want to use a later lab but I'm not happy with any of the exercises so I'd want to edit them and add more in depth error messages.)
+
+\textbf{Insert url to the DataCamp course page}
 
@@
 \begin{frame}
+\frametitle{New Tools}
+\begin{block}{Tools Used for Learning}
+PolyLearn
 
-Slide showing the code for a coding example with a data set and it's corresponding preview
+DataCamp
+\end{block}
+\begin{block}{Tools Used for creating course}
+GitHub
 
+DataCamp
+\end{block}
+\begin{block}{Tools Used For Paper}
+Mendeley
+
+LaTeX
+\end{block}
 \end{frame}

### 2017-09-25 manuscript.tex

@@
 
+3) were you going to set something up on here that i was going to fill in? Oh the R code boxes where I can add the DataCamp edit code
 It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
@@
 capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
-interpreting real data sets \cite{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
-classroom \citet{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
+interpreting real data sets \citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
+classroom \citep{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
 (GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
-to use technology "as a way to explore conceptual ideas and enhance student learning" \cite{AmericanStatisticalAssociation2016}.
+to use technology "as a way to explore conceptual ideas and enhance student learning" \citep{AmericanStatisticalAssociation2016}.
 
@@
 there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
-in the GitHub course repository named \texttt{requirements.r}. The file should contain: \texttt{devtools::install\_version}, package name and version for every
-package you use in the DataCamp course. For example, following code will add the \texttt{ggplot2} and \texttt{mosaic} packages to the repository.
+in the GitHub course repository named \texttt{requirements.r}. The file should contain: \texttt{devtools::install\_version}, package name and version for 
+every package you use in the DataCamp course. For example, following code will add the \texttt{ggplot2} and \texttt{mosaic} packages to the repository.
 
@@
 \end{verbatim}
-In order for `DataCamp' to recognize this new file, you will need to add $$from: r-base-prod:27$$ to the course.yml file.
-
-**How do I override the subscripts for devtools?**
+In order for DataCamp to recognize this new file, you will need to add \texttt{from: r-base-prod:27} to the \texttt{course.yml} file.
 
@@
 %\bibliographystyle{ECA_jasa}
-\bibliographystyle{Chicago}
+\bibliographystyle{ECA_jasa}
 \bibliography{library}

### 2017-09-27 Integration notes.Rmd
added textbox and captioning for code

---
title: "Class set up notes"
author: "Shannon Pileggi"
date: "September 10, 2017"
output: html_document
---

+ Allow DataCamp one week to set up your group

+ Invite students by email addresses, separated by space or comma VERSUS using the LMS integration.  Only do one or the other?  Instructions sufficient to set up, relatively quick for first time.

+ Then assign students either an entire course or a chapter in a course, and set the deadline.  DataCamp sends an email notification of assignment.

+ Assignment and Courses section - what is the difference?  A bit confusing.  If I want to assign weekly chapters should the entire course also be assigned?

+ does integration duplicate assigments?

+ grader role difficulty using link

### 2017-09-27 manuscript.tex
added textbox and captioning for code

@@
 \usepackage{graphicx}
+\usepackage{setspace}
+\usepackage{fancyvrb}
 % Sets margins to 1 in
@@
 
+\doublespacing
+
 Questions:
@@
 3) were you going to set something up on here that i was going to fill in? Oh the R code boxes where I can add the DataCamp edit code
+
 It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
@@
 
-\begin{verbatim}
+\begin{figure}
+\caption{This code does this}
+\begin{Verbatim}[frame=single]
 --- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1 key:9707072219
@@
 ```
-
-\end{verbatim}
+\end{Verbatim}
+\end{figure}
 
@@
 %\bibliographystyle{ECA_jasa}
-\bibliographystyle{ECA_jasa}
+\bibliographystyle{plainnat}
 \bibliography{library}

### 2017-10-04 Presentation_notes.Rmd
presentation slides (+ notes on what I'm going to say)

---
title: "DataCamp Presentation Notes"
output: html_notebook
---

### Purpose of Research project slide

It is no suprise that technology plays a huge role in statistics and education. Even introductory courses 
are utilizing statistical software like R.

Non-statistics major students (like those in STAT 217) have a lot of trouble with R because they've never seen anything like it.

In my first statistics class at cal poly (STAT 150) we were intoduced to R and I remember feeling very intimidated.

I was happy to be chosen for this project because I understand student difficulties and wanted to help make the transition to coding easier for them.

The stat 217 class has a lab assignment every week that requires students to use R.
Dr. Pileggi's old pre-lab materials consisted of a lab manual and video tutorial demonstrating the R commands that would be used in the lab assignment. 
To prepare for the R coding in the lab, students would review these materials then take a short quiz.

The tutorials covered all bases but watching videos is a passive activity so students would still have trouble on the lab assignments.

And that is where I come in. My job this summer was to convert the old (passive) pre-lab activities to an interactive R programming course on a website called DataCamp. So instead of watching the tutorials, students will actively practive coding in R to prepare them for the lab assignments.

### What is DataCamp

I created the course on DataCamp, which is a website that provides online courses in programming languages, including R.

DataCamp is similar to swirl in a few ways:

Its an interactive teaching tool. When students submit their code and recieve instant feedback; if they get something wrong, different error messages will come up depending on what needs to be fixed.

It is also open source so educators can create their own lessons that coincide with their university course.

A big difference between swirl is that DataCamp is a web-based application so students don't need to install anything on their personal computers.

As long as you are a college professor you can create an academic group and all of the courses are free for students.

Also its really easy to track student progress because the datacamp course can be linked with LMS. So the course I created for Dr. Pileggi's STAT 217 class is linked to polylearn.
### Creating DataCamp course slide

###### Step 1: Review

The first step of the project was to work through all of the existing lab assignments, this includes reading lab manuals, 
watching videos, taking quiz's and completing the actual lab assignment. I took notes on the statistical concepts, syntax, and data types so that my online course would kind of mirror the previous lab content. This was a really cool part of the project because I was able to find other data sets for the DataCamp course that I thought were interesting and would be interesting for students.

###### Step 2: Practice

* Completed a few existing courses on DataCamp so I would get a better understanding of how the courses were set up.

###### Step 3: Create

* Then I read through all of the DataCamp documentation on creating a course.
* And finally I started the building process. This proved to be a huge learning curve; given that the DataCamp course is interactive, I spent
a lot of time predicting what students would get wrong then writing the corresponding error messages.

### Demonstration Slide

* For the sct's, this is the code that would compare the students answer to the solution so that the appropriate feedback would come up.

* Use Lab 5 exercise 2
  + Say that this is from Lab 5 which is all about one sample t-tests and the exercise is teaching the R code needed to check assumtions of the test.
  + Explain the parts of the page that I wrote and how that translated to what students see
  + Run the code only with the library command --> show the error message
  + Don't use correct syntax for favstats --> show error message
  + Click the get hint button then the show response button and submit
  + Read the success message outloud (this needs to be rewritten to include more info on assumptions)

### Tools
##### Learning
Used polylearn to re-learn introductory statistics material and I used the documentation on DataCamp to help build the course.

##### Building
For creating the course, I used GitHub which is a version control utility and every datacamp course is linked through GitHub so I was able to get some experience working with version control.

And I obviously used DataCamp - I mostly wrote the STAT 217 course on the DataCamp editing page.

##### Journal Article

This project has also led to an article that I am co-authoring for a statistics education journal. In the article we are introducing DataCamp as a new technology that other educators can ulilize for their own courses.

For this paper I use a reference management software called Mendeley which has helped with the citing references and writing the bibliography.

I'm also using LaTeX to write the article; LaTeX is a programming language used for typesetting documents. This summer was the first time I've used it but I really like it and this slideshow is actually written in LaTeX.

### Acknowledgement

And lastly, I'd like to thank Bill and Linda Frost for giving me this opportunity to take part in undergraduate research. It was an amazing experience.

### 2017-10-17 manuscript.tex
updated with figure labels
modified manuscript

@@
 
-1) should i add more about how it can be used in a flipped classroom
-
-2) should i add that the courses are written in Hadley Wickham style?
-  - yes one sentence
-
-3) were you going to set something up on here that i was going to fill in? Oh the R code boxes where I can add the DataCamp edit code
-
 It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
-unfold, the use of statistical software has become increasingly emphasized in education (**do i need to cite this**). By integrating the
-capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
+unfold, the use of statistical software has become increasingly emphasized in education \citep{AmericanStatisticalAssociation2016}. By integrating the
+capabilities of technology in statistics courses, students can explore fundamental concepts by analyzing and
 interpreting real data sets \citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
@@
 
-The goal for any introductory statistics course is to help students develope the ability to think statistically
-\cite{AmericanStatisticalAssociation2016}.
+The goal for any statistics course is to help students develop the ability to think statistically
+\citep{AmericanStatisticalAssociation2016}.
 Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
 variability, randomness and hypothesis testing. Although numerous statistical technologies exist, R and R Studio
-provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \cite{Chance2007}. R
+provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \citep{Chance2007}. R
 allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
-an interest in the domain of statistics \cite{Wang2017}.
+an interest in the domain of statistics \citep{Wang2017}.
 
 With this increased use of R in classrooms, there is a need for an effective way to get students familiar with statistical software
-\cite{Baumer2014}. While Rsoftware provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate
-this transition to R programming, popular interactive teaching technologies have been created including swirl (**need to cite this?
-if so what should i cite**), LearnR and TryR. 
+\citep{Baumer2014}. While R software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate
+this transition to R programming, popular interactive teaching technologies have been created including swirl (** need to cite package**), LearnR and TryR. 
 These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. swirl is an
@@
 contains several pre-existing lessons but what makes swirl so popular is its versitality; educators can also create their own
-lesson to fit the curriculum and assign it to students \cite{Carchedi2014}.
+lesson to fit the curriculum and assign it to students \citep{Carchedi2014}.
 While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, integration of learning management 
@@
 
-*I'm confused about LearnR and think someone else should write about it.*
+\textbf{Learn R section}
 
@@
 
-TryR (Code School 2014) is a web-based program and does not have swirls reproducible capability. Since public content authoring
+TryR (Code School 2014) is a web-based program but is not open source. Since public content authoring
 is not available, educators are limited on what they can teach their students. The R console can be intimidating to
-introductory statistics students so an advantage of a web-based teaching tool is
+new statistics students so an advantage of a web-based teaching tool is
 the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with
-software than the statistical concepts themselves \cite{Hare2017}. When students only need their web browser to participate,
+software than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
 all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.
@@
 tablet or moble device, making the courses accessable to anyone with an internet connection. 
-The DataCamp website offers pre-existing free community courses as well as specialized 'Premium' classes that you need to purchase. 
-However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
-Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
-\textit{community} courses or assign a course that they've created for the particular class.
+The DataCamp website offers pre-existing free community courses as well as specialized \textit{Premium} classes that you need to purchase. 
+However, when used for academic purposes the \textit{Premium} DataCamp content is also free for up to six months.
+Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign 
+\textit{community} courses, \textit{Premium} courses, and even a course that they've developed themselves. 
+The collection of \textit{community} courses available on DataCamp inlcude a wide range of topics from \textit{Introduction to R} to
+\textit{Quantitative Risk Management in R} so novice through advanced programming students benefit.
 
-The collection of community courses avaiable at DataCamp inlcude a wide range of topics from \textit{Introduction to R} to
-\textit{Quantitative Risk Management in R} so novice through advanced programming students will benefit.
 DataCamp can be used in the classroom in a number of ways: as traditional homework assignments, as an
@@
 can set deadlines for assignments and easily see not only when students complete an assignment but also which sections the
-students had trouble with in a detailed report (cite datacamp/teach website?). Student scores can be automatically updated to a
+students had trouble with in a detailed report (need to cite teach page of website). Student scores can be automatically updated to a
 current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration of student work.
 
-Each chapter in a DataCamp course is made up of modular exercises. Modulariy is critical component in designing a statistical
+Each chapter in a DataCamp course is made up of modular exercises. Modularity is critical component in designing a statistical
 learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality
-\cite{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
+\citep{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
 these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
@@
 defined again. Each of these exercises can be given a number of redeemable points which the students can see when they begin
-the exercise, introducing a gamification feature to the learning experience. If the student completes the exercise without
-any help they will recieve the full points. If they ask for a hint, 30 percent of the available points will be deducted and
-all of the points will be deducted if they ask for the entire answer. When in a classroom group, students can view their
+the exercise, introducing a gamification feature to the learning experience. If they ask for a hint, 30 percent of the available points are deducted;
+all points are deducted if they ask for the solution.  If the student completes the exercise without
+any help they will recieve the full points. When in a classroom group, students can view their
 progress (points and chapters completed) as well as then progress of their peers. This can help students perform better
 because they want to be on par with the rest of the class; furthermore, when students can see the number of available points
-for an exercise it will motivate them to meet their personal achievement goals. \citep{Chang2016}.
+for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}.
 
@@
 DataCamp has a range of available courses that educators can use as supplimental R practice. In order to utilize 
-DataCamp's \textit{classroom} benefits, you will first need to create an academic group on the website \url{https://www.datacamp.com/groups/education}.
+DataCamp's \textit{classroom} benefits, first create an academic group on the website \url{https://www.datacamp.com/groups/education}.
 After your university information has been verified and the classroom account has been approved, you can add students by their university
@@
 To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} and
-a GitHub account \url{https://github.com}. The simplest way to begin building the course is to use the templete course files from the 'Create
-DataCamp Course' dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
-make through DataCamp will update the GitHub repository and visa versa. Every DataCamp course is linked through GitHub version control,
+a GitHub account \url{https://github.com}. The simplest way to begin building the course is to use the template course files from the 
+\texttt{Create DataCamp Course} dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
+make through DataCamp will update the GitHub repository and vice versa. Every DataCamp course is linked through GitHub version control,
 allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
-on GitHub and under 'Settings' you can select the 'Collabroators' tab and enter the usernames of people you want to collaborate with.
+on GitHub and under \texttt{Settings} you can select the \texttt{Collabroators} tab and enter the user names of collaborators.
 
-The GitHub repository will contain three files: \texttt{README.md}, \texttt{course.yml}, and \texttt{chapter1.Rmd}.
+Newly created GitHub repositories will contain three files:
+
+1) \texttt{README.md}
+
+2) \texttt{course.yml}
+
+3) \texttt{chapter1.Rmd}
+
 \texttt{Readme.md} contains helpful information of how to get started, citing resourses to learn more about the process.
@@
 code, hint, solution and a submission correctness testing coded (SCT). However, the interface for students (or the 'Preview
-mode) only includes the lesson, Instructions, R script panel and a R console panel.
+mode) only includes the lesson, Instructions, R script panel and a R console panel (Figure~\ref{fig:code1}).
 
@@
 \end{Verbatim}
+\label{fig:code1}
 \end{figure}

### 2017-10-18 manuscript.tex
made edits, added SCT examples

@@
 
+How do I say that LaTeX is compatible with datacamp?
+
+I can't find the swirl package on mendeley so im not sure how to add that.
+
+How did the linking with LMS process go?
+
 It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
@@
 With this increased use of R in classrooms, there is a need for an effective way to get students familiar with statistical software
-\citep{Baumer2014}. While R software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate
+\citep{Baumer2014}. While R software provides users with extraordinary capabilities, there is no doubt a steep learning curve. To facilitate
 this transition to R programming, popular interactive teaching technologies have been created including swirl (** need to cite package**), LearnR and TryR. 
 These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. swirl is an
-open source R software package that allows students to learn R programing in their R console. This interactive learning tool
+open source R package that allows students to learn R programing in their R console. This interactive learning tool
 contains several pre-existing lessons but what makes swirl so popular is its versitality; educators can also create their own
@@
 DataCamp has the same reproducable capabilities as swirl but is a web-based application; educators can
-create their own courses that coincide with their lessons and students can access the course without having to install R.
+create their own courses that coincide with their lessons and students can access the course without installing R.
 Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
-tablet or moble device, making the courses accessable to anyone with an internet connection. 
+tablet or moble device, making the courses accessible to anyone with an internet connection. 
 The DataCamp website offers pre-existing free community courses as well as specialized \textit{Premium} classes that you need to purchase. 
@@
 are not cummulative; every exercise begins with a clear workspace so an object defined in a previous exercise needs to be
-defined again. Each of these exercises can be given a number of redeemable points which the students can see when they begin
-the exercise, introducing a gamification feature to the learning experience. If they ask for a hint, 30 percent of the available points are deducted;
-all points are deducted if they ask for the solution.  If the student completes the exercise without
+defined again.
+
+Each of these exercises can be given a number of redeemable points which the students can see when they begin
+the exercise, introducing a gamification feature to the learning experience. Students can view the exercise `hint' option and 30 percent
+of the available points are deducted; all points are deducted if they ask for the solution.  If the student completes the exercise without
 any help they will recieve the full points. When in a classroom group, students can view their
@@
 \subsection{Pre-existing R courses}
-DataCamp has a range of available courses that educators can use as supplimental R practice. In order to utilize 
+In order to utilize 
 DataCamp's \textit{classroom} benefits, first create an academic group on the website \url{https://www.datacamp.com/groups/education}.
-After your university information has been verified and the classroom account has been approved, you can add students by their university
-email address on the \textit{Members} tab and link the account to your LMS.
+After your university information has been verified and the classroom account has been approved, you can facilitate student access
+by either creating a group through the DataCamp website or linking directly to your LMS.
+
+(idk if this helps to say or is obvious) Add students by their university email address on the \textit{Members} tab and link the account to your LMS.)
 
@@
 allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
-on GitHub and under \texttt{Settings} you can select the \texttt{Collabroators} tab and enter the user names of collaborators.
+on GitHub and under \texttt{Settings} you can enter the user names of collaborators. Collaborators who are not the primary author need 
+to uncheck `My Courses' in order to view and contribute to the repository.
 
-Newly created GitHub repositories will contain three files:
+The newly created GitHub repositories will contain three files:
 
@@
 You can use these files as a guide to build your own course or duplicate the repository and tailor the content to fit specific needs.
-The DataCamp github repository contains links to the code for available courses; one of the most helpful when starting to build a course 
-is 'datacamp/courses-intro-r' which contains the source files for the 'Intoduction to R' course.
+The DataCamp github repository contains links to the code for several available courses; one of the most helpful when starting to build a course 
+is \url{https://github.com/datacamp/courses-intro-to-r} which contains the source files for the `Intoduction to R' course.
 
@@
 
-A 'NormalExercise' is an interactive coding exercise containing a lesson section, instructions, pre-exercise code, sample
-code, hint, solution and a submission correctness testing coded (SCT). However, the interface for students (or the 'Preview
+A \texttt{NormalExercise} is an exercise that prompts a user to submit code.
+The components of this include: lesson section, instructions, pre-exercise code, sample code, hint, solution and a submission correctness testing coded (SCT).
+However, the interface for students (or the 'Preview
 mode) only includes the lesson, Instructions, R script panel and a R console panel (Figure~\ref{fig:code1}).
@@
 \caption{This code does this}
-\begin{Verbatim}[frame=single]
+\begin{verbatim}[frame=single]
+--- type:NormalExercise lang:r xp:100 skills:1 key:9a4fea2da
+## Visualizing quantitative data in R
+
+We can visualize quantitative data with a *histogram*.
+
+To create a histogram in R, use the syntax:
+`hist(dataset$quant_var)`
+
+*** =instructions
+- Create a histogram of the `wage` variable from the 
+`CPS85` data set.
+*** =hint
+Follow the format from the lesson: `hist(dataset$variable)`
+with specified data set and variable.
+*** =pre_exercise_code
+```{r}
+library(mosaicData)
+```
+*** =sample_code
+```{r}
+# Create histogram of the wage variable
+```
+*** =solution
+```{r}
+# Create histogram of the wage variable 
+hist(CPS85$wage)
+```
+*** =sct
+```{r}
+test_function("hist", args = "x", incorrect_msg = 
+"Make sure you specify the `CPS85` data set
+and `wage` variable.")
+```
+
+\end{verbatim}
+\label{fig:code1}
+\end{figure}
+
+\begin{figure}[h]
+  \includegraphics[scale = 0.19] {preview.jpg}
+\end{figure}
+
+Whenever a new exercise is added, DataCamp automatically produces the top line in the editor. The header specifies the type
+of exercise \texttt{type}, language \texttt{lang}, available points \texttt{xp}, skills learned \texttt{skills} and a \texttt{key}. The key acts as a unique
+identifier for that exercise, allowing you to modify the content without losing any student data. Currently, DataCamp offers
+eight different skills which are defined by numbers 1-8. The skills and their corresponding numbers can be found in the DataCamp
+documentation \url{https://www.datacamp.com/teach/documentation#tab_gamification}. 
+In the above exercise code, the \texttt{type} is Normal, the language is R, the available points is 100 and the skills learned is 1 (which 
+corresponds to R Programming). DataCamp assigns 100 points to normal coding exercises but this value can be modified depending on
+difficulty level. After students have completed the exercise, they can check their personal profile to see how many points they earned.
+
+In the `Assignment' portion of the exercise, instructors can add additional information about the assignment that will help
+students understand and complete the instructions. The `Instructions' section contains the actual task the student is
+asked to execute; instructors can also include a `Hint' for extra guidence (optional). The 'pre-exercise code' sets up the workspace for 
+the student; this section will contain code to import data sets, install packages and any other operation that you want to be available to
+students. The 'sample code' section contains code or notes that students view in the R script panel. Students also use the R script panel to write
+the code that solves the tasks in the instructions. The correct answer to an exercise is coded in the 'solution' section
+and when the student clicks the `Submit Code' button, their answer passes through the SCT code where their code is checked for errors.
+
+The submission correctness testing code (or SCT) automatically assesses if the correct code was submitted. If a student submits an 
+incorrect answer, they will receive immediate feedback on what they are doing wrong and the system will guide them to the right answer.
+Instructors can use the default feedback that DataCamp automatically generates or write their own custom messages. For example, figure blank
+contains the default feedback for an incorrect submission of the \texttt{hist()} function.
+
+\begin{figure}
+\caption{This code does this}
+\begin{verbatim}[frame=single]
+
+Student:
+histogram(dataset$var_name)
+
+Default message:
+Have you called hist()?
+
+Student:
+hist(var_name)
+
+Default message:
+Check your call of hist(). Did you correctly specify 
+the argument x? Evaluating the expression you specified
+caused an error.
+
+Student:
+hist(dataset$misspelled_var)
+
+Default message:
+Check your call of hist(). Did you correctly specify the argument x? 
+It is a NULL, while it should be a numeric vector.
+
+\end{verbatim}
+\label{fig:code1}
+\end{figure}
+
+The default feedback is meaningful and specific; most of the time custom 
+messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
+DataCamp provides a helpful R package called 'testwhat' which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
+repository: \url{https://github.com/datacamp/testwhat/wiki}. 
+'testwhat' contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect.
+The submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
+arguements can be added to the test functions to alter the testing process and automatic feedback. (**do I cite datacamp website here?**)
+
+%add an example of a test_function sct.... maybe plot
+
+The \texttt{MultipleChoiceExercise}, as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson'
+portion of the exercise and offer solutions in the 'Insructions' section. Similar to the 'normal' coding exercises, the lesson, instructions, pre-exercise 
+code and SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions: simple and regular. 
+The simple multiple choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises 
+allow instructors to pre-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises 
+are straightforward to write can act as quick checks for understanding throughout the chapter.
+
+\begin{figure}
+\caption{This code does this}
+\begin{verbatim}[frame=single]
 --- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1 key:9707072219
@@
 ```
-\end{Verbatim}
+\end{verbatim}
 \label{fig:code1}
 \end{figure}
-
-\begin{figure}[h]
-  \includegraphics[scale = 0.19] {preview.jpg}
-\end{figure}
-
-Whenever a new exercise is added, DataCamp automatically produces the top line in the editor. The header specifies the type
-of exercise (type), language (lang), available points (xp), skills learned (skills) and a 'key'. The key acts as a unique
-identifier for that exercise, allowing you to modify the content without losing any student data. Currenly, DataCamp offers
-eight different skills which are defined by numbers 1-8. The skills and their corresponding numbers can be found in the DataCamp
-documentation \url{https://www.datacamp.com/teach/documentation#tab_gamification}. 
-In the above exercise code, the 'type' is Normal, the language is R, the available points is 100 and the skills learned is 1 (which 
-corresponds to *R Programming*. DataCamp assigns 100 points to normal coding exercises but this value can be modified depending on
-difficulty level. After students have completed the exercise, they can check their personal profile to see how many points they earned.
-
-In the 'assignment' portion of the exercise, instructors can add additional information about the assignment that will help
-students understand and complete the instructions. The Instructions section will contain the actual task the student is
-asked to execute. The 'pre-exercise code' sets up the workspace for the student; this section will contain code to import
-data sets, install packages and any other operation that you want to be in the workspace but hidden from students. The 'sample
-code' section contains code or notes that students view in the R script panel. Students also use the R script panel to write
-the code that solves the tasks in the instructions. If students are not able to complete the task without help, they can click
-on the 'Hint' button or eventually the 'solution'. When the student clicks the 'Submit Code' button, their answer passes through
-the SCT code where the code is checked for errors.
-
-The submission correctness testing code (or SCT) is the backbone for DataCamps' interactive nature. If a student submits an incorrect answer, they will 
-receive immediate feedback on what they are doing wrong and the system will guide them to the right answer. Instructors can use the default feedback
-that DataCamp automatically generates or write their own custom messages. The default feedback is meaningful and specific; most of the time custom 
-messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
-DataCamp provides a helpful R package called 'testwhat' which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
-repository: \url{https://github.com/datacamp/testwhat/wiki}. 
-'testwhat' contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect.
-The submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
-arguements can be added to the test functions to alter the testing process and automatic feedback. (**do I cite datacamp website here?**)
-
-%add an example of a test_function sct.... maybe plot
-
-The 'MultipleChoiceExercise', as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson'
-portion of the exercise and offer solutions in the 'Insructions' section. Similar to the 'normal' coding exercises, the lesson, instructions, pre-exercise 
-code and SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions: simple and regular. 
-The simple multiple choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises 
-allow instructors to pre-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises 
-are straightforward to write can act as quick checks for understanding throughout the chapter.
 
@@
 more detail on the content of the various exercises.
+
+Tips for smoother course development process:
+    + Using LaTeX math symbols to display greek letters, operators, ect.
+    + When using datacamp and github, press 'refresh' when available on the screen
 
@@
 
+LaTeX is compatable with DataCamp course builders can use LaTeX math symbols to display Greek letters, formulas, ect. For example:
+\begin{verbatim}
+$H_0$: $p = 0.07$
+$H_a$: $p \neq 0.07$
+\end{verbatim}
+
+translates to:
+
+$H_0$: $p = 0.07$
+
+$H_a$: $p \neq 0.07$
+
 %Check this out, Schubert said this \cite{Schubert13}.
@@
 \bibliography{library}
-% before it was 'library' so I thought if I changed it to the new bib file it would work but it doesn't :(
 

### 2017-11-02 manuscript.tex
edited

@@
 \caption{This code does this}
-\begin{verbatim}[frame=single]
+\begin{Verbatim}[frame=single]
 
-Student:
+Student types:
 histogram(dataset$var_name)
@@
 
-Student:
+Student types:
 hist(var_name)
@@
 
-Student:
+Student types:
 hist(dataset$misspelled_var)
@@
 Default message:
-Check your call of hist(). Did you correctly specify the argument x? 
+Check your call of hist(). Did you correctly specify the
+argument x? 
 It is a NULL, while it should be a numeric vector.
 
-\end{verbatim}
+\end{Verbatim}
 \label{fig:code1}
@@
 allow instructors to pre-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises 
-are straightforward to write can act as quick checks for understanding throughout the chapter.
+are straight forward to write can act as quick checks for understanding throughout the chapter.
 
@@
 \caption{This code does this}
-\begin{verbatim}[frame=single]
+\begin{Verbatim}[frame=single]
 --- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1 key:9707072219
@@
 ```
-\end{verbatim}
-\label{fig:code1}
+\end{Verbatim}
 \end{figure}

### 2017-12-20 manuscript.tex
format code to fit in text boxes

@@
 \caption{This code does this}
-\begin{verbatim}[frame=single]
+\begin{verbatim}
 --- type:NormalExercise lang:r xp:100 skills:1 key:9a4fea2da
@@
 \begin{Verbatim}[frame=single]
---- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1 key:9707072219
+--- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1
+    key:9707072219
+
 ## Quick check 2
@@
 msg_success <- "Exactly! R can do all of these things."
-test_mc(correct = 4, feedback_msgs = c(msg_bad, msg_bad, msg_bad, msg_success))
+test_mc(correct = 4, 
+    feedback_msgs = c(msg_bad, msg_bad, msg_bad, msg_success))
 ```

### 2017-12-24 manuscript.tex
made edits to manuscript

@@
 The DataCamp github repository contains links to the code for several available courses; one of the most helpful when starting to build a course 
-is \url{https://github.com/datacamp/courses-intro-to-r} which contains the source files for the `Intoduction to R' course.
+is \url{https://github.com/datacamp/courses-intro-to-r} which contains the source files for the \textit{Intoduction to R} course.
 
-Educators are able to edit their courses in a number of ways but the 'Teach Editor' located in the teach dashboard is the
-most straight forward editor. The 'Teach Editor' is specifically designed to make the creation process of a DataCamp course
+Educators are able to edit their courses in a number of ways but the \texttt{Teach Editor} located in the teach dashboard is the
+most straight forward editor. The \texttt{Teach Editor} is specifically designed to make the creation process of a DataCamp course
 as painless as possible, allowing writers to edit, preview, save changes and synchronize to a GitHub repository. Editing can
@@
 
-DataCamp courses may contain 3 different types of exercises: Normal, Multiple choice, and video.
+DataCamp courses may contain 3 different types of exercises: Normal coding exercises, Multiple choice, and Video.
 
 A \texttt{NormalExercise} is an exercise that prompts a user to submit code.
-The components of this include: lesson section, instructions, pre-exercise code, sample code, hint, solution and a submission correctness testing coded (SCT).
-However, the interface for students (or the 'Preview
-mode) only includes the lesson, Instructions, R script panel and a R console panel (Figure~\ref{fig:code1}).
+The components of this include: lesson section, instructions, pre-exercise code, sample code, hint, solution and a submission correctness testing code (SCT).
+(add reference to teach editor code) However, the interface for students (or the \texttt{Preview}
+mode) only includes the lesson, instructions, R script panel and a R console panel (Figure~\ref{fig:code1}).
 
 \begin{figure}
-\caption{This code does this}
+\caption{Teach Editor Interface}
 \begin{verbatim}
@@
 
-Whenever a new exercise is added, DataCamp automatically produces the top line in the editor. The header specifies the type
+Whenever a new exercise is added, DataCamp automatically produces the top line (header) in the editor. The header specifies the type
 of exercise \texttt{type}, language \texttt{lang}, available points \texttt{xp}, skills learned \texttt{skills} and a \texttt{key}. The key acts as a unique
@@
 documentation \url{https://www.datacamp.com/teach/documentation#tab_gamification}. 
-In the above exercise code, the \texttt{type} is Normal, the language is R, the available points is 100 and the skills learned is 1 (which 
+In the above exercise code (refer to teach editor code), the \texttt{type} is Normal, the language is R, the available points is 100 and the skills learned is 1 (which 
 corresponds to R Programming). DataCamp assigns 100 points to normal coding exercises but this value can be modified depending on
@@
 
-In the `Assignment' portion of the exercise, instructors can add additional information about the assignment that will help
-students understand and complete the instructions. The `Instructions' section contains the actual task the student is
-asked to execute; instructors can also include a `Hint' for extra guidence (optional). The 'pre-exercise code' sets up the workspace for 
+In the \textit{Assignment} portion of the exercise (not labeled but below the header), instructors can add additional information about the assignment that will help
+students understand and complete the instructions. The \textit{instructions} section contains the actual task the student is
+asked to execute; instructors can also include a \textit{hint} for extra guidence (optional). The \textit{pre-exercise code} sets up the workspace for 
 the student; this section will contain code to import data sets, install packages and any other operation that you want to be available to
-students. The 'sample code' section contains code or notes that students view in the R script panel. Students also use the R script panel to write
-the code that solves the tasks in the instructions. The correct answer to an exercise is coded in the 'solution' section
-and when the student clicks the `Submit Code' button, their answer passes through the SCT code where their code is checked for errors.
+students. The \textit{sample code} section contains code or notes that students view in the R script panel. Students also use the R script panel to write
+the code that solves the tasks in the instructions. The correct answer to an exercise is coded in the \textit{solution} section
+and when the student clicks the \texttt{Submit Code} button, their answer passes through the SCT code where their code is checked for errors.
 
@@
 Instructors can use the default feedback that DataCamp automatically generates or write their own custom messages. For example, figure blank
-contains the default feedback for an incorrect submission of the \texttt{hist()} function.
+contains the default feedback for a few possible incorrect submissions of the \texttt{hist()} function.
 
 \begin{figure}
-\caption{This code does this}
+\caption{Examples of DataCamps Default Feedback}
 \begin{Verbatim}[frame=single]
@@
 messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
-DataCamp provides a helpful R package called 'testwhat' which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
+DataCamp provides a helpful R package called \textit{testwhat} which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
 repository: \url{https://github.com/datacamp/testwhat/wiki}. 
-'testwhat' contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect.
+\textit{testwhat} contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect.
 The submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different

### 2018-01-03 manuscript.tex
add title
added to manuscript

@@
 %Substitute this all with tise_style
-\documentclass[12pt]{article}
+\documentclass[12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
+%% maxwidth is the original width if it is less than linewidth
+%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
+
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}
 \usepackage{natbib}  % used for citations
@@
 
-\title{Enter our title here}
+\title{DataCamp: An Interactive Teaching Tool}
 
-\author{Tessa Mcdonnel, Shannon Pileggi,  \\Statistics Department, California Polytechnic State University, San Luis Obispo}
-%\author{Shannon Pileggi \\Statistics Department, California Polytechnic State University, San Luis Obispo}
+\author{Tessa Mcdonnel, Shannon Pileggi \\Statistics Department \\ California Polytechnic State University, San Luis Obispo}
 
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 
-Questions:
-
-How do I say that LaTeX is compatible with datacamp?
-
-I can't find the swirl package on mendeley so im not sure how to add that.
-
-How did the linking with LMS process go?
-
-It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
+It is no suprise that technology plays a vital role in the field of statistics. As the technological revolution continues to
 unfold, the use of statistical software has become increasingly emphasized in education \citep{AmericanStatisticalAssociation2016}. By integrating the
@@
 interpreting real data sets \citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
-classroom \citep{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
-(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
-to use technology "as a way to explore conceptual ideas and enhance student learning" \citep{AmericanStatisticalAssociation2016}.
+classroom \citep{Wang2017}.
 
 The goal for any statistics course is to help students develop the ability to think statistically
-\citep{AmericanStatisticalAssociation2016}.
-Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
+\citep{AmericanStatisticalAssociation2016} and introducing technology into the curriculum can greatly strengthen this ability by illustrating concepts such as
 variability, randomness and hypothesis testing. Although numerous statistical technologies exist, R and R Studio
-provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \citep{Chance2007}. R
+provide extensive computational abilities (free of charge) and are commonly used in statistics courses. R
 allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
@@
 
-With this increased use of R in classrooms, there is a need for an effective way to get students familiar with statistical software
-\citep{Baumer2014}. While R software provides users with extraordinary capabilities, there is no doubt a steep learning curve. To facilitate
-this transition to R programming, popular interactive teaching technologies have been created including swirl (** need to cite package**), LearnR and TryR. 
-These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. swirl is an
-open source R package that allows students to learn R programing in their R console. This interactive learning tool
-contains several pre-existing lessons but what makes swirl so popular is its versitality; educators can also create their own
-lesson to fit the curriculum and assign it to students \citep{Carchedi2014}.
-While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, integration of learning management 
+\subsection{Interactive tools to learn R}
+With this increased use of R in classrooms, an effective tool to familiarlize students with statistical software is needed
+\citep{Baumer2014}. While R software provides users with extraordinary statistical capabilities, there is certainly a steep learning curve. To facilitate
+this transition to R programming, popular interactive teaching technologies have been created including \textit{swirl} \citep{Kross} and Try R \citep{TryR}. 
+These tools allow students to work through coding problems while receiving immediate feedback and can be used in and out of the classroom.
+
+\subsubsection{\textit{swirl}}
+\textit{swirl} is an
+open source R package that allows students to learn R programing in the R console. This interactive learning tool
+contains several pre-existing lessons and educators can also create their own
+lesson to fit the specific curriculum \citep{Carchedi2014}.
+While \textit{swirl} can be linked to a Massive Open Online Courses (MOOCs) like Coursera, integration of learning management 
 systems (LMS) is not available for the classroom.
 
-\textbf{Learn R section}
+\subsubsection{Try R}
+Try R \citep{TryR} also an interactive R programming course but unlike \textit{swirl}, Try R is web-based. 
+The R console can be intimidating to
+new statistics students so an advantage of a web-based teaching tool is
+the clean and easy to use interface. This is an important quality given that students often struggle more with the
+software used than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
+all installation complications are avoided and valuable class time can be focused on the lesson.
+However, Try R is not open source so public content authoring
+is not available; educators are limited to the existing lessons available on the Try R website.
 
-*Try R website  \url{http://tryr.codeschool.com} i dont know how to cite this with mendeley*
+\section{DataCamp}
 
-TryR (Code School 2014) is a web-based program but is not open source. Since public content authoring
-is not available, educators are limited on what they can teach their students. The R console can be intimidating to
-new statistics students so an advantage of a web-based teaching tool is
-the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with
-software than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
-all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.
+\subsection{DataCamp course features}
 
-The purpose of this article is to introduce a relatively new technology, DataCamp, which incorporates the best
-qualities from the teaching tools mentioned above.
+The purpose of this article is to introduce a new interactive teaching technology, DataCamp.
 
-DataCamp has the same reproducable capabilities as swirl but is a web-based application; educators can
-create their own courses that coincide with their lessons and students can access the course without installing R.
+\subsubsection{DataCamp compared to similar technologies}
+DataCamp provides the same reproducable capabilities as \textit{swirl} but is a web-based application. Educators can
+create their own courses that coincide with specific lessons and students can access the course without installing any software.
 Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
-tablet or moble device, making the courses accessible to anyone with an internet connection. 
-The DataCamp website offers pre-existing free community courses as well as specialized \textit{Premium} classes that you need to purchase. 
-However, when used for academic purposes the \textit{Premium} DataCamp content is also free for up to six months.
-Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign 
-\textit{community} courses, \textit{Premium} courses, and even a course that they've developed themselves. 
+tablet or moble device, making the courses accessible to anyone with an internet connection. The programming courses can be used in the 
+classroom in a number of ways: as traditional homework assignments, as an activity during lab periods, as pre-class assignments
+for a flipped classroom, and even as a test or assessment tool.
+
+\subsubsection{Wide variety of course topics}
+The DataCamp website offers pre-existing free community courses as well as more specialized \textit{Premium} classes that require a fee. 
 The collection of \textit{community} courses available on DataCamp inlcude a wide range of topics from \textit{Introduction to R} to
@@
 
-DataCamp can be used in the classroom in a number of ways: as traditional homework assignments, as an
-activity during lab periods, as pre-class assignments for a flipped classroom, and even as a test or assessment tool.
+\subsubsection{Integration with Learning Management Systems}
+One feature that sets DataCamp apart from competing technologies is the ability to track student progress. Educators
+can set deadlines for assignments and view which sections the
+students had trouble with in a detailed report. DataCamp courses can also be linked to the school's learning management system (LMS) so student scores are automatically updated to the
+current gradebook, allowing for a smooth integration of student work.
 
-A feature that sets DataCamp apart from competing technologies is the ability to track student progress. Educators
-can set deadlines for assignments and easily see not only when students complete an assignment but also which sections the
-students had trouble with in a detailed report (need to cite teach page of website). Student scores can be automatically updated to a
-current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration of student work.
-
-Each chapter in a DataCamp course is made up of modular exercises. Modularity is critical component in designing a statistical
+\subsubsection{Modularity}
+DataCamp courses are broken up into chapters and each chapter is composed of modular exercises. Modularity is a critical component in designing a
 learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality
-\citep{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
+\citep{Hare2017}. DataCamp course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
 these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
@@
 
-Each of these exercises can be given a number of redeemable points which the students can see when they begin
-the exercise, introducing a gamification feature to the learning experience. Students can view the exercise `hint' option and 30 percent
-of the available points are deducted; all points are deducted if they ask for the solution.  If the student completes the exercise without
-any help they will recieve the full points. When in a classroom group, students can view their
+\subsubsection{Gamification}
+Each chapter exercise is given a specified number of redeemable points which the students can see when they begin
+the exercise, introducing a gamification feature to the learning experience. When in a classroom group, students can view their
 progress (points and chapters completed) as well as then progress of their peers. This can help students perform better
 because they want to be on par with the rest of the class; furthermore, when students can see the number of available points
-for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}.
-
-\section{How to Use DataCamp}
-
+for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}. If the student completes the exercise without
+any assistance, they will recieve the full points. If the student is having trouble with a problem, they can view the exercise `hint' option and 30 percent
+of the available points are deducted; all points are deducted if they ask for the solution. 
 \subsection{Pre-existing R courses}
@@
 DataCamp's \textit{classroom} benefits, first create an academic group on the website \url{https://www.datacamp.com/groups/education}.
-After your university information has been verified and the classroom account has been approved, you can facilitate student access
-by either creating a group through the DataCamp website or linking directly to your LMS.
-
-(idk if this helps to say or is obvious) Add students by their university email address on the \textit{Members} tab and link the account to your LMS.)
-
-\subsection{Creating a DataCamp Course}
-To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} and
-a GitHub account \url{https://github.com}. The simplest way to begin building the course is to use the template course files from the 
-\texttt{Create DataCamp Course} dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
-make through DataCamp will update the GitHub repository and vice versa. Every DataCamp course is linked through GitHub version control,
+After your university information has been verified and the classroom account has been approved, access is facilitated 
+by either creating a group through the DataCamp website or linking directly to your LMS. You can add students to the course by their university email address on the \textit{Members} tab.
+\section{Creating a DataCamp Course}
+\subsection{Getting Started}
+To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} as well as
+a GitHub account \url{https://github.com}. Every DataCamp course is linked through GitHub version control,
 allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
 on GitHub and under \texttt{Settings} you can enter the user names of collaborators. Collaborators who are not the primary author need 
-to uncheck `My Courses' in order to view and contribute to the repository.
+to uncheck `My Courses' in order to view and contribute to the repository. The simplest way to begin building the course is to use the template course files from the
+\texttt{Create DataCamp Course} dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
+made through DataCamp will update the GitHub repository and vice versa.
 
@@
 
-When starting to create a DataCamp course, it is helpful to view code from pre-existing community courses which can be found on GitHub.
-You can use these files as a guide to build your own course or duplicate the repository and tailor the content to fit specific needs.
-The DataCamp github repository contains links to the code for several available courses; one of the most helpful when starting to build a course 
-is \url{https://github.com/datacamp/courses-intro-to-r} which contains the source files for the \textit{Intoduction to R} course.
-
+\subsection{Course Editing}
 Educators are able to edit their courses in a number of ways but the \texttt{Teach Editor} located in the teach dashboard is the
@@
 as painless as possible, allowing writers to edit, preview, save changes and synchronize to a GitHub repository. Editing can
-also be done through GitHub's online editor and through git locally but these methods do not allow for automatic content
+also be done through GitHub's online editor or through git locally but these methods do not allow for automatic content
 viewing.
-
-DataCamp courses may contain 3 different types of exercises: Normal coding exercises, Multiple choice, and Video.
-
-A \texttt{NormalExercise} is an exercise that prompts a user to submit code.
-The components of this include: lesson section, instructions, pre-exercise code, sample code, hint, solution and a submission correctness testing code (SCT).
-(add reference to teach editor code) However, the interface for students (or the \texttt{Preview}
-mode) only includes the lesson, instructions, R script panel and a R console panel (Figure~\ref{fig:code1}).
-
+\subsection{Components of a DataCamp Course}
+\subsubsection{Exercise Layout}
+Figure1 is an example of an interactive coding exercise for an introductory statistics course.
+Students will read the lesson information and instructions, answer the question, and submit their code; it should take approximately 5 minutes to complete this exercise.
 \begin{figure}
 \caption{Teach Editor Interface}
-\begin{verbatim}
+\begin{Verbatim}[frame=single]
 --- type:NormalExercise lang:r xp:100 skills:1 key:9a4fea2da
@@
 ```
-
-\end{verbatim}
+\end{Verbatim}
 \label{fig:code1}
@@
 \begin{figure}[h]
-  \includegraphics[scale = 0.19] {preview.jpg}
+  \includegraphics[scale = 0.40] {preview.jpg}
 \end{figure}
@@
 
+\subsubsection{Submission Correctness Test}
 The submission correctness testing code (or SCT) automatically assesses if the correct code was submitted. If a student submits an 
@@
 \begin{Verbatim}[frame=single]
-
 Student types:
@@
 \end{figure}
-
 The default feedback is meaningful and specific; most of the time custom 
@@
 
-%add an example of a test_function sct.... maybe plot
+\subsection{DataCamp Exercise Types}
+DataCamp courses may contain 3 different types of exercises: Normal coding, video, and multiple choice exercises.
+\subsubsection{Normal Exercise}
+A \texttt{NormalExercise} is an exercise that prompts a user to submit code.
+The components of this include: lesson section, instructions, pre-exercise code, sample code, hint, solution and a submission correctness testing code (SCT).
+(add reference to teach editor code) However, the interface for students (or the \texttt{Preview}
+mode) only includes the lesson, instructions, R script panel and a R console panel (Figure~\ref{fig:code1}).
+\subsubsection{Video Exercise}
+Video exercises act as in instructional video addition to a DataCamp course; instructors can add short videos of them explaining concepts and with 
+relevent slides that appear in the background. The DataCamp website \url{https://www.datacamp.com/teach/documentation#tab_code_exercises} provides 
+more detail on the content of the various exercises.
+
+\subsubsection{Multiple Choice Exercise}
 
@@
 \end{figure}
+\subsection{Advise for smoother course development}
+DataCamp is fairly new so the only existing information on creating a course is on the DataCamp website.
+While writing my first introductory R programming class on DataCamp, I learned a few tricks that I wish I knew before I started.
+\subsubsection{GitHub repositories}
+When creating your first DataCamp course, it is helpful to view code from pre-existing community courses which can be found on GitHub.
+DataCamp's github repository contains links to the code for several available courses; one of the most helpful when starting to build a course 
+is \url{https://github.com/datacamp/courses-intro-to-r} which contains the source files for the \textit{Intoduction to R} course.
+You can use these files as a guide to build your own course or duplicate the repository and tailor the content to fit specific needs.
 
-%add example of regular multiple choice exercise --> use Quick check 2 from lab 8
-
-Video exercises act as in instructional video addition to a DataCamp course; instructors can add short videos of them explaining concepts and with 
-relevent slides that appear in the background. The DataCamp website \url{https://www.datacamp.com/teach/documentation#tab_code_exercises} provides 
-more detail on the content of the various exercises.
-
-Tips for smoother course development process:
-    + Using LaTeX math symbols to display greek letters, operators, ect.
-    + When using datacamp and github, press 'refresh' when available on the screen
-
+\subsubsection{Integrating R packages}
 All DataCamp courses will have a course badge and most will use data sets and R packages. Information on how to add data sets and images
@@
 
+\subsubsection{TeX typesetting}
 LaTeX is compatable with DataCamp course builders can use LaTeX math symbols to display Greek letters, formulas, ect. For example:
@@
 
-%Check this out, Schubert said this \cite{Schubert13}.
+\section{Conclusion}
 
-%Check this out, Campbell said this \cite{Campbell02} regularly, but cite this in parentheses \citep{Campbell02}.
-
-%Check this out, Chi said this \cite{Chi81}.
-
-%Use this for final submission
-%\bibliographystyle{ECA_jasa}
 \bibliographystyle{plainnat}

### 2018-01-03 manuscript.tex
add to manuscript

@@
 
-It is no suprise that technology plays a vital role in the field of statistics. As the technological revolution continues to
+It is no surprise that technology plays a vital role in the field of statistics. As the technological revolution continues to
 unfold, the use of statistical software has become increasingly emphasized in education \citep{AmericanStatisticalAssociation2016}. By integrating the
@@
 \subsection{Interactive tools to learn R}
-With this increased use of R in classrooms, an effective tool to familiarlize students with statistical software is needed
+With this increased use of R in classrooms, an effective tool to familiarize students with statistical software is needed
 \citep{Baumer2014}. While R software provides users with extraordinary statistical capabilities, there is certainly a steep learning curve. To facilitate
 this transition to R programming, popular interactive teaching technologies have been created including \textit{swirl} \citep{Kross} and Try R \citep{TryR}. 
-These tools allow students to work through coding problems while receiving immediate feedback and can be used in and out of the classroom.
+Interactive tools allow students to work through coding problems while receiving immediate feedback and can be used in and outside of the classroom.
 
 \subsubsection{\textit{swirl}}
-\textit{swirl} is an
-open source R package that allows students to learn R programing in the R console. This interactive learning tool
-contains several pre-existing lessons and educators can also create their own
-lesson to fit the specific curriculum \citep{Carchedi2014}.
-While \textit{swirl} can be linked to a Massive Open Online Courses (MOOCs) like Coursera, integration of learning management 
+\textit{swirl} \citep{Kross} is an
+open source R package that allows students to learn R programming in the R console. This interactive learning tool
+contains several pre-existing lessons but educators can also create their own
+lesson content to fit specific curriculum \citep{Carchedi2014}.
+While \textit{swirl} can be linked to Massive Open Online Courses (MOOCs) like Coursera, integration of learning management 
 systems (LMS) is not available for the classroom.
@@
 \subsubsection{Try R}
-Try R \citep{TryR} also an interactive R programming course but unlike \textit{swirl}, Try R is web-based. 
+Try R \citep{TryR} is another interactive R programming course but unlike \textit{swirl}, Try R is web-based. 
 The R console can be intimidating to
-new statistics students so an advantage of a web-based teaching tool is
-the clean and easy to use interface. This is an important quality given that students often struggle more with the
+new statistics students so an advantage of web-based teaching tools is
+the clean and easy to use interface. User-friendliness is an important quality given that students often struggle more with the
 software used than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
@@
 \subsubsection{DataCamp compared to similar technologies}
-DataCamp provides the same reproducable capabilities as \textit{swirl} but is a web-based application. Educators can
+DataCamp provides the same reproducible capabilities as \textit{swirl} but is a web-based application. Educators can
 create their own courses that coincide with specific lessons and students can access the course without installing any software.
-Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
-tablet or moble device, making the courses accessible to anyone with an internet connection. The programming courses can be used in the 
+Courses are available through the DataCamp website so students can access the lesson through their web-browser on a laptop,
+tablet or mobile device, making the courses accessible to anyone with an internet connection. These programming courses can be used in the 
 classroom in a number of ways: as traditional homework assignments, as an activity during lab periods, as pre-class assignments
@@
 The DataCamp website offers pre-existing free community courses as well as more specialized \textit{Premium} classes that require a fee. 
-The collection of \textit{community} courses available on DataCamp inlcude a wide range of topics from \textit{Introduction to R} to
+The collection of \textit{community} courses available on DataCamp include a wide range of topics from \textit{Introduction to R} to
 \textit{Quantitative Risk Management in R} so novice through advanced programming students benefit.
@@
 students had trouble with in a detailed report. DataCamp courses can also be linked to the school's learning management system (LMS) so student scores are automatically updated to the
-current gradebook, allowing for a smooth integration of student work.
+current grade-book, allowing for a smooth integration of student work.
 
@@
 these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
-are not cummulative; every exercise begins with a clear workspace so an object defined in a previous exercise needs to be
+are not cumulative; every exercise begins with a clear work space so an object defined in a previous exercise needs to be
 defined again.
@@
 because they want to be on par with the rest of the class; furthermore, when students can see the number of available points
-for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}. If the student completes the exercise without
-any assistance, they will recieve the full points. If the student is having trouble with a problem, they can view the exercise `hint' option and 30 percent
+for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}. If the student completes an exercise without
+any assistance, they will receive the full points. If the student is having trouble with a problem, they can view the exercise `hint' option and 30 percent
 of the available points are deducted; all points are deducted if they ask for the solution. 
@@
 To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} as well as
-a GitHub account \url{https://github.com}. Every DataCamp course is linked through GitHub version control,
+a Git Hub account \url{https://github.com}. Every DataCamp course is linked through Git Hub version control,
 allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
-on GitHub and under \texttt{Settings} you can enter the user names of collaborators. Collaborators who are not the primary author need 
+on Git Hub and under \texttt{Settings} you can enter the user names of collaborators. Collaborators who are not the primary author need 
 to uncheck `My Courses' in order to view and contribute to the repository. The simplest way to begin building the course is to use the template course files from the
-\texttt{Create DataCamp Course} dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
-made through DataCamp will update the GitHub repository and vice versa.
+\texttt{Create DataCamp Course} dialog. This will automatically create a Git Hub repository that is linked to DataCamp; any changes that are
+made through DataCamp will update the Git Hub repository and vice versa.
 
-The newly created GitHub repositories will contain three files:
+The newly created Git Hub repositories will contain three files:
 
@@
 
-\texttt{Readme.md} contains helpful information of how to get started, citing resourses to learn more about the process.
+\texttt{Readme.md} contains helpful information of how to get started, citing resources to learn more about the process.
 \texttt{course.yml} is a file that contains general information about the course you're creating: title, university, description,
 difficulty level, ect.
-\texttt{chapter1.Rmd} is a template chapter file with examples of 'normal' interative coding exercises and multiple choice questions.
+\texttt{chapter1.Rmd} is a template chapter file with examples of 'normal' iterative coding exercises and multiple choice questions.
 To add more chapters to an R course, create new files in the repository and name them \texttt{chapter1.Rmd}, \texttt{chapter2.Rmd},
@@
 most straight forward editor. The \texttt{Teach Editor} is specifically designed to make the creation process of a DataCamp course
-as painless as possible, allowing writers to edit, preview, save changes and synchronize to a GitHub repository. Editing can
-also be done through GitHub's online editor or through git locally but these methods do not allow for automatic content
+as painless as possible, allowing writers to edit, preview, save changes and synchronize to a Git Hub repository. Editing can
+also be done through Git Hub's online editor or through git locally but these methods do not allow for automatic content
 viewing.
@@
 students understand and complete the instructions. The \textit{instructions} section contains the actual task the student is
-asked to execute; instructors can also include a \textit{hint} for extra guidence (optional). The \textit{pre-exercise code} sets up the workspace for 
+asked to execute; instructors can also include a \textit{hint} for extra guidance (optional). The \textit{pre-exercise code} sets up the work space for 
 the student; this section will contain code to import data sets, install packages and any other operation that you want to be available to
@@
 messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
-DataCamp provides a helpful R package called \textit{testwhat} which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's GitHub 
+DataCamp provides a helpful R package called \textit{testwhat} which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's Git Hub 
 repository: \url{https://github.com/datacamp/testwhat/wiki}. 
@@
 The submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
-arguements can be added to the test functions to alter the testing process and automatic feedback. (**do I cite datacamp website here?**)
+arguments can be added to the test functions to alter the testing process and automatic feedback. (**do I cite datacamp website here?**)
 
@@
 Video exercises act as in instructional video addition to a DataCamp course; instructors can add short videos of them explaining concepts and with 
-relevent slides that appear in the background. The DataCamp website \url{https://www.datacamp.com/teach/documentation#tab_code_exercises} provides 
+relevant slides that appear in the background. The DataCamp website \url{https://www.datacamp.com/teach/documentation#tab_code_exercises} provides 
 more detail on the content of the various exercises.
@@
 The \texttt{MultipleChoiceExercise}, as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson'
-portion of the exercise and offer solutions in the 'Insructions' section. Similar to the 'normal' coding exercises, the lesson, instructions, pre-exercise 
+portion of the exercise and offer solutions in the 'Instructions' section. Similar to the 'normal' coding exercises, the lesson, instructions, pre-exercise 
 code and SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions: simple and regular. 
@@
 While writing my first introductory R programming class on DataCamp, I learned a few tricks that I wish I knew before I started.
-\subsubsection{GitHub repositories}
-When creating your first DataCamp course, it is helpful to view code from pre-existing community courses which can be found on GitHub.
+\subsubsection{Git Hub repositories}
+When creating your first DataCamp course, it is helpful to view code from pre-existing community courses which can be found on Git Hub.
 DataCamp's github repository contains links to the code for several available courses; one of the most helpful when starting to build a course 
-is \url{https://github.com/datacamp/courses-intro-to-r} which contains the source files for the \textit{Intoduction to R} course.
+is \url{https://github.com/datacamp/courses-intro-to-r} which contains the source files for the \textit{Introduction to R} course.
 You can use these files as a guide to build your own course or duplicate the repository and tailor the content to fit specific needs.
@@
 there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
-in the GitHub course repository named \texttt{requirements.r}. The file should contain: \texttt{devtools::install\_version}, package name and version for 
+in the Git Hub course repository named \texttt{requirements.r}. The file should contain: \texttt{devtools::install\_version}, package name and version for 
 every package you use in the DataCamp course. For example, following code will add the \texttt{ggplot2} and \texttt{mosaic} packages to the repository.
@@
 \subsubsection{TeX typesetting}
-LaTeX is compatable with DataCamp course builders can use LaTeX math symbols to display Greek letters, formulas, ect. For example:
+LaTeX is comparable with DataCamp course builders can use LaTeX math symbols to display Greek letters, formulas, ect. For example:
 \begin{verbatim}

### 2018-01-04 manuscript.tex
edit manuscript

@@
 \subsection{Interactive tools to learn R}
-With this increased use of R in classrooms, an effective tool to familiarize students with statistical software is needed
+With the increased use of R in classrooms, an effective tool to familiarize students with statistical software is needed
 \citep{Baumer2014}. While R software provides users with extraordinary statistical capabilities, there is certainly a steep learning curve. To facilitate
 this transition to R programming, popular interactive teaching technologies have been created including \textit{swirl} \citep{Kross} and Try R \citep{TryR}. 
-Interactive tools allow students to work through coding problems while receiving immediate feedback and can be used in and outside of the classroom.
+Interactive tools allow students to actively work through coding problems while receiving immediate feedback.
 

### 2018-01-06 manuscript.tex
edit and organized

@@
 The goal for any statistics course is to help students develop the ability to think statistically
-\citep{AmericanStatisticalAssociation2016} and introducing technology into the curriculum can greatly strengthen this ability by illustrating concepts such as
+\citep{AmericanStatisticalAssociation2016}; introducing technology into the curriculum can greatly strengthen this ability by illustrating concepts such as
 variability, randomness and hypothesis testing. Although numerous statistical technologies exist, R and R Studio
@@
 While \textit{swirl} can be linked to Massive Open Online Courses (MOOCs) like Coursera, integration of learning management 
-systems (LMS) is not available for the classroom.
+systems (LMS) is not available currently.
 
@@
 \subsubsection{Wide variety of course topics}
-The DataCamp website offers pre-existing free community courses as well as more specialized \textit{Premium} classes that require a fee. 
-The collection of \textit{community} courses available on DataCamp include a wide range of topics from \textit{Introduction to R} to
+The DataCamp website offers free `community' courses as well as more specialized \textit{Premium} classes that require a fee. 
+However, when used for academic purposes the \textit{Premium} DataCamp content is free for up to six months.
+College educators can create a classroom group on the DataCamp website, add students to the group, 
+assign any of the existing courses and even assign a course that they've developed themselves. 
+The collection of community courses available on DataCamp include a wide range of topics from \textit{Introduction to R} to
 \textit{Quantitative Risk Management in R} so novice through advanced programming students benefit.
-
-\subsubsection{Integration with Learning Management Systems}
-One feature that sets DataCamp apart from competing technologies is the ability to track student progress. Educators
-can set deadlines for assignments and view which sections the
-students had trouble with in a detailed report. DataCamp courses can also be linked to the school's learning management system (LMS) so student scores are automatically updated to the
-current grade-book, allowing for a smooth integration of student work.
 
@@
 DataCamp courses are broken up into chapters and each chapter is composed of modular exercises. Modularity is a critical component in designing a
-learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality
+learning tool because it allows independent pieces to be added, modified or removed from the entire functionality
 \citep{Hare2017}. DataCamp course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
@@
 the exercise, introducing a gamification feature to the learning experience. When in a classroom group, students can view their
-progress (points and chapters completed) as well as then progress of their peers. This can help students perform better
-because they want to be on par with the rest of the class; furthermore, when students can see the number of available points
+progress (points and chapters completed) as well as the progress of their peers. This can help students perform better
+in order to be on par with the rest of the class. Furthermore, when students can see the number of available points
 for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}. If the student completes an exercise without
@@
 of the available points are deducted; all points are deducted if they ask for the solution.
+
+\subsubsection{Integration with Learning Management Systems}
+One feature that sets DataCamp apart from competing technologies is the ability to track student progress. Educators
+can set deadlines for assignments and view which sections the
+students had trouble with in a detailed report. DataCamp courses can also be linked to the school's learning management system (LMS) so student scores are automatically updated to the
+current grade-book, allowing for a smooth integration of student work.
+
 \subsection{Pre-existing R courses}
@@
 To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} as well as
-a Git Hub account \url{https://github.com}. Every DataCamp course is linked through Git Hub version control,
+a GitHub account \url{https://github.com}. Every DataCamp course is linked through GitHub version control,
 allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
-on Git Hub and under \texttt{Settings} you can enter the user names of collaborators. Collaborators who are not the primary author need 
+on GitHub and under \texttt{Settings} you can enter the user names of collaborators. Collaborators who are not the primary author need 
 to uncheck `My Courses' in order to view and contribute to the repository. The simplest way to begin building the course is to use the template course files from the
-\texttt{Create DataCamp Course} dialog. This will automatically create a Git Hub repository that is linked to DataCamp; any changes that are
-made through DataCamp will update the Git Hub repository and vice versa.
+\texttt{Create DataCamp Course} dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
+made through DataCamp will update the GitHub repository and vice versa.
 
-The newly created Git Hub repositories will contain three files:
+The newly created GitHub repositories will contain three files:
 
@@
 most straight forward editor. The \texttt{Teach Editor} is specifically designed to make the creation process of a DataCamp course
-as painless as possible, allowing writers to edit, preview, save changes and synchronize to a Git Hub repository. Editing can
-also be done through Git Hub's online editor or through git locally but these methods do not allow for automatic content
+as painless as possible, allowing writers to edit, preview, save changes and synchronize to a GitHub repository. Editing can
+also be done through GitHub's online editor or through git locally but these methods do not allow for automatic content
 viewing.
@@
 \subsubsection{Exercise Layout}
-Figure1 is an example of an interactive coding exercise for an introductory statistics course.
-Students will read the lesson information and instructions, answer the question, and submit their code; it should take approximately 5 minutes to complete this exercise.
+Figure1 is an example of an exercise in the editor and figure2 is the corresponding interface for students.
+Students will read the lesson information and instructions, answer the question, and submit their code; it should take approximately 5 minutes for a student to complete this exercise.
 \begin{figure}
@@
 \begin{figure}[h]
-  \includegraphics[scale = 0.40] {preview.jpg}
+  \includegraphics[scale = 0.20] {preview.jpg}
 \end{figure}
+\subsubsection{Exercise Header}
+Whenever a new exercise is added, DataCamp automatically produces the top line of the editor. The header specifies the type
+of exercise (\texttt{type}), programming language (\texttt{lang}), available points (\texttt{xp}), skills learned (\texttt{skills}) and a \texttt{key}. 
+The types of exercises include normal coding, video, and multiple choice exercises; we will discuss these further in the next section.
+In addition to R, DataCamp offers courses in other programming languages including Python and SQL for data science.
+DataCamp assigns 100 points \texttt{xp} to normal coding exercises but this value can be modified depending on
+difficulty level. After students have completed the exercise, they can check their personal profile to see how many points they earned.
+The \texttt{skills} portion of the header refers to DataCamp's
+eight different skill sets, defined by numbers 1-8. Skills and their corresponding numbers can be found in the DataCamp
+documentation \url{https://www.datacamp.com/teach/documentation#tab_gamification}. 
+Lastly, the \texttt{key} acts as a unique
+identifier for that exercise, allowing you to modify content without losing any student data. 
+In the above exercise code (refer to teach editor code), the \texttt{type} is Normal, the language is R, the available points is 100xp and the skills learned is 1 (which 
+corresponds to R Programming).
 
-Whenever a new exercise is added, DataCamp automatically produces the top line (header) in the editor. The header specifies the type
-of exercise \texttt{type}, language \texttt{lang}, available points \texttt{xp}, skills learned \texttt{skills} and a \texttt{key}. The key acts as a unique
-identifier for that exercise, allowing you to modify the content without losing any student data. Currently, DataCamp offers
-eight different skills which are defined by numbers 1-8. The skills and their corresponding numbers can be found in the DataCamp
-documentation \url{https://www.datacamp.com/teach/documentation#tab_gamification}. 
-In the above exercise code (refer to teach editor code), the \texttt{type} is Normal, the language is R, the available points is 100 and the skills learned is 1 (which 
-corresponds to R Programming). DataCamp assigns 100 points to normal coding exercises but this value can be modified depending on
-difficulty level. After students have completed the exercise, they can check their personal profile to see how many points they earned.
-
+\subsubsection{Exercise Body}
 In the \textit{Assignment} portion of the exercise (not labeled but below the header), instructors can add additional information about the assignment that will help
@@
 asked to execute; instructors can also include a \textit{hint} for extra guidance (optional). The \textit{pre-exercise code} sets up the work space for 
-the student; this section will contain code to import data sets, install packages and any other operation that you want to be available to
-students. The \textit{sample code} section contains code or notes that students view in the R script panel. Students also use the R script panel to write
-the code that solves the tasks in the instructions. The correct answer to an exercise is coded in the \textit{solution} section
-and when the student clicks the \texttt{Submit Code} button, their answer passes through the SCT code where their code is checked for errors.
+the student - this section contains code to import data sets, install packages and any other operation that you want to be available to
+students.
+The \textit{sample code} section will contain code or notes that will be visible to students in the R script panel.
+Students also use the R script panel to write code that solves the tasks in the instructions.
+The correct answer to an exercise is coded in the \textit{solution} section
+and when a student clicks the \texttt{Submit Code} button, their answer passes through the SCT code where their answer is checked for errors.
 
@@
 incorrect answer, they will receive immediate feedback on what they are doing wrong and the system will guide them to the right answer.
-Instructors can use the default feedback that DataCamp automatically generates or write their own custom messages. For example, figure blank
-contains the default feedback for a few possible incorrect submissions of the \texttt{hist()} function.
+DataCamp provides a helpful R package called \textit{testwhat} which acts as a guide to writing and using SCTs - available on DataCamp's GitHub 
+repository: \url{https://github.com/datacamp/testwhat/wiki}. 
+\textit{testwhat} contains functions that test different types of problems including loops, object definitions, printed output, functions, and other R programming problems.
+The submission correctness testing code compares the ideal answer (from the solution code) to the students answer. Various
+arguments can be added to the test functions to adjust the testing process and feedback.
+Instructors can either use the default feedback that DataCamp automatically generates or write their own custom messages. For example, figure blank
+contains the default feedback for a few possible incorrect submissions of the \texttt{hist()} function from the example exercise \textit{Visualizing quantitative data in R}.
 
@@
 \caption{Examples of DataCamps Default Feedback}
-\begin{Verbatim}[frame=single]
+\begin{Verbatim}
 Student types:
@@
 \end{Verbatim}
-\label{fig:code1}
 \end{figure}
-The default feedback is meaningful and specific; most of the time custom 
-messages are not necessary unless there is a common problem that student are struggling with in which more unique feedback is necessary. 
-DataCamp provides a helpful R package called \textit{testwhat} which acts as a guide to writing and using SCTs (this can be accessed on DataCamp's Git Hub 
-repository: \url{https://github.com/datacamp/testwhat/wiki}. 
-\textit{testwhat} contains functions that can test different types of problems including loops, object definitions, printed output, functions, ect.
-The submission correctness testing code compares the ideal answer (from the solution) to the students answer. Different
-arguments can be added to the test functions to alter the testing process and automatic feedback. (**do I cite datacamp website here?**)
+DataCamp's default feedback is meaningful and specific so a lot of the time custom 
+messages are not necessary.
+However, if students are struggling with a common problem then unique feedback can be very beneficial.
 
@@
 A \texttt{NormalExercise} is an exercise that prompts a user to submit code.
-The components of this include: lesson section, instructions, pre-exercise code, sample code, hint, solution and a submission correctness testing code (SCT).
-(add reference to teach editor code) However, the interface for students (or the \texttt{Preview}
-mode) only includes the lesson, instructions, R script panel and a R console panel (Figure~\ref{fig:code1}).
+The components of this include: lesson section, instructions, pre-exercise code, sample code, hint, solution and submission correctness testing code (SCT).
+However, the interface for students (or the \texttt{Preview}
+mode) will only include the lesson, instructions, R script panel and R console panel (Figure~\ref{fig:code1}).
 \subsubsection{Video Exercise}
-Video exercises act as in instructional video addition to a DataCamp course; instructors can add short videos of them explaining concepts and with 
-relevant slides that appear in the background. The DataCamp website \url{https://www.datacamp.com/teach/documentation#tab_code_exercises} provides 
-more detail on the content of the various exercises.
+Video exercises act as instructional videos that accompany a DataCamp course. Instructors can add short videos of them explaining concepts while 
+relevant slides appear in the background. The DataCamp website \url{https://www.datacamp.com/teach/documentation#tab_code_exercises} provides 
+more detail on the content of video exercises.
 
@@
 
-The \texttt{MultipleChoiceExercise}, as you would expect, contains a question and a list of various answers. Instructors write the questions in the 'lesson'
-portion of the exercise and offer solutions in the 'Instructions' section. Similar to the 'normal' coding exercises, the lesson, instructions, pre-exercise 
-code and SCTs have to be specified but sample and solution code do not. DataCamp offers two types of multiple choice questions: simple and regular. 
+The \texttt{MultipleChoiceExercise}, as you would expect, contains a question and a list of various answers. 
+DataCamp offers two types of multiple choice questions: simple and regular. 
 The simple multiple choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises 
@@
 
+Similar to \texttt{normal} coding exercises, the lesson, instructions, hint, pre-exercise 
+code and SCTs are included in the teach editor. However, multiple choice exercises do not have sample or solution code. 
+Instructors write the questions in the lesson
+portion of the exercise and offer solutions in the \texit{Instructions} section. Figuremultichoice is an example of plain multiple choice question.
 \begin{figure}
@@
 \end{figure}
+
+ADD PICTURE OF CORRESPONDING PREVIEW FOR MC QUESTION
+
 \subsection{Advise for smoother course development}
@@
 While writing my first introductory R programming class on DataCamp, I learned a few tricks that I wish I knew before I started.
-\subsubsection{Git Hub repositories}
-When creating your first DataCamp course, it is helpful to view code from pre-existing community courses which can be found on Git Hub.
+\subsubsection{GitHub repositories}
+When creating your first DataCamp course, it is helpful to view code from pre-existing community courses which can be found on GitHub.
 DataCamp's github repository contains links to the code for several available courses; one of the most helpful when starting to build a course 
@@
 there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
-in the Git Hub course repository named \texttt{requirements.r}. The file should contain: \texttt{devtools::install\_version}, package name and version for 
+in the GitHub course repository named \texttt{requirements.r}. The file should contain: \texttt{devtools::install\_version}, package name and version for 
 every package you use in the DataCamp course. For example, following code will add the \texttt{ggplot2} and \texttt{mosaic} packages to the repository.

### 2018-01-06 manuscript.tex
added manuscript pdf - need help with figures
edit manuscript

@@
 capabilities of technology in statistics courses, students can explore fundamental concepts by analyzing and
-interpreting real data sets \citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
+interpreting real data sets \citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is 
+practiced outside of the
 classroom \citep{Wang2017}.
 
-The goal for any statistics course is to help students develop the ability to think statistically
+The goal of any statistics course is to help students develop the ability to think statistically
 \citep{AmericanStatisticalAssociation2016}; introducing technology into the curriculum can greatly strengthen this ability by illustrating concepts such as
@@
 The R console can be intimidating to
-new statistics students so an advantage of web-based teaching tools is
+new statistics students so an advantage of a web-based teaching tool is
 the clean and easy to use interface. User-friendliness is an important quality given that students often struggle more with the
@@
 
-\section{DataCamp}
+\section{Introduction to DataCamp}
+
+The purpose of this article is to introduce a new interactive teaching technology, DataCamp.
 
@@
 
-The purpose of this article is to introduce a new interactive teaching technology, DataCamp.
-
-\subsubsection{DataCamp compared to similar technologies}
 DataCamp provides the same reproducible capabilities as \textit{swirl} but is a web-based application. Educators can
@@
 the exercise, introducing a gamification feature to the learning experience. When in a classroom group, students can view their
-progress (points and chapters completed) as well as the progress of their peers. This can help students perform better
+progress (points and chapters completed) as well as the progress of their peers. Students will often perform better
 in order to be on par with the rest of the class. Furthermore, when students can see the number of available points
@@
 \begin{figure}[h]
-  \includegraphics[scale = 0.20] {preview.jpg}
+  \includegraphics[scale = 0.40] {preview.jpg}
 \end{figure}
@@
 Instructors write the questions in the lesson
-portion of the exercise and offer solutions in the \texit{Instructions} section. Figuremultichoice is an example of plain multiple choice question.
+portion of the exercise and offer solutions in the \textit{Instructions} section. Figuremultichoice is an example of plain multiple choice question.
 \begin{figure}
-\caption{This code does this}
+\caption{This should be in section 3.4.3}
 \begin{Verbatim}[frame=single]

### 2018-01-07 manuscript.tex
edited 'advise' section

@@
 \textit{swirl} \citep{Kross} is an
-open source R package that allows students to learn R programming in the R console. This interactive learning tool
+open source R package where students can learn R programming directly in the R console. This interactive learning tool
 contains several pre-existing lessons but educators can also create their own
@@
 \begin{Verbatim}
-Student types:
-histogram(dataset$var_name)
+
+Student types:  histogram(dataset$var_name)
 
@@
 
-Student types:
-hist(var_name)
+***
+
+Student types: hist(var_name)
 
@@
 
-Student types:
-hist(dataset$misspelled_var)
+***
+
+Student types: hist(dataset$misspelled_var)
 
@@
 Video exercises act as instructional videos that accompany a DataCamp course. Instructors can add short videos of them explaining concepts while 
-relevant slides appear in the background. The DataCamp website \url{https://www.datacamp.com/teach/documentation#tab_code_exercises} provides 
+relevant slides appear in the background. The DataCamp website provides 
 more detail on the content of video exercises.
@@
 are straight forward to write can act as quick checks for understanding throughout the chapter.
-
-Similar to \texttt{normal} coding exercises, the lesson, instructions, hint, pre-exercise 
-code and SCTs are included in the teach editor. However, multiple choice exercises do not have sample or solution code. 
-Instructors write the questions in the lesson
-portion of the exercise and offer solutions in the \textit{Instructions} section. Figuremultichoice is an example of plain multiple choice question.
 \begin{figure}
-\caption{This should be in section 3.4.3}
+\caption{Example of Multiple Choice - This should be in section 3.4.3}
 \begin{Verbatim}[frame=single]
@@
 - All of the above
-
 *** =hint
 R software can be used for all of these things.
-
 *** =pre_exercise_code
 ```{r}
-
 ```
-
 *** =sct
 ```{r}
-
 msg_bad <- "That is not correct"
@@
 \end{figure}
-
+Similar to \texttt{normal} coding exercises, the lesson, instructions, hint, pre-exercise 
+code and SCTs are included in the teach editor. However, multiple choice exercises do not have sample or solution code. 
+Instructors write the questions in the lesson
+portion of the exercise and offer solutions in the \textit{Instructions} section.
+Figuremultichoice is an example of plain multiple choice question.
 ADD PICTURE OF CORRESPONDING PREVIEW FOR MC QUESTION
@@
 \subsection{Advise for smoother course development}
-DataCamp is fairly new so the only existing information on creating a course is on the DataCamp website.
-While writing my first introductory R programming class on DataCamp, I learned a few tricks that I wish I knew before I started.
+DataCamp is fairly new and the only available information about course creation is on the DataCamp website.
+While writing my first DataCamp R programming course, I learned a few tricks that I wish I knew before I started.
+
 \subsubsection{GitHub repositories}
-When creating your first DataCamp course, it is helpful to view code from pre-existing community courses which can be found on GitHub.
-DataCamp's github repository contains links to the code for several available courses; one of the most helpful when starting to build a course 
+When creating your first DataCamp course, it is helpful to view the code from existing community courses. 
+The DataCamp repository on GitHub contains links to the course code from several of their available courses. One of the most helpful links for DataCamp beginners
 is \url{https://github.com/datacamp/courses-intro-to-r} which contains the source files for the \textit{Introduction to R} course.
-You can use these files as a guide to build your own course or duplicate the repository and tailor the content to fit specific needs.
+You can use these files as a guide to build your own course or even duplicate the file and tailor the content to fit specific needs.
 
 \subsubsection{Integrating R packages}
-All DataCamp courses will have a course badge and most will use data sets and R packages. Information on how to add data sets and images
-can be found in DataCamps 'Teach' documentation \url{https://www.datacamp.com/teach/documentation} under the 'Upload Assets' tab. However,
+All DataCamp courses will have a course badge (image) and most will use data sets and R packages. Information on how to add data sets and images
+can be found in DataCamps \textit{Teach} documentation \url{https://www.datacamp.com/teach/documentation} under the `Upload Assets' tab. However,
 there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
-in the GitHub course repository named \texttt{requirements.r}. The file should contain: \texttt{devtools::install\_version}, package name and version for 
-every package you use in the DataCamp course. For example, following code will add the \texttt{ggplot2} and \texttt{mosaic} packages to the repository.
+in the GitHub course repository named \texttt{requirements.r}. This file should contain a line of code with three components: \texttt{devtools::install\_version}, package name and version for 
+every package you wish to include in the DataCamp course. For example, the following code will add the \texttt{ggplot2} and \texttt{mosaic} packages to the repository.
 
@@
 \end{verbatim}
-In order for DataCamp to recognize this new file, you will need to add \texttt{from: r-base-prod:27} to the \texttt{course.yml} file.
+In order for DataCamp to recognize this new file, you will need to add: \\ \texttt{from: r-base-prod:27} \\ to the \texttt{course.yml} file.
 
 \subsubsection{TeX typesetting}
-LaTeX is comparable with DataCamp course builders can use LaTeX math symbols to display Greek letters, formulas, ect. For example:
+LaTeX is compatible with DataCamp; course builders can use LaTeX math symbols to display Greek letters, formulas, ect. For example:
 \begin{verbatim}

### 2018-01-14 manuscript.tex
edited 'advise' section
edits to manuscript

@@
 The purpose of this article is to introduce a new interactive teaching technology, DataCamp.
-
+In addition to R, DataCamp offers courses in other programming languages including Python and SQL for data science.
 \subsection{DataCamp course features}
@@
 
-\subsubsection{Wide variety of course topics}
-The DataCamp website offers free `community' courses as well as more specialized \textit{Premium} classes that require a fee. 
+\subsubsection{Introduction to DataCamp - don't know what that note says?}
+DataCamp website offers free "community" courses as well as more specialized \textit{Premium} classes that require a fee. 
 However, when used for academic purposes the \textit{Premium} DataCamp content is free for up to six months.
 College educators can create a classroom group on the DataCamp website, add students to the group, 
-assign any of the existing courses and even assign a course that they've developed themselves. 
+assign any of the existing courses and even assign a course that they have developed themselves. 
 The collection of community courses available on DataCamp include a wide range of topics from \textit{Introduction to R} to
@@
 can set deadlines for assignments and view which sections the
-students had trouble with in a detailed report. DataCamp courses can also be linked to the school's learning management system (LMS) so student scores are automatically updated to the
+students had trouble with in a detailed report.
+DataCamp courses can also be linked to the school's learning management system (LMS), such as Moodle or Blackboard, so student scores are automatically updated to the
 current grade-book, allowing for a smooth integration of student work.
@@
 After your university information has been verified and the classroom account has been approved, access is facilitated 
-by either creating a group through the DataCamp website or linking directly to your LMS. You can add students to the course by their university email address on the \textit{Members} tab.
+by adding students to the DataCamp group by supplying university email addresses on the \textit{Members} tab, or by creating an integration to your LMS.
 \section{Creating a DataCamp Course}
@@
 To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} as well as
-a GitHub account \url{https://github.com}. Every DataCamp course is linked through GitHub version control,
-allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
-on GitHub and under \texttt{Settings} you can enter the user names of collaborators. Collaborators who are not the primary author need 
-to uncheck `My Courses' in order to view and contribute to the repository. The simplest way to begin building the course is to use the template course files from the
+a GitHub account (\url{https://github.com}). (Should this be in section 3.5.2? -- Every DataCamp course is linked through GitHub version control,
+allowing statistics educators to easily collaborate and reproduce code.) The simplest way to begin building the course is to use the template course files from the
 \texttt{Create DataCamp Course} dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
@@
 \texttt{Readme.md} contains helpful information of how to get started, citing resources to learn more about the process.
-\texttt{course.yml} is a file that contains general information about the course you're creating: title, university, description,
+The \texttt{course.yml} is a file that contains general information about the course you're creating: title, university, description,
 difficulty level, ect.
-\texttt{chapter1.Rmd} is a template chapter file with examples of 'normal' iterative coding exercises and multiple choice questions.
+The \texttt{chapter1.Rmd} is a template chapter file with examples of `normal' iterative coding exercises and multiple choice questions.
 To add more chapters to an R course, create new files in the repository and name them \texttt{chapter1.Rmd}, \texttt{chapter2.Rmd},
@@
 \subsection{Course Editing}
-Educators are able to edit their courses in a number of ways but the \texttt{Teach Editor} located in the teach dashboard is the
+Educators are able to edit their courses in a number of ways, but the \texttt{Teach Editor} located in the DataCamp dashboard is the
 most straight forward editor. The \texttt{Teach Editor} is specifically designed to make the creation process of a DataCamp course
@@
 \subsubsection{Exercise Layout}
-Figure1 is an example of an exercise in the editor and figure2 is the corresponding interface for students.
-Students will read the lesson information and instructions, answer the question, and submit their code; it should take approximately 5 minutes for a student to complete this exercise.
+Figure1 is an example of an exercise in the Teach Editor and figure2 is the corresponding interface for students.
+Students will read the lesson information and instructions, answer the question, and submit their code; it is recommended that each exercise takes approximately 5 minutes.
 \begin{figure}
@@
 \subsubsection{Exercise Header}
-Whenever a new exercise is added, DataCamp automatically produces the top line of the editor. The header specifies the type
+Whenever a new exercise is added, DataCamp automatically produces the exercise header (---type:, etc.). The header specifies the type
 of exercise (\texttt{type}), programming language (\texttt{lang}), available points (\texttt{xp}), skills learned (\texttt{skills}) and a \texttt{key}. 
-The types of exercises include normal coding, video, and multiple choice exercises; we will discuss these further in the next section.
-In addition to R, DataCamp offers courses in other programming languages including Python and SQL for data science.
-DataCamp assigns 100 points \texttt{xp} to normal coding exercises but this value can be modified depending on
+The types of exercises include normal coding, video, and multiple choice exercises; which will be discussed further in the next section. 
+DataCamp assigns 100 points \texttt{xp} by default to normal coding exercises but this value can be modified depending on
 difficulty level. After students have completed the exercise, they can check their personal profile to see how many points they earned.
@@
 identifier for that exercise, allowing you to modify content without losing any student data. 
-In the above exercise code (refer to teach editor code), the \texttt{type} is Normal, the language is R, the available points is 100xp and the skills learned is 1 (which 
+In Figure 1, the \texttt{type} is Normal, the language is R, the available points is 100xp and the skills learned is 1 (which 
 corresponds to R Programming).
@@
 In the \textit{Assignment} portion of the exercise (not labeled but below the header), instructors can add additional information about the assignment that will help
-students understand and complete the instructions. The \textit{instructions} section contains the actual task the student is
-asked to execute; instructors can also include a \textit{hint} for extra guidance (optional). The \textit{pre-exercise code} sets up the work space for 
-the student - this section contains code to import data sets, install packages and any other operation that you want to be available to
+students understand and complete the instructions, which is displayed in the top left panel of Figure 2. The \textit{instructions} section contains the actual task the student is
+asked to execute; instructors can also include a \textit{hint} for extra guidance (bottom left panel Figure 2). The \textit{pre-exercise code} sets up the work space for 
+the student - this section contains code to import data sets, install packages and any other operation that you want to be available but not visible to
 students.
-The \textit{sample code} section will contain code or notes that will be visible to students in the R script panel.
+The \textit{sample code} section will contain code or notes that will be visible to students in the R script panel (top right figure 2).
 Students also use the R script panel to write code that solves the tasks in the instructions.
 The correct answer to an exercise is coded in the \textit{solution} section
-and when a student clicks the \texttt{Submit Code} button, their answer passes through the SCT code where their answer is checked for errors.
+and when a student clicks the \texttt{Submit Code} button, their answer passes through the R console, and then the Submission Correctness Testing (SCT) code where their answer is checked for errors.
 
@@
 repository: \url{https://github.com/datacamp/testwhat/wiki}. 
-\textit{testwhat} contains functions that test different types of problems including loops, object definitions, printed output, functions, and other R programming problems.
+The \textit{testwhat} package contains functions that test different types of problems including loops, object definitions, printed output, functions, and other R programming problems.
 The submission correctness testing code compares the ideal answer (from the solution code) to the students answer. Various
@@
 Instructors can either use the default feedback that DataCamp automatically generates or write their own custom messages. For example, figure blank
-contains the default feedback for a few possible incorrect submissions of the \texttt{hist()} function from the example exercise \textit{Visualizing quantitative data in R}.
+contains the default feedback for a few possible incorrect submissions of the \texttt{hist()} function. 
+Suppose the data set is called \texttt{birthdata} and the variable of interest is \texttt{weight}.
 
@@
 
-Student types:  histogram(dataset$var_name)
+It's weird but I get errors when I name the data set birth_data.
 
-Default message:
-Have you called hist()?
+Student types:                  Default message:
 
-***
+histogram(birthdata$weight)    Have you called hist()?
 
-Student types: hist(var_name)
-
-Default message:
-Check your call of hist(). Did you correctly specify 
-the argument x? Evaluating the expression you specified
+hist(weight)                    Check your call of hist(). Did you 
+                                correctly specify the argument x? 
+                                Evaluating the expression you specified
                                 caused an error.
 
-***
-
-Student types: hist(dataset$misspelled_var)
-
-Default message:
-Check your call of hist(). Did you correctly specify the
-argument x? 
-It is a NULL, while it should be a numeric vector.
+hist(birthdata$wieght)         Check your call of hist(). Did you
+                                correctly specify the argument x? It is
+                                a NULL, while it should be a numeric vector.
 
@@
 \end{figure}
+
+\textit{I might want to add one where student types something with the wrong symbol but I can't get onto the datacamp course for some reason.}
+
 DataCamp's default feedback is meaningful and specific so a lot of the time custom 
@@
 
+\begin{verbatim}
+Multiple choice exercises use the SCT function called  \texttt{test_mc} 
+which requires two arguments: \texttt{correct} and \texttt{feedback_msgs}. 
+The \texttt{correct} argument specifies the position of the correct answer;
+if the correct answer is the second option listed, then set \texttt{correct = 2}. 
+The \texttt{feedback_msgs} argument is a vector of strings that contain feedback 
+messages corresponding to the positions of the listed options.
+
+\end{verbatim}
 \subsection{Advise for smoother course development}
 DataCamp is fairly new and the only available information about course creation is on the DataCamp website.
-While writing my first DataCamp R programming course, I learned a few tricks that I wish I knew before I started.
+While the documentation on DataCamp is comprehensive, here are some tips for developing a first course.
 
@@
 
+\subsubsection{Collaboration for course development}
+To add collaborators to the course, go to the course repository
+on GitHub and under \texttt{Settings} you can enter the user names of collaborators. Collaborators who are not the primary author need 
+to uncheck `My Courses' in order to view and contribute to the repository.
 \subsubsection{Integrating R packages}
-All DataCamp courses will have a course badge (image) and most will use data sets and R packages. Information on how to add data sets and images
+Information on how to add data sets and images to a course
 can be found in DataCamps \textit{Teach} documentation \url{https://www.datacamp.com/teach/documentation} under the `Upload Assets' tab. However,
@@
 
-\subsubsection{TeX typesetting}
+\subsubsection{TeX typesetting or Markdown}
 LaTeX is compatible with DataCamp; course builders can use LaTeX math symbols to display Greek letters, formulas, ect. For example:

### 2018-01-19 manuscript.tex
final edits

@@
 the exercise, introducing a gamification feature to the learning experience. When in a classroom group, students can view their
-progress (points and chapters completed) as well as the progress of their peers. Students will often perform better
-in order to be on par with the rest of the class. Furthermore, when students can see the number of available points
+progress (points and chapters completed) as well as the progress of their peers. When students can see the number of available points
 for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}. If the student completes an exercise without
@@
 To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} as well as
-a GitHub account (\url{https://github.com}). (Should this be in section 3.5.2? -- Every DataCamp course is linked through GitHub version control,
-allowing statistics educators to easily collaborate and reproduce code.) The simplest way to begin building the course is to use the template course files from the
+a GitHub account (\url{https://github.com}). The simplest way to begin building the course is to use the template course files from the
 \texttt{Create DataCamp Course} dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
@@
 Figure1 is an example of an exercise in the Teach Editor and figure2 is the corresponding interface for students.
-Students will read the lesson information and instructions, answer the question, and submit their code; it is recommended that each exercise takes approximately 5 minutes.
+Students will read the lesson information and instructions, answer the question, and submit their code.
 \begin{figure}
@@
 
-\begin{verbatim}
-Multiple choice exercises use the SCT function called  \texttt{test_mc} 
-which requires two arguments: \texttt{correct} and \texttt{feedback_msgs}. 
+Multiple choice exercises use the SCT function called  \texttt{test\_mc} 
+which requires two arguments: \texttt{correct} and \texttt{feedback\_msgs}. 
 The \texttt{correct} argument specifies the position of the correct answer;
 if the correct answer is the second option listed, then set \texttt{correct = 2}. 
-The \texttt{feedback_msgs} argument is a vector of strings that contain feedback 
+The \texttt{feedback\_msgs} argument is a vector of strings that contain feedback 
 messages corresponding to the positions of the listed options.
 
-\end{verbatim}
 \subsection{Advise for smoother course development}
@@
 \subsubsection{Collaboration for course development}
+Every DataCamp course is linked through GitHub version control,
+allowing statistics educators to easily collaborate and reproduce code. 
 To add collaborators to the course, go to the course repository

### 2018-04-05 manuscript.tex
manuscript revisions

--- 2018-01-07 manuscript.tex
@@
-%\documentclass{tise_style}
-%\usepackage{natbib}
-%Having trouble getting tise_style to compile correctly in RStudio, will re-run it with this before submission
+\documentclass{tise_style_doi}
 
-%-----------------------------------------------------------------------------------------------------
-%Substitute this all with tise_style
-\documentclass[12pt]{article}\usepackage[]{graphicx}\usepackage[]{color}
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
+\usepackage{soul}     % for highlighting
+\usepackage{upquote}  % for correct display of single quotes in verbatim
+\usepackage{booktabs} % for toprule, etc. in tabular
 
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
+%--------------------------------------------------------------------------------
+%<--- TYPE WITHIN THESE BOUNDS  ------------------  TYPE WITHIN THESE BOUNDS --->
+%12345678901234567890123456789012345678901234567890123456789012345678901234567890
+%--------------------------------------------------------------------------------
 
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
+\title{DataCamp: An Interactive Teaching Tool for Programming}
 
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+\author{Tessa Mcdonnel, Mine \c{C}etinkaya-Rundel, Weston Stearns, Shannon Pileggi}
 
-\usepackage{alltt}
-\usepackage{natbib}  % used for citations
-\usepackage[parfill]{parskip} %used for formatting style of text
-\usepackage{url}
-\usepackage{graphicx}
-\usepackage{setspace}
-\usepackage{fancyvrb}
-% Sets margins to 1 in
-%\addtolength{\oddsidemargin}{-.5in}%
-%\addtolength{\evensidemargin}{-.5in}%
-%\addtolength{\textwidth}{1in}%
-%\addtolength{\textheight}{1.3in}%
-%\addtolength{\topmargin}{-.8in}%
-%-----------------------------------------------------------------------------------------------------
-
-\title{DataCamp: An Interactive Teaching Tool}
-
-\author{Tessa Mcdonnel, Shannon Pileggi \\Statistics Department \\ California Polytechnic State University, San Luis Obispo}
-
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 
+%================================================================================
 \section{Introduction}
 
-\doublespacing
+%\doublespacing
 
-It is no surprise that technology plays a vital role in the field of statistics. As the technological revolution continues to
-unfold, the use of statistical software has become increasingly emphasized in education \citep{AmericanStatisticalAssociation2016}. By integrating the
-capabilities of technology in statistics courses, students can explore fundamental concepts by analyzing and
-interpreting real data sets \citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is 
-practiced outside of the
-classroom \citep{Wang2017}.
+It is no surprise that technology plays a vital role in the field of statistics. As
+the technological revolution continues to unfold, the use of statistical software
+has become increasingly emphasized in education \citep{AmericanStatisticalAssociation2016}.
+By integrating the capabilities of technology in statistics courses, students can
+explore fundamental concepts by analyzing and interpreting real data sets
+\citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics
+is practiced outside of the classroom \citep{Wang2017}.
 
-The goal of any statistics course is to help students develop the ability to think statistically
-\citep{AmericanStatisticalAssociation2016}; introducing technology into the curriculum can greatly strengthen this ability by illustrating concepts such as
-variability, randomness and hypothesis testing. Although numerous statistical technologies exist, R and R Studio
-provide extensive computational abilities (free of charge) and are commonly used in statistics courses. R
-allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
-an interest in the domain of statistics \citep{Wang2017}.
+As the stated goal of a statistics course is to help students develop the ability to think
+statistically \citep{AmericanStatisticalAssociation2016}, introducing technology into
+the curriculum can greatly strengthen this ability by illustrating concepts such as
+variability, randomness and hypothesis testing. Although numerous statistical technologies
+exist, R and RStudio provide extensive computational abilities (free of charge) and are
+commonly used in statistics courses. R allows students to explore real-world data sets which
+can not only enhance their understanding of concepts, but can also spark an interest in the
+domain of statistics \citep{Wang2017}.
 
+%--------------------------------------------------------------------------------
 \subsection{Interactive tools to learn R}
-With the increased use of R in classrooms, an effective tool to familiarize students with statistical software is needed
-\citep{Baumer2014}. While R software provides users with extraordinary statistical capabilities, there is certainly a steep learning curve. To facilitate
-this transition to R programming, popular interactive teaching technologies have been created including \textit{swirl} \citep{Kross} and Try R \citep{TryR}. 
-Interactive tools allow students to actively work through coding problems while receiving immediate feedback.
 
-\subsubsection{\textit{swirl}}
-\textit{swirl} \citep{Kross} is an
-open source R package where students can learn R programming directly in the R console. This interactive learning tool
-contains several pre-existing lessons but educators can also create their own
-lesson content to fit specific curriculum \citep{Carchedi2014}.
-While \textit{swirl} can be linked to Massive Open Online Courses (MOOCs) like Coursera, integration of learning management 
-systems (LMS) is not available currently.
+With the increased use of R in classrooms, an effective tool to familiarize students
+with statistical software is needed \citep{Baumer2014}. While R software provides users
+with extraordinary statistical capabilities, there is certainly a steep learning curve.
+To facilitate this transition to R programming, popular interactive teaching technologies
+have been created including \texttt{swirl} \citep{Kross}, Try R \citep{TryR}, LearnR, and DataCamp.
+Interactive tools allow students to actively work through coding problems and receive
+immediate feedback.
 
+%--------------------------------------------------------------------------------
+\subsubsection{Swirl}
+
+\texttt{Swirl} is an open source R package where students can learn R programming
+directly in the R console \citep{Kross}. This interactive learning tool contains several
+pre-existing lessons but educators can also create their own lesson content to fit
+specific curriculum \citep{Carchedi2014}.  While \textit{swirl} can be linked to Massive
+Open Online Courses (MOOCs) like Coursera, integration of learning management systems (LMS)
+is not currently available.
+
+%--------------------------------------------------------------------------------
 \subsubsection{Try R}
-Try R \citep{TryR} is another interactive R programming course but unlike \textit{swirl}, Try R is web-based. 
-The R console can be intimidating to
-new statistics students so an advantage of a web-based teaching tool is
-the clean and easy to use interface. User-friendliness is an important quality given that students often struggle more with the
-software used than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
-all installation complications are avoided and valuable class time can be focused on the lesson.
-However, Try R is not open source so public content authoring
-is not available; educators are limited to the existing lessons available on the Try R website.
 
+Try R is another interactive R programming course but unlike \texttt{swirl}, Try R
+is web-based \citep{TryR}. The RStudio console can be intimidating to new statistics students
+so an  advantage of a web-based teaching tool is the clean and easy to use interface.
+User-friendliness is an important quality given that students often struggle more
+with the software used than the statistical concepts themselves \citep{Hare2017}.
+When students only need their web browser to participate, all installation
+complications are avoided and valuable class time can be focused on the lesson.
+However, Try R is not open source so public content authoring is not available;
+educators are limited to the existing lessons available on the Try R website.
+Lastly, Try R cannot currently integrate with LMS.
+
+%--------------------------------------------------------------------------------
+\subsubsection{LearnR?}
+
+%================================================================================
 \section{Introduction to DataCamp}
 
-The purpose of this article is to introduce a new interactive teaching technology, DataCamp.
+\hl{Weston - insert background here}
+DataCamp (\url{www.datacamp.com}) was first created in X with the mission to X.
+DataCamp provides a comprehensive web-based platform to interactive lessons on various coding
+languages. The DataCamp website offers free `community' courses
+as well as more specialized \textit{Premium} classes that require a fee. However, when used
+for academic purposes the \textit{Premium} DataCamp content is free for up to six months.
+Currently, DataCamp has X number of users across X countries.
 
-\subsection{DataCamp course features}
+%--------------------------------------------------------------------------------
+\subsection{Accessibility}
 
-DataCamp provides the same reproducible capabilities as \textit{swirl} but is a web-based application. Educators can
-create their own courses that coincide with specific lessons and students can access the course without installing any software.
-Courses are available through the DataCamp website so students can access the lesson through their web-browser on a laptop,
-tablet or mobile device, making the courses accessible to anyone with an internet connection. These programming courses can be used in the 
-classroom in a number of ways: as traditional homework assignments, as an activity during lab periods, as pre-class assignments
-for a flipped classroom, and even as a test or assessment tool.
+DataCamp lessons are available through the both the DataCamp website and a mobile app
+(\url{https://www.datacamp.com/mobile}) so students can access lessons through their
+web-browser on a laptop, tablet or mobile device.  This makes learning programming
+accessible to anyone with an internet connection and negates the barrier of software installation.
 
-\subsubsection{Wide variety of course topics}
-The DataCamp website offers free `community' courses as well as more specialized \textit{Premium} classes that require a fee. 
-However, when used for academic purposes the \textit{Premium} DataCamp content is free for up to six months.
-College educators can create a classroom group on the DataCamp website, add students to the group, 
-assign any of the existing courses and even assign a course that they've developed themselves. 
-The collection of community courses available on DataCamp include a wide range of topics from \textit{Introduction to R} to
-\textit{Quantitative Risk Management in R} so novice through advanced programming students benefit.
+%--------------------------------------------------------------------------------
+\subsection{Courses}
 
-\subsubsection{Modularity}
-DataCamp courses are broken up into chapters and each chapter is composed of modular exercises. Modularity is a critical component in designing a
-learning tool because it allows independent pieces to be added, modified or removed from the entire functionality
-\citep{Hare2017}. DataCamp course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
-these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
-are not cumulative; every exercise begins with a clear work space so an object defined in a previous exercise needs to be
-defined again.
+There are currently 114 premium courses created by 82 instructors, and this
+number is constantly growing.  Courses span a wide range of languages (R, Python, SQL,
+Git, and shell) as well as topics (programming, data manipulation, data visualization,
+statistical methods, etc.).  The breadth of courses offered makes DataCamp suitable
+for novice students to advance programmers. If there is not a course that quite
+fits your needs, you can also create your own community course (see Section \ref{creating}).
 
-\subsubsection{Gamification}
-Each chapter exercise is given a specified number of redeemable points which the students can see when they begin
-the exercise, introducing a gamification feature to the learning experience. When in a classroom group, students can view their
-progress (points and chapters completed) as well as the progress of their peers. Students will often perform better
-in order to be on par with the rest of the class. Furthermore, when students can see the number of available points
-for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}. If the student completes an exercise without
-any assistance, they will receive the full points. If the student is having trouble with a problem, they can view the exercise `hint' option and 30 percent
-of the available points are deducted; all points are deducted if they ask for the solution.
+%--------------------------------------------------------------------------------
+\subsection{Modularity}
 
-\subsubsection{Integration with Learning Management Systems}
-One feature that sets DataCamp apart from competing technologies is the ability to track student progress. Educators
-can set deadlines for assignments and view which sections the
-students had trouble with in a detailed report. DataCamp courses can also be linked to the school's learning management system (LMS) so student scores are automatically updated to the
-current grade-book, allowing for a smooth integration of student work.
+DataCamp courses are broken up into chapters and each chapter is composed of modular
+exercises. Modularity is a critical component in designing a learning tool because it
+allows independent pieces to be added, modified or removed from the entire functionality
+\citep{Hare2017}. This is particularly useful when creating your own course as DataCamp
+course exercises can be added, modified, or deleted as new topics arise and instructors
+can tailor these exercises to meet the needs of a particular class.
 
-\subsection{Pre-existing R courses}
-In order to utilize 
-DataCamp's \textit{classroom} benefits, first create an academic group on the website \url{https://www.datacamp.com/groups/education}.
-After your university information has been verified and the classroom account has been approved, access is facilitated 
-by either creating a group through the DataCamp website or linking directly to your LMS. You can add students to the course by their university email address on the \textit{Members} tab.
-\section{Creating a DataCamp Course}
-\subsection{Getting Started}
-To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} as well as
-a GitHub account \url{https://github.com}. Every DataCamp course is linked through GitHub version control,
-allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
-on GitHub and under \texttt{Settings} you can enter the user names of collaborators. Collaborators who are not the primary author need 
-to uncheck `My Courses' in order to view and contribute to the repository. The simplest way to begin building the course is to use the template course files from the
-\texttt{Create DataCamp Course} dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
-made through DataCamp will update the GitHub repository and vice versa.
+%--------------------------------------------------------------------------------
+\subsection{Gamification}
 
-The newly created GitHub repositories will contain three files:
+Each exercise is given a specified number of redeemable points which the students
+can see when they begin the exercise, introducing a gamification feature to the learning
+experience. When in a classroom group, students can view their progress (points and chapters
+completed) \hl{as well as the progress of their peers - verify}. Furthermore, when students
+can see the number of available points for an exercise it can motivate them to meet their personal
+achievement goals \citep{Chang2016}. If the student completes an exercise without
+any assistance, they will receive the full points. If the student is having difficulty, they can
+view the exercise `hint' option and 30 percent of the available points are deducted.
+Lastly, if the student is completely stuck the student may view the solution; however, all
+points are deducted.
 
-1) \texttt{README.md}
+%--------------------------------------------------------------------------------
+\subsection{Tracking student progress}
 
-2) \texttt{course.yml}
+A notable feature that sets DataCamp apart from competing technologies is the ability
+to track student progress. This means that programming courses can be used
+in the classroom in a number of ways: as traditional homework assignments, as an activity
+during lab periods, as pre-class assignments for a flipped classroom, and even as a
+test or assessment tool.
 
-3) \texttt{chapter1.Rmd}
+In order to utilize DataCamp's \textit{classroom} benefits, first create an academic
+group on the website \url{https://www.datacamp.com/groups/education}. After your
+university information has been verified and the classroom account has been approved,
+access is facilitated by either creating a group through the DataCamp website or
+linking directly to your LMS.
 
-\texttt{Readme.md} contains helpful information of how to get started, citing resources to learn more about the process.
-\texttt{course.yml} is a file that contains general information about the course you're creating: title, university, description,
-difficulty level, ect.
-\texttt{chapter1.Rmd} is a template chapter file with examples of 'normal' iterative coding exercises and multiple choice questions.
-To add more chapters to an R course, create new files in the repository and name them \texttt{chapter1.Rmd}, \texttt{chapter2.Rmd},
-\texttt{chapter3.Rmd}, ect.
+If using the group functionality on the DataCamp website, you can add students to the course
+by their university email address on the \textit{Members} tab.  You can also set deadlines
+for assignments (entire courses or individual chapters) and view downloadable grade reports.
 
-\subsection{Course Editing}
-Educators are able to edit their courses in a number of ways but the \texttt{Teach Editor} located in the teach dashboard is the
-most straight forward editor. The \texttt{Teach Editor} is specifically designed to make the creation process of a DataCamp course
-as painless as possible, allowing writers to edit, preview, save changes and synchronize to a GitHub repository. Editing can
-also be done through GitHub's online editor or through git locally but these methods do not allow for automatic content
-viewing.
-\subsection{Components of a DataCamp Course}
-\subsubsection{Exercise Layout}
-Figure1 is an example of an exercise in the editor and figure2 is the corresponding interface for students.
-Students will read the lesson information and instructions, answer the question, and submit their code; it should take approximately 5 minutes for a student to complete this exercise.
+Alternatively, students can be linked to DataCamp assignments via an LMS (including
+Blackboard, Moodle, Sakai, Canvas, EdX, Coursera, and Schoology) in the \textit{Settings} tab.
+With direct LMS integration educators do not have to add students via their email address.
+Furthermore, they can link directly to specific assignments in their LMS, and grades are
+automatically recorded in the LMS grade book.
+
+%================================================================================
+\section{Creating a DataCamp course}
+\label{creating}
+
+%--------------------------------------------------------------------------------
+%\subsection{Getting Started}
+
+To build a course on DataCamp you need both a DataCamp account and a GitHub account 
+(\url{https://github.com}). Once logged into DataCamp as user, it is hard to find a link
+to the \emph{teach} site - just go to \url{www.datacamp.com/teach/}.  
+Every DataCamp course is linked through GitHub version control, allowing educators to 
+easily collaborate and maintain code. While comprehensive documentation is provided 
+through the \emph{teach} website, we will discuss the basics.
+
+The simplest way to begin building the course is to use the template course files from
+the \texttt{Create Course} dialog. This will automatically create a GitHub repository
+that is linked to DataCamp.
+
+%--------------------------------------------------------------------------------
+\subsection{Initial repository}
+
+The newly created GitHub repository will contain three files:
+\begin{enumerate}
+\item \texttt{README.md}
+\item[] Contains helpful information on how to get started and cites resources to
+learn more about the process.
+\item \texttt{course.yml}
+\item[] Contains general information about the course you are creating: title, university,
+description, difficulty level, etc.
+\item \texttt{chapter1.Rmd}
+\item[] A template chapter file with examples of `normal' iterative coding exercises and
+multiple choice questions.  To add more chapters to an R course, create new files in the repository
+and name them \texttt{chapter1.Rmd}, \texttt{chapter2.Rmd}, \texttt{chapter3.Rmd}, etc.
+\end{enumerate}
+
+%--------------------------------------------------------------------------------
+\subsection{Course editing}
+
+Course creators can edit their courses through either GitHub or the \texttt{Teach Editor}
+accessed through the DataCamp website. The \texttt{Teach Editor} allows content
+creators to edit, preview, save changes, and synchronize to the GitHub repository.
+Editing completed via GitHub does not allow for automatic content viewing. Any changes
+that are made through the DataCamp \texttt{Teach Editor} will update the GitHub
+repository and vice versa.
+
+%--------------------------------------------------------------------------------
+\subsection{Components of a DataCamp lesson}
+
+DataCamp lessons can consist of coding exercises, multiple choice exercises, 
+and videos.  Each exercise is presented as a multi-panel layout that consists
+of an exercise body, instructions, script editor, and R console.  Exercises
+can be initiated through creation buttons available in the \texttt{Teach Editor},
+which automatically create an exercise template.
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{Exercise layout}
+
+Figure \ref{fig:code1} is an example of ``normal exercise'' syntax and Figure 
+\ref{fig:preview} is the corresponding interface students see. Students read the 
+lesson information and instructions, answer the question, and submit their code.
+
+\hl{It looks like the exercise header (yaml) has updated since last summer - update this?}
+
+\hl{Take all examples from Intro to R course rather than personal course?}
+
 \begin{figure}
-\caption{Teach Editor Interface}
+\caption{Syntax to create a ``normal exercise'' on DataCamp.  In DataCamp's
+\texttt{Teach Editor}, the syntax is color-coded.}
 \begin{Verbatim}[frame=single]
---- type:NormalExercise lang:r xp:100 skills:1 key:9a4fea2da
+--- type:NormalExercise lang:r xp:100 skills:1 key:9a4fea2da0
+
 ## Visualizing quantitative data in R
@@
 
-To create a histogram in R, use the syntax:
-`hist(dataset$quant_var)`
+- use `hist(dataset$quant_var)` to create a histogram
 
 *** =instructions
-- Create a histogram of the `wage` variable from the 
-`CPS85` data set.
+- Create a histogram of the `wage` variable from the `CPS85` data set 
+using the `hist()` function.
+- Click the 'Submit Answer' Button and take a look at the R output in the 
+console.
+
 *** =hint
-Follow the format from the lesson: `hist(dataset$variable)`
-with specified data set and variable.
+
 *** =pre_exercise_code
@@
 ```
+
 *** =sample_code
 ```{r}
-# Create histogram of the wage variable
+# Create histogram of wage variable with hist() function
+
 ```
+
 *** =solution
 ```{r}
-# Create histogram of the wage variable 
+# Create histogram of wage variable with hist() function
 hist(CPS85$wage)
 ```
+
 *** =sct
 ```{r}
-test_function("hist", args = "x", incorrect_msg = 
-"Make sure you specify the `CPS85` data set
-and `wage` variable.")
+test_function("hist", args = "x", 
+              incorrect_msg = "Follow the format: `hist(dataset$variable)` 
+                               with specified dataset and variable.")
 ```
+
 \end{Verbatim}
@@
 \begin{figure}[h] 
-  \includegraphics[scale = 0.40] {preview.jpg}
+\caption{Preview of the rendered result of the ``normal exercise'' syntax displayed 
+in Figure \ref{fig:code1}.}
+\includegraphics[width = 1.0\textwidth] {code1preview.png}
+\label{fig:preview}
 \end{figure}
-\subsubsection{Exercise Header}
-Whenever a new exercise is added, DataCamp automatically produces the top line of the editor. The header specifies the type
-of exercise (\texttt{type}), programming language (\texttt{lang}), available points (\texttt{xp}), skills learned (\texttt{skills}) and a \texttt{key}. 
-The types of exercises include normal coding, video, and multiple choice exercises; we will discuss these further in the next section.
-In addition to R, DataCamp offers courses in other programming languages including Python and SQL for data science.
-DataCamp assigns 100 points \texttt{xp} to normal coding exercises but this value can be modified depending on
-difficulty level. After students have completed the exercise, they can check their personal profile to see how many points they earned.
-The \texttt{skills} portion of the header refers to DataCamp's
-eight different skill sets, defined by numbers 1-8. Skills and their corresponding numbers can be found in the DataCamp
-documentation \url{https://www.datacamp.com/teach/documentation#tab_gamification}. 
-Lastly, the \texttt{key} acts as a unique
-identifier for that exercise, allowing you to modify content without losing any student data. 
-In the above exercise code (refer to teach editor code), the \texttt{type} is Normal, the language is R, the available points is 100xp and the skills learned is 1 (which 
-corresponds to R Programming).
 
-\subsubsection{Exercise Body}
-In the \textit{Assignment} portion of the exercise (not labeled but below the header), instructors can add additional information about the assignment that will help
-students understand and complete the instructions. The \textit{instructions} section contains the actual task the student is
-asked to execute; instructors can also include a \textit{hint} for extra guidance (optional). The \textit{pre-exercise code} sets up the work space for 
-the student - this section contains code to import data sets, install packages and any other operation that you want to be available to
-students.
-The \textit{sample code} section will contain code or notes that will be visible to students in the R script panel.
-Students also use the R script panel to write code that solves the tasks in the instructions.
-The correct answer to an exercise is coded in the \textit{solution} section
-and when a student clicks the \texttt{Submit Code} button, their answer passes through the SCT code where their answer is checked for errors.
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{Exercise header}
 
-\subsubsection{Submission Correctness Test}
-The submission correctness testing code (or SCT) automatically assesses if the correct code was submitted. If a student submits an 
-incorrect answer, they will receive immediate feedback on what they are doing wrong and the system will guide them to the right answer.
-DataCamp provides a helpful R package called \textit{testwhat} which acts as a guide to writing and using SCTs - available on DataCamp's GitHub 
-repository: \url{https://github.com/datacamp/testwhat/wiki}. 
-\textit{testwhat} contains functions that test different types of problems including loops, object definitions, printed output, functions, and other R programming problems.
-The submission correctness testing code compares the ideal answer (from the solution code) to the students answer. Various
-arguments can be added to the test functions to adjust the testing process and feedback.
-Instructors can either use the default feedback that DataCamp automatically generates or write their own custom messages. For example, figure blank
-contains the default feedback for a few possible incorrect submissions of the \texttt{hist()} function from the example exercise \textit{Visualizing quantitative data in R}.
+When creating a new exercise, DataCamp automatically produces the header (the first line
+of syntax). The header specifies the type of exercise (\texttt{type}), programming
+language (\texttt{lang}), available points (\texttt{xp}), skills learned (\texttt{skills})
+and a \texttt{key}. By default, DataCamp assigns 100 points to normal coding exercises,
+but this value can be modified. The \texttt{skills} portion of the header refers to DataCamp's
+eight different skill sets, defined by numbers 1-8. Skills and their corresponding
+numbers can be found in the DataCamp documentation
+\url{https://www.datacamp.com/teach/documentation#tab_gamification}.
+Lastly, the \texttt{key} acts as a unique identifier for that exercise, allowing you
+to modify content without losing any student data. In Figures \ref{fig:code1} and
+\ref{fig:preview}, the \texttt{type} is Normal, the language is R,
+the available points is 100xp and the skills learned is 1 (which corresponds to R Programming).
 
-\begin{figure}
-\caption{Examples of DataCamps Default Feedback}
-\begin{Verbatim}
+\hl{skills not used anymore? - link goes to a different page}
 
-Student types:  histogram(dataset$var_name)
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{Exercise body}
 
-Default message:
-Have you called hist()?
+In the \textit{lesson} portion of the exercise (not labeled but below the header),
+instructors can add additional information about the assignment that will help
+students understand and complete the instructions. The \textit{instructions} section
+contains the actual task required; instructors can also include
+a \textit{hint} for extra guidance (optional). The \textit{pre-exercise code} sets up
+the R work space for the student - here, you can automate tasks for the students such
+as loading packages, importing data sets, or pre-processing data. The \textit{sample code} 
+section contains comments and code that will be visible to students in the R script 
+panel, which is where students submit code.  The correct answer to an exercise is 
+coded in the \textit{solution} section.  After student clicks the \texttt{Submit Code}
+ button, their answer passes through the \textit{submission correctness test} (SCT) 
+where the submission is assessed for accuracy.
 
-***
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{Submission correctness test}
 
-Student types: hist(var_name)
+The SCT automatically assesses if the correct code was submitted. If a student submits 
+an incorrect answer, they will receive immediate feedback and guidance towards
+the correct answer.  The SCT is executed through DataCamp's \texttt{testwhat} R
+package (\url{https://github.com/datacamp/testwhat/wiki}). The \textit{testwhat} package 
+contains functions that test different types of problems including multiple choice
+exercises, what students typed, and output generated.  The SCT compares the ideal answer 
+(from the solution code) to the student's answer. Various arguments can be added to the 
+test functions to adjust the testing process and feedback.  Instructors can either use the 
+default feedback that DataCamp automatically generates or write their own custom messages. 
+For example, Table \ref{tab:SCT} contains the default feedback for a few possible incorrect submissions 
+of the \texttt{hist()} function from the example
+exercise \textit{Visualizing quantitative data in R} shown in Figures \ref{fig:code1} and
+\ref{fig:preview}.
 
-Default message:
-Check your call of hist(). Did you correctly specify 
-the argument x? Evaluating the expression you specified
-caused an error.
+\begin{table}\label{tab:SCT}
+\caption{Feedback provided in the R console and in the DataCamp lesson through the 
+SCT for the exercise shown in Figures \ref{fig:code1} and \ref{fig:preview}.}
+\begin{tabular}{lll}
+\toprule
+Student submission & R console & SCT feedback \\
+\midrule
+\texttt{histogram(CPS85\$wage)} & Error: could not find & Have you called hist()? \\
+                                & function ``histogram'' & \\
+[2ex]
+\texttt{hist(wage)} & Error: object `wage' & Follow the format: hist(dataset\$variable) \\
+                    &  not found           & with specified dataset and variable.\\
+[2ex]                    
+\texttt{hist(CP85\$wage)} & Error: object `CP85' & Follow the format: hist(dataset\$variable) \\
+                               & not found       & with specified dataset and variable. \\
+[2ex]                                                   
+\texttt{hist(CPS85\$wage)} & & Great work! \\
+\bottomrule
+\end{tabular}
+\end{table}
 
-***
+%--------------------------------------------------------------------------------
+\subsection{DataCamp exercises}
 
-Student types: hist(dataset$misspelled_var)
+DataCamp courses currently have six different exercise types available (see
+Table \ref{tab:exercises}).
 
-Default message:
-Check your call of hist(). Did you correctly specify the
-argument x? 
-It is a NULL, while it should be a numeric vector.
+\begin{table}\label{tab:exercises}
+\caption{Exercise types currently supported in DataCamp}
+\begin{tabular}{ll}
+\toprule
+Type & Description \\
+\midrule
+\texttt{VideoExercise}              & Displays a video exercise \\
+\texttt{NormalExercise}	            & Instructions, exercise, code editor, and console \\
+\texttt{MultipleChoiceExercise}     & Multiple choice question and console \\
+\texttt{PureMultipleChoiceExercise} & Multiple choice question without a console \\
+\texttt{TabExercise}	            & A series of connected sub-exercises \\
+\texttt{BulletExercise}	            & A series of connected sub-exercises \\
+\bottomrule
+\end{tabular}
+\end{table}
 
-\end{Verbatim}
-\end{figure}
-DataCamp's default feedback is meaningful and specific so a lot of the time custom 
-messages are not necessary.
-However, if students are struggling with a common problem then unique feedback can be very beneficial.
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{Video exercise}
 
-\subsection{DataCamp Exercise Types}
-DataCamp courses may contain 3 different types of exercises: Normal coding, video, and multiple choice exercises.
-\subsubsection{Normal Exercise}
-A \texttt{NormalExercise} is an exercise that prompts a user to submit code.
-The components of this include: lesson section, instructions, pre-exercise code, sample code, hint, solution and submission correctness testing code (SCT).
-However, the interface for students (or the \texttt{Preview}
-mode) will only include the lesson, instructions, R script panel and R console panel (Figure~\ref{fig:code1}).
-\subsubsection{Video Exercise}
-Video exercises act as instructional videos that accompany a DataCamp course. Instructors can add short videos of them explaining concepts while 
-relevant slides appear in the background. The DataCamp website provides 
-more detail on the content of video exercises.
+A \texttt{VideoExercise} displays as instructional video while relevant
+slides appear in the background.
 
-\subsubsection{Multiple Choice Exercise}
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{Normal exercise}
 
-The \texttt{MultipleChoiceExercise}, as you would expect, contains a question and a list of various answers. 
-DataCamp offers two types of multiple choice questions: simple and regular. 
-The simple multiple choice exercises are used for questions that do not require the R console or any R output. Regular multiple choice exercises 
-allow instructors to pre-program objects or plots that the student needs to access to answer the question. Both types of multiple choice exercises 
-are straight forward to write can act as quick checks for understanding throughout the chapter.
-\begin{figure}
-\caption{Example of Multiple Choice - This should be in section 3.4.3}
-\begin{Verbatim}[frame=single]
---- type:PlainMultipleChoiceExercise lang:r xp:50 skills:1
-    key:9707072219
+A \texttt{NormalExercise} prompts students to submit code. The components of this 
+include: lesson section, instructions, pre-exercise code, sample code, hint, solution 
+and submission correctness testing code (SCT). The students interface consists of the 
+lesson, instructions, R script panel and R console (Figure \ref{fig:code1}).
 
-## Quick check 2
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{Multiple choice exercises}
 
-What can R be used for?
+The \texttt{MultipleChoiceExercise} contains a question and a list of various answers. 
+This exercise is accompanied by the R console and R output, and allows instructors to 
+pre-program objects or plots that the student needs to access to answer the question.
+The \texttt{PureMultipleChoiceExercise} contains a question and a list of various
+answers - this exercise type does not include the R console and output. Similar to a
+\texttt{NormalExercise}, the lesson, instructions, hint, pre-exercise code and SCTs are 
+included in the exercise syntax. Instructors write the questions in the lesson portion 
+of the exercise, present options in the \textit{Instructions} section, and can specify a 
+\textit{hint} as well. The \texttt{MultipleChoiceExercise} utilizes SCT for assessment,
+whereas the \texttt{PureMultipleChoiceExercise} utilizes simpler syntax.
 
-*** =instructions
-- Graphing data
-- Analyzing data
-- Calculations
-- All of the above
-*** =hint
-R software can be used for all of these things.
-*** =pre_exercise_code
-```{r}
-```
-*** =sct
-```{r}
-msg_bad <- "That is not correct"
-msg_success <- "Exactly! R can do all of these things."
-test_mc(correct = 4, 
-    feedback_msgs = c(msg_bad, msg_bad, msg_bad, msg_success))
-```
-\end{Verbatim}
-\end{figure}
-Similar to \texttt{normal} coding exercises, the lesson, instructions, hint, pre-exercise 
-code and SCTs are included in the teach editor. However, multiple choice exercises do not have sample or solution code. 
-Instructors write the questions in the lesson
-portion of the exercise and offer solutions in the \textit{Instructions} section.
-Figuremultichoice is an example of plain multiple choice question.
-ADD PICTURE OF CORRESPONDING PREVIEW FOR MC QUESTION
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{Connected sub-exercises}
 
-\subsection{Advise for smoother course development}
-DataCamp is fairly new and the only available information about course creation is on the DataCamp website.
-While writing my first DataCamp R programming course, I learned a few tricks that I wish I knew before I started.
+Both \texttt{TabExercise} and \texttt{BulletExercise} are a series of connected
+sub-exercises and are suitable for problems that require several steps in a sequence.
+DataCamp documentation provides advice on which exercise is appropriate for a
+given situation.
 
-\subsubsection{GitHub repositories}
-When creating your first DataCamp course, it is helpful to view the code from existing community courses. 
-The DataCamp repository on GitHub contains links to the course code from several of their available courses. One of the most helpful links for DataCamp beginners
-is \url{https://github.com/datacamp/courses-intro-to-r} which contains the source files for the \textit{Introduction to R} course.
-You can use these files as a guide to build your own course or even duplicate the file and tailor the content to fit specific needs.
+%--------------------------------------------------------------------------------
+\subsection{Advice for course development}
 
-\subsubsection{Integrating R packages}
-All DataCamp courses will have a course badge (image) and most will use data sets and R packages. Information on how to add data sets and images
-can be found in DataCamps \textit{Teach} documentation \url{https://www.datacamp.com/teach/documentation} under the `Upload Assets' tab. However,
-there is currently no information on DataCamp about integrating R packages. To use R packages in a course, you will need to create a new file
-in the GitHub course repository named \texttt{requirements.r}. This file should contain a line of code with three components: \texttt{devtools::install\_version}, package name and version for 
-every package you wish to include in the DataCamp course. For example, the following code will add the \texttt{ggplot2} and \texttt{mosaic} packages to the repository.
+While the documentation provided by DataCamp is comprehensive, here are some tips 
+and things to consider as you get started with course development.
 
-\begin{verbatim}
-devtools::install_version("ggplot2", "2.2.0")
-devtools::install_version("mosaic", "0.14.4")
-\end{verbatim}
-In order for DataCamp to recognize this new file, you will need to add: \\ \texttt{from: r-base-prod:27} \\ to the \texttt{course.yml} file.
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{Can I do this? How long does it take?}
 
-\subsubsection{TeX typesetting}
-LaTeX is compatible with DataCamp; course builders can use LaTeX math symbols to display Greek letters, formulas, ect. For example:
-\begin{verbatim}
-$H_0$: $p = 0.07$
-$H_a$: $p \neq 0.07$
-\end{verbatim}
+Of course time to build a course will vary from instructor to instructor.  But to
+put it in perspective, at California Polytechnic State University, San Luis Obispo a faculty
+member collaborated on a DataCamp course for introductory statistics with an 
+undergraduate research assistant over 8 weeks in the summer (no video content
+was created).  The undergraduate research assistant took the lead on course creation, 
+had no prior experience with DataCamp, had never used GitHub, and was minimally 
+familiar with the course content. So yes, you can do it!
 
-translates to:
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{Collaborating on course development}
 
-$H_0$: $p = 0.07$
+Each DataCamp course is associated with a primary content creator, but multiple individuals 
+can contribute simultaneously to the course.  To do so, go to the course repository on GitHub 
+and under \texttt{Settings} enter the Github user names of collaborators. One note of caution 
+here - to deploy the course to your class, the primary content creator needs to be listed 
+as member of the course.
 
-$H_a$: $p \neq 0.07$
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{Learn from other courses}
 
+When creating your first DataCamp course, it is helpful to view the code from existing
+community courses. The DataCamp GitHub account (\url{https://github.com/datacamp}) 
+contains repositories for premium courses.  A useful repository to examine for
+beginners is the Introduction to R course (\url{https://github.com/datacamp/courses-intro-to-r}).
+You can use these files as a guide to build your own course or even duplicate the repository 
+and tailor the content to fit specific needs.
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{Typesetting}
+
+Exercise syntax adheres to some Markdown and some \LaTeX typesetting.  This means that 
+\texttt{\#\#} creates a bold header and \verb|$\neq$| renders as \texttt{$\neq$}. However,
+sometimes the mix of the two produce conflicting results.  For example, when we initially
+created the course, \verb|$H_0$| rendered the \texttt{0} in italics rather than as
+a subscript.  The solution was to use the backslash escape (\verb|$H\_0$|) for 
+correct rendering.
+
+%================================================================================
+\section{Experiences in the classroom}
+
+%--------------------------------------------------------------------------------
+\subsection{Traditional classroom}
+
+At California Polytechnic State University, San Luis Obispo we utilized DataCamp
+in three sections of 35 students enrolled in an introductory statistics course
+for non-statistics majors with no programming background. This course meets in a 
+traditional classroom three days a week and a computer lab classroom one day a week.
+
+Students spent their first lab class completing the first chapter of our community 
+DataCamp course assigned via Moodle, and most students finished in about 20 minutes.  
+The in-class time for the first chapter was beneficial as it allowed the instructor
+to be present to answer questions and help some students overcome their initial 
+apprehension at typing code.
+
+For subsequent weeks, DataCamp chapters were assigned as pre-lab homework assignments 
+(completed outside of the classroom) so that students could familiarize themselves with 
+code prior to attending lab.  Then the lab period was spent working on a lab exercise
+completed in RStudio and compiled as an R Markdown document.
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{What went well}
+
+Integration of DataCamp assignments with Moodle was easy.  A link with the assigned
+chapter was posted on the course site, and then students were taken directly to the 
+first page of the assigned chapter (no additional log in required!). Grades were 
+available in the Moodle grade book immediately after students completed the assignment.
+DataCamp computes scores as experience points (\texttt{xp}), but Moodle automatically 
+converted this a percentage completion as desired.  In addition, students were
+able to re-visit the chapter as many times as they wanted.
+
+Although it was not formally evaluated, it appeared that students were able to complete
+in-class lab assignments easier with the DataCamp preparation, as opposed to previous
+course iterations which only had assigned readings and videos on code lessons.
+
+While there will always be some students (among non-statistics majors) that grumble about 
+having to learn R, overall student feedback was positive.
+
+%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsubsection{What could be improved}
+
+With integration via Moodle, one chapter was assigned at a time.  Although it
+was possible to specify a recommended deadline for assignment completion, this
+was not enforced via Moodle.  This meant that students could complete the
+assignment after the deadline and still receive full credit.  Moreover,
+because students are able to re-visit a chapter, the grade recorded in the Moodle
+grade center was always the highest grade recorded for the student, regardless of
+the completion iteration (first, second attempt?) or date of completion.
+
+DataCamp does not implement clear and strong delineations between chapters, and the
+default is for lessons to continue immediately to a next chapter after chapter
+completion.  (It was very easy for students to miss the notification of Chapter 1
+completion, and they would keep going on to Chapter 2.)  This had two consequences.
+First, students may be learning more material than required for a given week, which
+could overwhelm them.  Second, a student who completed Chapter 2 via the Chapter 1 
+Moodle integration would not have a grade assigned to Moodle for Chapter 2.  The only
+way a grade would be assigned for Chapter 2 was if the student accessed Chapter 2 via 
+Moodle directly from the Chapter 2 integration link.
+
+Lastly, there were occasional issues where students said they completed an assignment
+and their grade was not recorded or that they could not complete the assignment because
+the DataCamp session expired.  It was unclear if these problems were due to local internet
+connectivity issues or due to interruptions on the DataCamp website.  However, in general,
+work from previous DataCamp sessions was saved for each individual student, and so to 
+rectify the situation the student simply needed to re-access the integration link and 
+re-submit their saved solutions.
+
+%--------------------------------------------------------------------------------
+\subsection{Massive open online courses}
+
+\hl{Mine - insert here}
+
+%================================================================================
+\section{Using metadata for iterative course development}
+
+\hl{Weston - I can't find metadata for my course!  Is there a difference in how
+data is recorded when you add members to DataCamp via email vs link via LMS?
+
+Mine - can you add in here?
+}
+
+%================================================================================
+\section{Discussion}
+
+-The only disadvantage of the modularity feature is that the sessions are not cumulative; every
+exercise begins with a clear work space so an object defined in a previous exercise needs
+to be defined again.
+
+-DataCamp is changing constantly
+
+-emphasis on correct code over interpretation of results
+
+-no way to produce reproducible reports based on data camp work
+
+-no notes/summaries provided - easy to forget
+
+-in the classroom
+
+-glitches in teach editor
+
+%================================================================================
 \section{Conclusion}

### 2018-04-09 manuscript.tex

@@
 \usepackage{booktabs} % for toprule, etc. in tabular
+\usepackage{pifont}   % used to create check/x marks
+
+\newcommand{\cmark}{\ding{51}} % check mark
+\newcommand{\xmark}{\ding{55}} % x mark
 
@@
 
-\title{DataCamp: An Interactive Teaching Tool for Programming}
-
-\author{Tessa Mcdonnel, Mine \c{C}etinkaya-Rundel, Weston Stearns, Shannon Pileggi}
+\title{DataCamp: An Interactive Learning Tool for Programming}
 
@@
 
+\hl{Discuss benefits of `learn by doing' or repetition?  Ie, this incorporates
+more student practice with typing code.}
+
 %--------------------------------------------------------------------------------
@@
 To facilitate this transition to R programming, popular interactive teaching technologies
-have been created including \texttt{swirl} \citep{Kross}, Try R \citep{TryR}, LearnR, and DataCamp.
+have been created including Try R, \texttt{swirl}, \texttt{learnr}, and DataCamp.
 Interactive tools allow students to actively work through coding problems and receive
-immediate feedback.
+immediate feedback.  See Table \ref{tab:compare} for a comparison of existing
+technologies.
 
-%--------------------------------------------------------------------------------
-\subsubsection{Swirl}
+\hl{Best placement for this table?}
 
-\texttt{Swirl} is an open source R package where students can learn R programming
-directly in the R console \citep{Kross}. This interactive learning tool contains several
-pre-existing lessons but educators can also create their own lesson content to fit
-specific curriculum \citep{Carchedi2014}.  While \textit{swirl} can be linked to Massive
-Open Online Courses (MOOCs) like Coursera, integration of learning management systems (LMS)
-is not currently available.
+\begin{table}
+\begin{tabular}{lcccc}
+\toprule
+Feature                      & Try R  & \texttt{swirl}    & \texttt{learnr} & DataCamp \\
+\midrule
+%Requires R installation     & \cmark & \cmark            &  $\sim$         & \xmark   \\
+Web-based                    & \cmark & \xmark            &  $\sim$         & \cmark   \\
+Tracks student progress      & \xmark & $\sim$            &  \xmark         & \cmark   \\
+Integrates with LMS          & \xmark & \xmark            &  \xmark         & \cmark   \\
+Variety of lessons available & \xmark & \cmark            &  \xmark         & \cmark   \\
+Educators can create content & \xmark & \cmark            &  \cmark         & \cmark   \\
+%Meta-data available         & \xmark &   ?               &                 & \cmark   \\
+\bottomrule
+\end{tabular}
+\caption{Comparison of interactive technologies to learn programming in R.
+For web-based applications, R installation is not required.}
+\label{tab:compare}
+\end{table}
 
@@
 
-Try R is another interactive R programming course but unlike \texttt{swirl}, Try R
-is web-based \citep{TryR}. The RStudio console can be intimidating to new statistics students
+Try R is web-based interactive R programming course that consists only of
+codding exercises \citep{TryR}. The RStudio console
+can be intimidating to new statistics students
 so an  advantage of a web-based teaching tool is the clean and easy to use interface.
@@
 educators are limited to the existing lessons available on the Try R website.
-Lastly, Try R cannot currently integrate with LMS.
+Lastly, Try R does not currently integrate with learning management systems (LMS).
 
 %--------------------------------------------------------------------------------
-\subsubsection{LearnR?}
+\subsubsection{swirl}
+
+\texttt{swirl} is an open source R package where students can learn R programming
+directly in the R console (so it requires a local R installation) \citep{Kross}.
+This interactive learning tool incorporates both code exercises and multiple choice
+questions. \texttt{swirl} contains several pre-existing lessons, and
+educators can also create their own lesson content to fit
+specific curriculum \citep{Carchedi2014}.  While \texttt{swirl} can be linked to Massive
+Open Online Courses (MOOCs) like Coursera, integration of LMS
+is not currently available.
+
+%--------------------------------------------------------------------------------
+\subsubsection{learnr}
+
+\texttt{learnr} is an open source R package that converts R Markdown documents
+to programming tutorials using Shiny \citep{GarrettGrolemund2017}.  These
+tutorials can consist of code exercises, multiple choice questions, videos,
+and interactive Shiny components.  \texttt{learnr} enables instructors to
+write their own programming tutorials, but there is not a collection of readily available
+lessons.  Although the ``hint'' options in \texttt{learnr}
+are minimal, the \texttt{checkr} package works with \texttt{learnr} to provide
+tailored feedback \citep{DanielKaplan2018}.  \texttt{learnr} tutorials can be deployed either
+locally on a user's computer (requires R installation) or through a Shiny Server (web-based).
+This interactive tutorial does not allow for tracking of student progress.
 
@@
 The simplest way to begin building the course is to use the template course files from
-the \texttt{Create Course} dialog. This will automatically create a GitHub repository
+the \textit{Create Course} dialog. This will automatically create a GitHub repository
 that is linked to DataCamp.
@@
 
-Course creators can edit their courses through either GitHub or the \texttt{Teach Editor}
-accessed through the DataCamp website. The \texttt{Teach Editor} allows content
+Course creators can edit their courses through either GitHub or the \textit{Teach Editor}
+accessed through the DataCamp website. The \textit{Teach Editor} allows content
 creators to edit, preview, save changes, and synchronize to the GitHub repository.
 Editing completed via GitHub does not allow for automatic content viewing. Any changes
-that are made through the DataCamp \texttt{Teach Editor} will update the GitHub
+that are made through the DataCamp \textit{Teach Editor} will update the GitHub
 repository and vice versa.
@@
 Figure \ref{fig:code1} is an example of ``normal exercise'' syntax and Figure
-\ref{fig:preview} is the corresponding interface students see. Students read the 
+\ref{fig:preview} is the corresponding student interface. Students read the
 lesson information and instructions, answer the question, and submit their code.
@@
 \begin{figure}
-\caption{Syntax to create a ``normal exercise'' on DataCamp.  In DataCamp's
-\texttt{Teach Editor}, the syntax is color-coded.}
 \begin{Verbatim}[frame=single]
@@
 \end{Verbatim}
+\caption{Syntax to create a ``normal exercise'' on DataCamp.  In DataCamp's
+\texttt{Teach Editor}, the syntax is color-coded. \hl{Just include
+screenshot here instead of verbatim so color coding is visible?}}
 \label{fig:code1}
@@
 \begin{figure}[h]
+\includegraphics[width = 1.0\textwidth] {code1preview.png}
 \caption{Preview of the rendered result of the ``normal exercise'' syntax displayed
 in Figure \ref{fig:code1}.}
-\includegraphics[width = 1.0\textwidth] {code1preview.png}
 \label{fig:preview}
@@
 
-The SCT automatically assesses if the correct code was submitted. If a student submits 
-an incorrect answer, they will receive immediate feedback and guidance towards
+The SCT automatically assesses if the correct code was submitted \citep{Vankrunkelsven2016}. 
+If a student submits an incorrect answer, they will receive immediate feedback and guidance towards
 the correct answer.  The SCT is executed through DataCamp's \texttt{testwhat} R
@@
 
-\begin{table}\label{tab:SCT}
-\caption{Feedback provided in the R console and in the DataCamp lesson through the 
-SCT for the exercise shown in Figures \ref{fig:code1} and \ref{fig:preview}.}
+\hl{I don't think I have fully utilized the power of SCT in my example because
+you can link multiple SCTs together, right?  Could use a different example.}
+
+\begin{table}
 \begin{tabular}{lll}
@@
 \end{tabular}
+\caption{Feedback provided in the R console and in the DataCamp lesson through the
+SCT for the exercise shown in Figures \ref{fig:code1} and \ref{fig:preview}.}
+\label{tab:SCT}
 \end{table}
@@
 
-\begin{table}\label{tab:exercises}
-\caption{Exercise types currently supported in DataCamp}
+\begin{table}
 \begin{tabular}{ll}
@@
 \end{tabular}
+\caption{Exercise types currently supported in DataCamp}
+\label{tab:exercises}
 \end{table}
@@
 The \texttt{PureMultipleChoiceExercise} contains a question and a list of various
-answers - this exercise type does not include the R console and output. Similar to a
-\texttt{NormalExercise}, the lesson, instructions, hint, pre-exercise code and SCTs are 
-included in the exercise syntax. Instructors write the questions in the lesson portion 
+answers - this exercise type does not include the R console and output. 
+%Similar to a
+%\texttt{NormalExercise}, the lesson, instructions, hint, pre-exercise code and SCTs are
+%included in the exercise syntax. 
+Instructors write the questions in the lesson portion
 of the exercise, present options in the \textit{Instructions} section, and can specify a
@@
 can contribute simultaneously to the course.  To do so, go to the course repository on GitHub
-and under \texttt{Settings} enter the Github user names of collaborators. One note of caution 
+and under \textit{Settings} enter the Github user names of collaborators. One note of caution
 here - to deploy the course to your class, the primary content creator needs to be listed
-as member of the course.
+as member of the course in the DataCamp group.
 
@@
 chapter was posted on the course site, and then students were taken directly to the
-first page of the assigned chapter (no additional log in required!). Grades were 
+first page of the assigned chapter (no additional log-in required!). Grades were
 available in the Moodle grade book immediately after students completed the assignment.
@@
 While there will always be some students (among non-statistics majors) that grumble about
-having to learn R, overall student feedback was positive.
+having to learn R, overall student feedback was positive (see Table \ref{tab:evals}
+in the Appendix for comparison of course evaluations with and without DataCamp).
+Student comments included:
+\begin{itemize}
+\item \emph{DataCamp is really easy and fun to use.
+It is useful because it resembles the actual lab itself and we are still trying to figure out how to code ourselves but we are not penalize if we get the wrong answer.}
+\item \emph{Data camp was helpful because it was actually like R.}
+\item \emph{I think it's pretty good because it gives you an interactive way to look over what you'll need to do in class, but doesn't take super long. }
+\end{itemize}
+\hl{Clearly, I am cherry-picking here and there were criticisms of DataCamp as well. 
+How best to present?}
 
@@
 grade center was always the highest grade recorded for the student, regardless of
-the completion iteration (first, second attempt?) or date of completion.
+the completion iteration (first, second attempt?) or date of completion.  However,
+this is more of a Moodle integration issue than a DataCamp issue.
 
@@
 
+%--------------------------------------------------------------------------------
+\subsection{Other possibilities}
+
+Although we only discussed DataCamp classroom experiences for non-majors, this
+platform is also well-suited and appropriate for undergraduate students in statistics 
+and data science, as well as graduate students in statistics or even other disciplines. 
+In addition, DataCamp can be a great learning tool for students
+as they embark upon independent student research.
+
 %================================================================================
@@
 
--The only disadvantage of the modularity feature is that the sessions are not cumulative; every
-exercise begins with a clear work space so an object defined in a previous exercise needs
-to be defined again.
+While DataCamp is an incredible interactive tool to learn coding, there are some
+pedagogical disadvantages. First, DataCamp can be fast-paced. Of course, the 
+each user advances through the tutorial at their own speed; however, DataCamp
+lessons are designed to keep moving forward with no clear pauses for reflection.
+Another consequence of this is that DataCamp courses tend to assess correct
+input of code, but not correct interpretation of results. Educators building
+their own course content can incorporate interpretation questions based on 
+achieved output; however, due to the modularity feature of DataCamp sessions
+are not cumulative (every exercises begins with a clear workspace) so that 
+an object created in a coding exercise would need to be re-defined for the student
+in a multiple choice exercise. Lastly, due to the fast-paced nature, it is easy
+for students to feel like they ``get it'' in the moment, but have little
+recall as to what they did the next day. Educators can overcome this by 
+encouraging or requiring note-taking, or by providing quick reference guides
+of syntax learned for later use.
 
--DataCamp is changing constantly
+While DataCamp provides a platform to learn coding in R, it does not enable
+users to fully utilize the reproducible and version control capabilities
+of RStudio. Although it does contain courses such as 
+\emph{Reporting with R Markdown} and \emph{Introduction to Git for Data Science},
+it does not enable users to generate Markdown style reports from the web-based
+interface. \hl{(Can you imagine if there was a Markdown button at the end of a lesson
+to generate a report of what you learned?)} For this reason, educators may
+want to use DataCamp as a learning aid, but not as a primary mode for 
+student activities.
 
--emphasis on correct code over interpretation of results
-
--no way to produce reproducible reports based on data camp work
-
--no notes/summaries provided - easy to forget
-
--in the classroom
-
--glitches in teach editor
+DataCamp is a private, for-profit company that has gracefully allowed
+the academic community to utilize their resources for free.  However, 
+this means that both the website and way in which lesson content
+is created is constantly changing.  For example, between September of
+2017 and April of 2018, DataCamp:
+\begin{itemize}
+\item Changed exercise headers from single text line to a \texttt{yaml}
+\item Changed the naming of the exercise \texttt{PlainMultipleChoice} 
+to \texttt{PureMultipleChoice}
+\item Added new exercise options (the connected sub-exercises)
+\item Changed the \emph{teach} documentation
+\item Changed the web-site interface for \emph{groups}
+\end{itemize}
+While rapid and continuous development of DataCamp products is beneficial 
+to both educators and learners, it can be jarring for a new educator
+who just got accustomed to the platform.  Moreover, community
+content creators are not notified when these changes are deployed.  
+Thankfully, for now, lessons created under older formats (i.e.,
+with \texttt{PlainMultipleChoice} or headers in a single text
+line instead of a \texttt{yaml}) still render correctly and no updates are required to
+lesson syntax. This also means that any specific weblinks listed
+here or exercise syntax may already have changed by the time you read this.
 
@@
 
+DataCamp fills a much needed void for interactive coding exercises that allow
+for tracking of student progress.  Due to the breadth of courses already offered as
+well as the ability to create your own course content, DataCamp is a learning
+platform that can be used by any instructor that incorporates coding into their
+course content.  \hl{A bit more here?}
+
+%================================================================================
+\section{Appendix}
+\begin{table}
+ \resizebox{\textwidth}{!}{ 
+\begin{tabular}{lcc}
+\toprule
+	&	Winter 2017	  &	Winter 2018	\\
+    &   $(n = 63)$    &  $(n = 59)$  \\
+\midrule
+\multicolumn{3}{l}{\textbf{How do you rate the following items in terms of building your knowledge of introductory statistics?}} 					\\
+\multicolumn{3}{l}{\textbf{1 = Not valuable/ did not contribute; 4 = very valuable/highly contributed}}					\\
+Lab videos	            &	3.24	&   N/A		\\
+DataCamp assignments	&	N/A	    &	2.47	\\
+Lab assignments	        &	2.86	&	2.81	\\
+\midrule
+\multicolumn{3}{l}{\textbf{How well did the course address the following learning objectives?}}					\\
+\multicolumn{3}{l}{\textbf{1 = poor; 5 = great}}					\\
+Use R as a tool to perform statistical analysis	&	3.84	&	3.90	\\
+\midrule
+\multicolumn{3}{l}{\textbf{How were the pre-lab and lab assignments?}}					\\
+\multicolumn{3}{l}{\textbf{1 = strongly disagree; 5 = strongly agree}}					\\
+I had difficulty understanding the connections between lecture and lab.             	&	2.60    &	2.88	\\
+The pre-lab assignments sufficiently prepared me for lab	                            &	4.00	&	3.80	\\
+The lab assignments helped me see how statistical analysis is done in the real world.	&	3.63	&	3.51	\\
+DataCamp was easy to use	                                                            &	N/A	    &	4.15	\\
+I enjoyed learning how to code on DataCamp	                                            &	N/A	    &	3.32	\\
+\midrule
+\multicolumn{3}{l}{\textbf{How did you like using R in this class?}}					\\
+\multicolumn{3}{l}{\textbf{1 = strongly disagree; 5 = strongly agree}}					\\
+R was challenging to use the entire term	                    &	3.05	&	2.76	\\
+R became easier to use as the term progressed	                &	4.08	&	4.00	\\
+Using R made it hard to learn how to do statistical analysis	&	2.46	&	2.32	\\
+Using R helped me understand how to do statistical analysis	    &	3.17	&	3.39	\\
+I enjoyed using R	                                            &	2.87	&	2.92	\\
+I am glad I learned R	                                        &	3.46	&	3.61	\\
+\bottomrule
+\end{tabular}}
+\caption{Course evaluations from two sections of STAT 217 in Winter 2017 (without DataCamp, response rate = 90\%) 
+and Winter 2018 (with DataCamp, response rate = 82\%) taught
+by the same instructor with otherwise virtually no changes.}
+\label{tab:evals}
+\end{table}
+
+\hl{Is this table even worthwhile or of interest to include?  If so, I can work on better formatting.  Include
+SDs?  Present graphically instead?}
+
+%================================================================================
 \bibliographystyle{plainnat}

### 2018-04-18 manuscript.tex
updates from Weston

@@
 \hl{Weston - insert background here}
-DataCamp (\url{www.datacamp.com}) was first created in X with the mission to X.
+DataCamp (\url{www.datacamp.com}) was first created in 2013 with the mission to 
+``democratize data science education world wide''.
 DataCamp provides a comprehensive web-based platform to interactive lessons on various coding
@@
 for academic purposes the \textit{Premium} DataCamp content is free for up to six months.
-Currently, DataCamp has X number of users across X countries.
+Currently, DataCamp has 2.5 million users across virtually all countries.
 
@@
 %--------------------------------------------------------------------------------
+\subsection{Builds}
+
+Once you have executed and saved changes to your DataCamp course, DataCamp will initialize
+a ``build'' attempt.  A build performs validity checks on exercises, provides
+warnings and recommendations, and makes the updates available on the learning
+platform.  Possible build status's include: \emph{in progress}, \emph{warning},
+\emph{pass}, and \emph{fail}.  In the event that a build fails, a build log
+can help you to identify the source of the error and make corrections. Warnings 
+can include helpful suggestions based on design recommendations from DataCamp, 
+including items such as ``The course shouldn't have more than 5 chapters'' or 
+``Exercise X should have at least one submission correctness test''.
+
+%--------------------------------------------------------------------------------
 \subsection{Advice for course development}
@@
 
-\hl{Weston - I can't find metadata for my course!  Is there a difference in how
-data is recorded when you add members to DataCamp via email vs link via LMS?
+In addition to tracking data on individual users, DataCamp also tracks metadata 
+about the course overall.  Currently, the metadata is readily available to educators
+utilizing premium courses but not to those utilizing community courses.  However,
+educators utilizing community courses can correspond directly with DataCamp to 
+request metadata for their course.  Metadata includes the following for each exercise
+in a course:
+\begin{itemize}
+\item identifying information 
+\item number of individuals who started the exercise
+\item number of individuals who completed the exercise
+\item the percent that completed the exercise
+\item the percent that asked for a hint
+\item the percent that asked for the solution
+\end{itemize} 
+This information can be used to refine and improve exercises.  A guideline
+used by DataCamp is to flag and modify exercises that have exceed 20\% 
+on hint or solution requests.
 
-Mine - can you add in here?
-}
+\hl{Mine - can you add in here?}
 
